---
title: "Initial Communities"

author: "ZJ"

date: "March 25, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r python stuff, message=FALSE,warning=FALSE,include=FALSE}
library(reticulate)
use_condaenv("randpython")
#import("geopandas")
#import("pandas")
#import("gdal")
#import("rasterio")
#virtualenv_list()

```

Initial Communities: 

Within LANDIS-II each raster is given an initial community, describing the biomass for each age class of each species present. 
This requires that data both represent landscape coverage (containign sufficient data about the location of certain stands) and be representative
of demographics ( for example, age class is not usually known, nor are sufficient measure of carbon or biomass). 
The FIA database (Bechotld and Patterson 2005) while often one of the richest source of data on forest
stands is nowhere near to contiguous and the locatplots. 
Conversly, imputation maps can estimate the amount (in basal area ) of each tree species expected at each location, but often lack
the more robust data needed for stand age and biomass.  Our goal is therefore to create an initial communities mpa that integrates  the strengths of
both these methods. We will use the spatial estimations provided by imputation data and associate it with current and recent FIA plot
to take advantage of their more robust data.  We will use several indexes of similarity (or dissimilarity) to compare imputed raster
cell compositions with the composition of FIA sites, assuming that the FIA sites provide a stand-in example for a stand of that type.

Bechtold, W. A., & Patterson, P. L. (2005). The enhanced forest inventory and analysis program--national sampling design and estimation procedures (Vol. 80). USDA Forest Service, Southern Research Station.

####FS imputation maps 

We begin by using FS imputation maps(Wilson et al., 2013). These maps can be found at https://www.fs.usda.gov/rds/archive/Product/RDS-2013-0013.   These maps were created combining MODIS imagery with environmental variables, using a k-nearest neighbor and canonical correspondence
analysis to estimate the abundance and distribution of each species at a 250 m pixel size (Wilson et al., 2013). 



Citation:
Wilson, Barry Tyler; Lister, Andrew J.; Riemann, Rachel I.; Griffith, Douglas M. 2013. Live tree species basal area of the contiguous
United States (2000-2009). Newtown Square, PA: USDA Forest Service, Rocky Mountain Research Station.
https://doi.org/10.2737/RDS-2013-0013


First, each map was reprojected and masked to the study area.
```{python,message=FALSE,warning=FALSE,include=FALSE,eval=FALSE}
#Packages
import geopandas as gp
import rasterio as rt
import rasterio.mask
import gdal 
from rasterio.mask import mask
from rasterio.crs import CRS

##########Functions

def getFeatures(gdf):
    """Function to parse features from GeoDataFrame in such a manner that rasterio wants them"""
    import json
    return [json.loads(gdf.to_json())['features'][0]['geometry']]


##Imports
"This is our list of species of intrest"

specieslist=[832,315,356,373,391,402,407,421,491,544,591,602,731,762,812,
             731,
             762,
             812,
             931,
             952,
             316,
             621,
             129,
             711,
             132,
             802,
             833,
             261,
             372,
             693,
             901,
             403,
             837,
             131,
             110,
             126,
             409,
             371,531,318,655,541,951,581,332,97,651,123,16,761,806]


#specieslist=[611,491]
"A simple loop to cut maps"
for sp in specieslist:
    print(sp)
    "Bring in ty wilson's imputation map for a species"
    filename="Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/Ty_wilson/Inputs/s"+str(sp)+".img"
    input_raster=gdal.Open(filename)
    "create a temp map, This is a weird gdal/rasterio work around"
    output_raster=r"Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/Inputs/temp.tif"
    "reformat raster to the format of AOI"
    gdal.Warp(output_raster,input_raster,dstSRS='EPSG:26917')
    "bring um back"
    data=rt.open(output_raster)
    " get the CRS cod for our projection"    
    crs = CRS.from_epsg(26917)
    #print(CRS.to_string(crs))
    #Lut_tif="Z://Users/zjrobbin/Desktop/Geopandas/temp/practice"+ecoregion+".tif"
    "load in the AOI shape"
    AOI=gp.read_file(r"Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/InputsTy_wilson/Inputs/Dissolved_AOI.shp",crs={'init':'EPSG:26917'})
    "get AOI's crs code"
    geo=AOI.to_crs(crs=data.crs.data)
    coords=getFeatures(geo)
    ###Copy the meta data
    out_meta = data.meta.copy()
    
    ####Preform a mask on the raster
    out_img,out_transform=mask(raster=data,shapes=coords,crop=True)
    out_meta = data.meta.copy()
    epsg_code = int(data.crs.data['init'][5:])
    out_meta.update({"driver": "GTiff",
                             "height": out_img.shape[1],
                             "width": out_img.shape[2],
                             "transform": out_transform}
                                )
    ######
    out_tif="Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/"+str(sp)+"_cut.tif"
    #######
    with rasterio.open(out_tif, "w", **out_meta) as dest:
        dest.write(out_img)
    ###rewritting as a presence absence map                 
    data=rt.open(out_tif)
    #get stats
    width=data.width
    height=data.height
    projection=data.crs
   #Get band
    band1=data.read(1)
    #Write new
    new_dataset=rt.open("Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/Inputs/PA"+str(sp)+"_cut.tif", 'w', driver='GTiff',height=height, width=width, count=1, dtype='float32', crs=projection) 
    #Alter band
    band1[band1!=0]=1
    #Write
    new_dataset.write(band1,1)
    #Shut the door. 
    new_dataset.close()
```

Here is what the intial maps looked like and here is our reprojection and masking 

``` {r,fig.height=20.0,fig.width=14.0,align="center",message=FALSE,warning=FALSE}
library(raster)
library(rgdal)
library(RColorBrewer)
library(rasterVis)
  
div_raster_col<-brewer.pal(7,"Spectral")
single_line_col<-brewer.pal(9,"YlGn")
single_line_col[1]<-"#000000"

TopTenSP<-c(832,316,621,129,711,806,132,802,833,261)

###Basal Area Maps
par(mar = c(1,1,2,2),mfrow=c(2,1))
AOI<-readOGR("Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/Inputs/Ty_wilson/Inputs/Dissolved_AOI.shp",verbose=FALSE)
TY_after<-raster("Z:/Robbins/Sapps/Model_Prep/Initial_Communities/Ty_wilson_Backup/Outputs/316_cut.tif")
TY_before<-raster("Z:/Robbins/Sapps/Model_Prep/Initial_Communities/Ty_wilson_Backup/Inputs/s316.img")

plot(TY_before,main=paste("Ty Wilson's Red Maple map"),axes=FALSE, box=FALSE,col=single_line_col,col.lab="white",breaks=c(0,5,30,45,60,75,100),bg="black")
plot(AOI,border="white",add=TRUE)
plot(TY_after,main=paste("Southern Apps. Red Maple",sep=""),axes=FALSE, box=FALSE,col=single_line_col,col.axis="white", breaks=c(0,5,30,45,60,75,100), bg="black" )
plot(AOI,border="white",add=TRUE)
```

Once we create the speices basal area maps we need to associate each sites basal area composition with an FIA site. 
We used four differnt comparison methods to compare to the FIA data we have gathered
[here](https://github.com/LANDIS-II-Foundation/Project-Southern-Appalachians-2018/tree/master/Parameterizing/FIA%20Analysis) 




```{r,message=FALSE,warning=FALSE}
library(sp)
library(raster); options(scipen=999) # scipen removes scientific notation from FIA data
library(rgdal)
library(plyr)
library(dplyr)
library(reshape2)
SPLUT<-read.csv("Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/Inputs/SpeciesLUT.csv")
SP<-unique(SPLUT$Species)
```



```{r,eval=FALSE}
###Work Drives
w_dir<-"Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/"
setwd(w_dir)


####We want to get all the data to look similar for comparison. 
#
#FIA data. 
#
###Loading in the FIA sites that are in the study area.
TREEtbl_all<-read.csv("Inputs/AOI_TREE.csv")
TREEtbl_all<-(TREEtbl_all[!is.na(TREEtbl_all$TPA_UNADJ),])

###Get the plot numbers
plot_numbers<-TREEtbl_all$PLT_CN

# Bring in species excel file for my species of interest
###This is a LUT table that should have the FIA codes for each speies
spp_file <- read.csv(paste(w_dir,"Inputs/SpeciesLUT.csv",sep=""))
spp <- spp_file[,"Species"] 

#This selects just the  species of interest from all the species in the FIA plots. 
tree_data <- TREEtbl_all[TREEtbl_all$SPCD %in% spp,]


###Clean the Data####
tree_data[is.na(tree_data$DIA),]<-0.0
tree_data<-tree_data[order(-tree_data$DIA),]
###Get the plotcn
uniquepltcn<-unique(tree_data$PLT_CN)

#This loop reformats the FIA data and expands it to look like the TW data Dia/
Plt_DF<-NULL
for( i in 1:length(uniquepltcn)){
    two<-NULL
    end<-NULL
    Plot<-uniquepltcn[i]
   # print(i)
    Thisguy<-tree_data[tree_data$PLT_CN==uniquepltcn[i],]
    ABFR<-sum(((Thisguy$DIA[Thisguy$SPCD==16]^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==16])
    ####so the Diam is turned to Basal Area, Mutliplied by the expansion as a matrix, these are summed. then
    ### I checked this for order of operation concerns.
    PICRU<-sum((((Thisguy$DIA[Thisguy$SPCD==97])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==97])
    PIEC2<-sum((((Thisguy$DIA[Thisguy$SPCD==110])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==110])
    PIPU5<-sum((((Thisguy$DIA[Thisguy$SPCD==123])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==123])
    PIRI<-sum((((Thisguy$DIA[Thisguy$SPCD==126])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==126])
    PIST<-sum((((Thisguy$DIA[Thisguy$SPCD==129])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==129])
    PITA<-sum((((Thisguy$DIA[Thisguy$SPCD==131])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==131])
    PIVI2<-sum((((Thisguy$DIA[Thisguy$SPCD==132])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==132])
    TSCA<-sum((((Thisguy$DIA[Thisguy$SPCD==261])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==261])
    ACPE<-sum((((Thisguy$DIA[Thisguy$SPCD==315])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==315])
    ACRU<-sum((((Thisguy$DIA[Thisguy$SPCD==316])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==316])
    ACSA3<-sum((((Thisguy$DIA[Thisguy$SPCD==318])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==318])
    AEFL<-sum((((Thisguy$DIA[Thisguy$SPCD==332])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==332])
    AMAR<-sum((((Thisguy$DIA[Thisguy$SPCD==356])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==356])
    BEAL<-sum((((Thisguy$DIA[Thisguy$SPCD==371])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==371])
    BELE<-sum((((Thisguy$DIA[Thisguy$SPCD==372])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==372])
    BENI<-sum((((Thisguy$DIA[Thisguy$SPCD==373])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==373])
    CACA18<-sum((((Thisguy$DIA[Thisguy$SPCD==391])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==391])
    CARCO<-sum((((Thisguy$DIA[Thisguy$SPCD==402])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==402])
    CARGL<-sum((((Thisguy$DIA[Thisguy$SPCD==403])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==403])
    CAROV<-sum((((Thisguy$DIA[Thisguy$SPCD==407])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==407])
    CARAL<-sum((((Thisguy$DIA[Thisguy$SPCD==409])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==409])
    CASDE<-sum((((Thisguy$DIA[Thisguy$SPCD==421])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==421])
    COFL2<-sum((((Thisguy$DIA[Thisguy$SPCD==491])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==491])
    FAGR<-sum((((Thisguy$DIA[Thisguy$SPCD==531])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==531])
    FAXI<-sum((((Thisguy$DIA[Thisguy$SPCD==541])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==541])
    FAPE<-sum((((Thisguy$DIA[Thisguy$SPCD==544])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==544])
    HADI<-sum((((Thisguy$DIA[Thisguy$SPCD==581])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==581])
    ILOP<-sum((((Thisguy$DIA[Thisguy$SPCD==591])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==591])
    JUNI<-sum((((Thisguy$DIA[Thisguy$SPCD==602])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==602])
    LIST2<-sum((((Thisguy$DIA[Thisguy$SPCD==611])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==611])
    LITU<-sum((((Thisguy$DIA[Thisguy$SPCD==621])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==621])
    MAAC<-sum((((Thisguy$DIA[Thisguy$SPCD==651])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==651])
    MAMA<-sum((((Thisguy$DIA[Thisguy$SPCD==655])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==655])
    NYSY<-sum((((Thisguy$DIA[Thisguy$SPCD==693])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==693])
    OXAR<-sum((((Thisguy$DIA[Thisguy$SPCD==711])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==711])
    PLOC<-sum((((Thisguy$DIA[Thisguy$SPCD==731])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==731])
    PRPE<-sum((((Thisguy$DIA[Thisguy$SPCD==761])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==761])
    PRSE<-sum((((Thisguy$DIA[Thisguy$SPCD==761])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==761])
    QULA2<-sum((((Thisguy$DIA[Thisguy$SPCD==802])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==802])
    QUCO2<-sum((((Thisguy$DIA[Thisguy$SPCD==806])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==806])
    QUFA<-sum((((Thisguy$DIA[Thisguy$SPCD==812])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==812])
    QUPR2<-sum((((Thisguy$DIA[Thisguy$SPCD==832])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==832])
    QURU<-sum((((Thisguy$DIA[Thisguy$SPCD==833])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==833])
    QUST<-sum((((Thisguy$DIA[Thisguy$SPCD==835])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==835])
    LIST2<-sum((((Thisguy$DIA[Thisguy$SPCD==837])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==837])
    ROBP<-sum((((Thisguy$DIA[Thisguy$SPCD==901])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==901])
    OXAR<-sum((((Thisguy$DIA[Thisguy$SPCD==931])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==931])
    TIAM<-sum((((Thisguy$DIA[Thisguy$SPCD==951])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==951])
    TIAM2<-sum((((Thisguy$DIA[Thisguy$SPCD==952])^2)*.005454)*Thisguy$TPA_UNADJ[Thisguy$SPCD==952])
    row<-cbind(Plot,ABFR,PICRU,PIEC2,PIPU5,PIRI,PIST,PITA,PIVI2,TSCA,ACPE,ACRU,ACSA3,AEFL,AMAR,BEAL,BELE,BENI,CACA18,CARCO,CARGL,CAROV,CARAL,CASDE,COFL2,FAGR,FAXI,FAPE,HADI,ILOP,JUNI,
               LIST2,LITU,MAAC,MAMA,NYSY,OXAR,PLOC,PRPE,PRSE,QULA2,QUCO2,QUFA,QUPR2,QURU,QUST,LIST2,ROBP,OXAR,TIAM,TIAM2)
    
    Plt_DF<-rbind(Plt_DF,row)
  }
###Sum each row for index
Plt_DF_Sums<-rowSums(Plt_DF[,-1])
Plt_DF_2<-cbind(Plt_DF,Plt_DF_Sums)
Plt_CN<-Plt_DF_2[,1]
Plt_DF_2<-Plt_DF_2[,-1]
Plt_DF_2<-cbind(Plt_DF_2,Plt_CN)
Plt_DF_2<-as.data.frame(Plt_DF_2)


print(head(Plt_DF_2))
```



```{r}
#Now we load in our ty wilson maps and turn it into a dataframe. 
####load in the Biomass Imputation Rasters for the top 50 species as according to FIA Analysis
w_dir<-"Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/"
clip_16 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/16_cut.tif",sep=""))
clip_97 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/97_cut.tif",sep=""))
clip_110 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/110_cut.tif",sep=""))
clip_123 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/123_cut.tif",sep=""))
clip_126 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/126_cut.tif",sep=""))
clip_129 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/129_cut.tif",sep=""))
clip_131 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/131_cut.tif",sep=""))
clip_132 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/132_cut.tif",sep=""))
clip_261 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/261_cut.tif",sep=""))
clip_315 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/315_cut.tif",sep=""))
clip_316 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/316_cut.tif",sep=""))
clip_318 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/318_cut.tif",sep=""))
clip_332 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/332_cut.tif",sep=""))
clip_356 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/356_cut.tif",sep=""))
clip_371 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/371_cut.tif",sep=""))
clip_372 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/372_cut.tif",sep=""))
clip_373 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/373_cut.tif",sep=""))
clip_391 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/391_cut.tif",sep=""))
clip_402 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/402_cut.tif",sep=""))
clip_403 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/403_cut.tif",sep=""))
clip_407 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/407_cut.tif",sep=""))
clip_409 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/409_cut.tif",sep=""))
clip_421 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/421_cut.tif",sep=""))
clip_491 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/491_cut.tif",sep=""))
clip_531 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/531_cut.tif",sep=""))
clip_541 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/541_cut.tif",sep=""))
clip_544 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/544_cut.tif",sep=""))
clip_581 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/581_cut.tif",sep=""))
clip_591 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/591_cut.tif",sep=""))
clip_602 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/602_cut.tif",sep=""))
clip_611 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/611_cut.tif",sep=""))
clip_621 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/621_cut.tif",sep=""))
clip_651 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/651_cut.tif",sep=""))
clip_655 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/655_cut.tif",sep=""))
clip_693 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/693_cut.tif",sep=""))
clip_711 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/711_cut.tif",sep=""))
clip_731 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/731_cut.tif",sep=""))
clip_761 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/761_cut.tif",sep=""))
clip_762 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/762_cut.tif",sep=""))
clip_802 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/802_cut.tif",sep=""))
clip_806 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/806_cut.tif",sep=""))
clip_812 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/812_cut.tif",sep=""))
clip_832 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/832_cut.tif",sep=""))
clip_833 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/833_cut.tif",sep=""))
clip_835 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/833_cut.tif",sep=""))
clip_837 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/837_cut.tif",sep=""))
clip_901 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/901_cut.tif",sep=""))
clip_931 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/931_cut.tif",sep=""))
clip_951 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/951_cut.tif",sep=""))
clip_952 <- raster(paste(w_dir,"/Inputs/Ty_wilson/Outputs/952_cut.tif",sep=""))

# Stack the rasters
clip_stack<-stack(c(clip_16, clip_97, clip_110, clip_123 , clip_126,clip_129, clip_131, clip_132, clip_261, clip_315,
              clip_316,clip_318,clip_332,clip_356,clip_371,clip_372,clip_373,clip_391,clip_402,clip_403,clip_407,
              clip_409,clip_421,clip_491,clip_531,clip_541,clip_544,clip_581,clip_591,clip_602,clip_611,
              clip_621,clip_651,clip_655,clip_693,clip_711,clip_731,clip_761,clip_762,clip_802,clip_806,clip_812,clip_832,clip_833,
              clip_835,clip_837,clip_901,clip_931,clip_951,clip_952))

has.data = which(!is.na(getValues(max(clip_stack, na.rm=TRUE))))
N_hasdata<-length(has.data)
###Visualize
plot(clip_stack)
###Create Dataframe
clip_stack_df <- as.data.frame(clip_stack)
####Clear the rasters
rm(clip_16, clip_97, clip_110, clip_123 , clip_126,clip_129, clip_131, clip_132, clip_261, clip_315,
  clip_316,clip_318,clip_332,clip_356,clip_371,clip_372,clip_373,clip_391,clip_402,clip_403,clip_407,
  clip_409,clip_421,clip_491,clip_531,clip_541,clip_544,clip_581,clip_591,clip_602,clip_611,
  clip_621,clip_651,clip_655,clip_693,clip_711,clip_731,clip_761,clip_762,clip_802,clip_806,clip_812,clip_832,clip_833,
  clip_835,clip_837,clip_901,clip_931,clip_951,clip_952)
###Count how many locations contain data
count1=as.data.frame(rowSums(clip_stack_df[,1:11]))
N_zeros_indataframe<-sum(is.na(count1))
N_zero_and_hasdata<-sum(N_zeros_indataframe,N_hasdata)
NumberofRaster<-nrow(clip_stack_df)



# Extract data for each cell of raster stack
cr <- extract(clip_stack, c(1: ncell(clip_stack)))
clip_ras_df <- as.data.frame(cr)
```




```{r}
########Create a threshold for which to remove low proportion trees#####
########This was used out of fear of over distribution of species. 
# Becuase we believe the Ty Wilson data to be perhaps too liberal with placing low basal area trees across a wider area, we set a #tresehold of removal to remove basal area below .05 of the total basal area. This also makes association earier.
Threshold=.05
cr_bi <- cr
Sum<-rowSums(cr_bi)
totalBa<-sum(Sum)
cr_bi<-cbind(cr_bi,Sum)
Sumper=Sum*Threshold
cr_bi<-cbind(cr_bi,Sumper)


test1<-cr_bi[459415,]
cr_bi[cr_bi<Sumper]<-0
test2<-cr_bi[459415,]
cr_bi<-as.data.frame(cr_bi[,(-52)])
test1<-as.data.frame((cr_bi[459415,]))
###This creates a market to locate each raster cell.
Marker<-as.data.frame(1:nrow(cr))
cr_bi<-cbind(cr_bi,Marker)
###Create the data frame
colnames(cr_bi)<-c('ABFR','PICRU','PIEC2','PIPU5','PIRI','PIST','PITA','PIVI2','TSCA','ACPE','ACRU','ACSA3','AEFL','AMAR','BEAL','BELE','BENI','CACA18','CARCO','CARGL','CAROV','CARAL','CASDE','COFL2','FAGR','FAXI','FAPE','HADI','ILOP','JUNI',
                   'LIST2','LITU','MAAC','MAMA','NYSY','OXAR','PLOC','PRPE','PRSE','QULA2','QUCO2','QUFA','QUPR2','QURU','QUST','LIST2','LITU',"OXAR","TIAM","TIAM2","Sum","Cell")

#nrow(cr_bi)

```

```{r,eval=FALSE}
#####Isolate all the empty cells so we don't need to process them
zeros=cr_bi[(cr_bi[,1]==0 &cr_bi[,2]==0&
                   cr_bi[,3]==0&
                   cr_bi[,4]==0&
                   cr_bi[,5]==0&
                   cr_bi[,6]==0&
                   cr_bi[,7]==0&
                   cr_bi[,8]==0&
                   cr_bi[,9]==0&
                   cr_bi[,10]==0&
                   cr_bi[,11]==0&
                  cr_bi[,12]==0&
                  cr_bi[,13]==0&
               cr_bi[,14]==0&
               cr_bi[,15]==0&
               cr_bi[,16]==0&
               cr_bi[,17]==0&
               cr_bi[,18]==0&
               cr_bi[,19]==0&
               cr_bi[,20]==0&
               cr_bi[,21]==0&
               cr_bi[,22]==0&
               cr_bi[,23]==0&
               cr_bi[,24]==0&
               cr_bi[,25]==0&
               cr_bi[,26]==0&
               cr_bi[,27]==0&
               cr_bi[,28]==0&
               cr_bi[,29]==0&
               cr_bi[,30]==0&
               cr_bi[,31]==0&
               cr_bi[,32]==0&
               cr_bi[,33]==0&
               cr_bi[,34]==0&
               cr_bi[,35]==0&
               cr_bi[,36]==0&
               cr_bi[,37]==0&
               cr_bi[,38]==0&
               cr_bi[,39]==0&
               cr_bi[,40]==0&
               cr_bi[,41]==0&
               cr_bi[,42]==0&
               cr_bi[,43]==0&
               cr_bi[,44]==0&
               cr_bi[,45]==0&
               cr_bi[,46]==0&
               cr_bi[,47]==0&
               cr_bi[,48]==0&
               cr_bi[,49]==0&
               cr_bi[,50]==0&
               cr_bi[,51]==0),]


####Isolate non-empty Cells for processing
cr_bi_spp=cr_bi[!(cr_bi[,1]==0 &cr_bi[,2]==0&
                    cr_bi[,3]==0&
                    cr_bi[,4]==0&
                    cr_bi[,5]==0&
                    cr_bi[,6]==0&
                    cr_bi[,7]==0&
                    cr_bi[,8]==0&
                    cr_bi[,9]==0&
                    cr_bi[,10]==0&
                    cr_bi[,11]==0&
                    cr_bi[,12]==0&
                    cr_bi[,13]==0&
                    cr_bi[,14]==0&
                    cr_bi[,15]==0&
                    cr_bi[,16]==0&
                    cr_bi[,17]==0&
                    cr_bi[,18]==0&
                    cr_bi[,19]==0&
                    cr_bi[,20]==0&
                    cr_bi[,21]==0&
                    cr_bi[,22]==0&
                    cr_bi[,23]==0&
                    cr_bi[,24]==0&
                    cr_bi[,25]==0&
                    cr_bi[,26]==0&
                    cr_bi[,27]==0&
                    cr_bi[,28]==0&
                    cr_bi[,29]==0&
                    cr_bi[,30]==0&
                    cr_bi[,31]==0&
                    cr_bi[,32]==0&
                    cr_bi[,33]==0&
                    cr_bi[,34]==0&
                    cr_bi[,35]==0&
                    cr_bi[,36]==0&
                    cr_bi[,37]==0&
                    cr_bi[,38]==0&
                    cr_bi[,39]==0&
                    cr_bi[,40]==0&
                    cr_bi[,41]==0&
                    cr_bi[,42]==0&
                    cr_bi[,43]==0&
                    cr_bi[,44]==0&
                    cr_bi[,45]==0&
                    cr_bi[,46]==0&
                    cr_bi[,47]==0&
                    cr_bi[,48]==0&
                    cr_bi[,49]==0&
                    cr_bi[,50]==0&
                    cr_bi[,51]==0),]
####Do those two add up? they should
nrow(zeros)+nrow(cr_bi_spp)

cr_bi_spp<-as.data.frame(cr_bi_spp)

```

We created dataframes of each site (imputation data, and FIA plots) reformatted to have matching features with regard to basal area. In this case, that is a basal areasum for each species, and a basal area sum for each total plot in units of a gram per meter squared. Then each raster cell is 
evaluated against each plot for dissimilarity using a formula such as this: 


```{r,echo=TRUE}
####This is the New_Sorensons_Similarity_function

New_Sorensons_Similarity<-function(Break,Plt_DF_2){####Break is just our cr_bi_spp broken down for speed
                                                    ####Plt_DF_2 is the FIA product above
 ###Create Null objects to feed
  Log<-NULL
  Output<-NULL
  for(j in 1:nrow(Break)){
    ##Each raster cell
    practice<-Break[j,]
    cell<-practice$Cell
    print(cell)
    ####Get just the trees, no sums
    finder1<-practice[,c(-51,-52)]
    Sample1<-Plt_DF_2
    Sample2<-finder1
    DeltaSamples<-NULL
    ###Preforming the Indexing
    if(!is.null(nrow(Sample2))){
      for(i in 1:length(Sample2)){
        #The top half of the function
        ###is a iterable maximum function.
        absw=abs(Sample2[,i]-Sample1[,i])
        mixed<-(Sample2[,i]+Sample1[,i])
        top<-(mixed-absw)
        halfed=.5*top
        DeltaSamples<-cbind(DeltaSamples,halfed)
        
      }
    }
    ###The sum of Top
      Top<-rowSums(DeltaSamples)
    ###The sum of bottom     
      Bottom<-Plt_DF_2[,51]+practice[,51]
    ###The index
    index<-Top/Bottom
   ###Assign each site its index
    Plt_indexed<-cbind(Plt_DF_2,index)
   ###Find the one with the highest index
    Closestplot<-max(Plt_indexed[,52][Plt_indexed[,53]==max(index)])
    #Record the score
    indexscore<-(Plt_indexed$index[Plt_indexed$Plt_CN==Closestplot])
    ###Create a row of the cell, its assinged plot and the score
    row<-cbind(cell,Closestplot,indexscore)    
    Output<-rbind(row,Output)
    ###This is for analysis log
    row2<-cbind(j,indexscore,finder1)
    row3<-cbind(j,indexscore,Plt_DF_2[Plt_DF_2$Plt_CN==Closestplot,])
    row3<-row3[,c(-53,-54)]
    colnames(row3)<-c("iteration","index",'ABFR','PICRU','PIEC2','PIPU5','PIRI','PIST','PITA','PIVI2','TSCA','ACPE','ACRU','ACSA3','AEFL',
                      'AMAR','BEAL','BELE','BENI','CACA18','CARCO','CARGL','CAROV','CARAL','CASDE','COFL2','FAGR','FAXI','FAPE','HADI','ILOP',
                      'JUNI','LIST2','LITU','MAAC','MAMA','NYSY','OXAR','PLOC','PRPE','PRSE','QULA2','QUCO2','QUFA','QUPR2','QURU','QUST',
                      'LIST2','LITU',"OXAR","TIAM","TIAM2")
    colnames(row2)<-c("iteration","index",'ABFR','PICRU','PIEC2','PIPU5','PIRI','PIST','PITA','PIVI2','TSCA','ACPE','ACRU','ACSA3','AEFL',
                      'AMAR','BEAL','BELE','BENI','CACA18','CARCO','CARGL','CAROV','CARAL','CASDE','COFL2','FAGR','FAXI','FAPE','HADI','ILOP',
                      'JUNI','LIST2','LITU','MAAC','MAMA','NYSY','OXAR','PLOC','PRPE','PRSE','QULA2','QUCO2','QUFA','QUPR2','QURU','QUST',
                      'LIST2','LITU',"OXAR","TIAM","TIAM2")
    Log<-rbind(Log,row2,row3)
    
  }
  
  return(list(Output,Log))
}
```


The formulas we used for this were, 

Bray Curtis: 
$1- ((2Cij)/Si+Sj)$

where C is the Basal area of species in common between the two sites and S is the total basal area at each site. 

Jaccards: 
$1- (Ci+Cj/Si+Sj)$ 
The Basal area of species that are include in both sites(inclusive) divided by the the totals 



Euclidean Distance: 
$Sqrt((ai+aj)^2+(bi+bj)^2..(ni+nj)^2)$
the common biomass is square and the square root of the sum is taken. 


And Sorensens: 

$\frac{2*\sum(min(aij+bij))}{Si+Sj}$


The two least dissimilar plots are assigned to one another. This process is repeated for site on the landscape. 

We tested several associations to  compare the results with the initial communities maps and the FIA data we had gathered earlier


```{r,,message=FALSE,warning=FALSE,include=FALSE,eval=FALSE}
###Faster before 50,000
#FakeBreak<-cr_bi_spp[1:500,]
FirstBreak<-cr_bi_spp[1:breaklist[1],]
SecondBreak<-cr_bi_spp[breaklist[1]:breaklist[2],]
ThirdBreak<-cr_bi_spp[breaklist[2]:breaklist[3],]
FourthBreak<-cr_bi_spp[breaklist[3]:breaklist[4],]
FifthBreak<-cr_bi_spp[breaklist[4]:breaklist[5],]
SixthBreak<-cr_bi_spp[breaklist[5]:breaklist[6],]
SeventhBreak<-cr_bi_spp[breaklist[6]:breaklist[7],]
EighthBreak<-cr_bi_spp[breaklist[7]:breaklist[8],]
NinthBreak<-cr_bi_spp[breaklist[8]:breaklist[9],]
TenthBreak<-cr_bi_spp[breaklist[9]:breaklist[10],]
###make sure it adds up
nrow(FirstBreak)+nrow(SecondBreak)+nrow(ThirdBreak)+nrow(FourthBreak)+nrow(FifthBreak)+
  nrow(SixthBreak)+nrow(SeventhBreak)+nrow(EighthBreak)+nrow(NinthBreak)+nrow(TenthBreak)
nrow(cr_bi_spp)



#####Preform Association.
FirstSection<-New_Sorensons_Similarity(FirstBreak,Plt_DF_2)
SecondSection<-New_Sorensons_Similarity(SecondBreak,Plt_DF_2)
ThirdSection<-New_Sorensons_Similarity(ThirdBreak,Plt_DF_2)
FourthSection<-New_Sorensons_Similarity(FourthBreak,Plt_DF_2)
FifthSection<-New_Sorensons_Similarity(FifthBreak,Plt_DF_2)
SixthSection<-New_Sorensons_Similarity(SixthBreak,Plt_DF_2)
SeventhSection<-New_Sorensons_Similarity(SeventhBreak,Plt_DF_2)
EighthSection<-New_Sorensons_Similarity(EighthBreak,Plt_DF_2)
NinthSection<-New_Sorensons_Similarity(NinthBreak,Plt_DF_2)
TenthSection<-New_Sorensons_Similarity(TenthBreak,Plt_DF_2)



##Post run save point
save.image(file="New_Sorensons_Similarity_Practice.Rdata")

###Extract the Output and the Log
Output<-rbind(as.data.frame(FirstSection[1]),as.data.frame(SecondSection[1]),as.data.frame(ThirdSection[1]),
              as.data.frame(FourthSection[1]),as.data.frame(FifthSection[1]),as.data.frame(SixthSection[1]),
              as.data.frame(SeventhSection[1]),as.data.frame(EighthSection[1]),
              as.data.frame(NinthSection[1]),as.data.frame(TenthSection[1]))

length(unique(Output$Closestplot))

Log<-rbind(as.data.frame(FirstSection[2]),as.data.frame(SecondSection[2]),as.data.frame(ThirdSection[2]),
            as.data.frame(FourthSection[2]),as.data.frame(FifthSection[2]),as.data.frame(SixthSection[2]),
            as.data.frame(SeventhSection[2]),as.data.frame(EighthSection[2]),as.data.frame(NinthSection[2]),
            as.data.frame(NinthSection[2]),as.data.frame(TenthSection[2]))

colnames(Log)<-c("iteration","index",'ABFR','PICRU','PIEC2','PIPU5','PIRI','PIST','PITA','PIVI2','TSCA','ACPE','ACRU','ACSA3','AEFL',
                  'AMAR','BEAL','BELE','BENI','CACA18','CARCO','CARGL','CAROV','CARAL','CASDE','COFL2','FAGR','FAXI','FAPE','HADI','ILOP',
                  'JUNI','LIST2','LITU','MAAC','MAMA','NYSY','OXAR','PLOC','PRPE','PRSE','QULA2','QUCO2','QUFA','QUPR2','QURU','QUST',
                  'LIST2','LITU',"OXAR","TIAM","TIAM2")

write.csv(Output,paste(w_dir,"New_Sorensons_Similarity_Practice.csv",sep=""))
Output<-read.csv(paste(w_dir,"New_Sorensons_Similarity_Practice.csv",sep=""))

```



```{r,eval=FALSE}
###Check for plots that are assigned, more than one index. 
NewOutput<-Output[!duplicated(Output$cell),]
NewOutput<-NewOutput[,-1]
###Return the ZeroCells
zeroscells<-as.data.frame(zeros$Cell)
zeroscellsPLT_CN=0
zeroscellsx<-0
zeroscellsindex<-0
zerobind<-cbind(zeroscells,zeroscellsPLT_CN,zeroscellsindex)
colnames(zerobind)<-c("cell","Closestplot","indexscore")

Output2<-rbind(zerobind,NewOutput)
Output2<-Output2[order(Output2$cell,decreasing=FALSE),]
####
listofoccupied<-cr_bi$Cell
listoffinal<-Output2$cell
###Fill in any missing cells
missing<-listofoccupied[!(listofoccupied %in% Output2$cell)]
missingrow<-cbind(missing,"0","0")
colnames(missingrow)<-c("cell","Closestplot","indexscore")  
Output3<-rbind(Output2,missingrow)  
Output4<-Output3[order(as.numeric(Output3$cell),decreasing=FALSE),]
print(Output)

write.csv(Output4,paste(w_dir,"New_Sorensons_Similarity_Output_9_30.csv",sep=""))
write.csv(Log,paste(w_dir,"New_Sorensons_Similarity_log_9_30.csv",sep=""))
```


#### Method Comparison

Here we compared the four methods. 

```{r,include=FALSE, eval=FALSE,warning=FALSE}
#####
#####Here we load in and  compare our modeling methods. Sorenson's, Jaccard's, Curtis-Bray, Euclidian.
#####It compares these model outputs to the TW and FIA data 
#####ZR 2018


###Libraries#
  library(ggplot2)
  library(ggrepel)
  library(plyr)
  library(wesanderson)
  library(cowplot)
  library(raster)

###Color Setup 
  LtoM <-colorRampPalette(c('red', 'yellow' ))
  Mid <- "snow3"
  MtoH <-colorRampPalette(c('lightgreen', 'darkgreen'))
  MtoH2<-colorRampPalette(c('burlywood','cadetblue3'))
  LtoM2<-colorRampPalette(c('coral','chocolate'))

###Work Drives
w_dir<-"Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/Inputs"
setwd(w_dir)




#####Ty Wilson Imputations
clip_16 <- raster(paste(w_dir,"/Ty_wilson/Outputs/16_cut.tif",sep=""))
clip_97 <- raster(paste(w_dir,"/Ty_wilson/Outputs/97_cut.tif",sep=""))
clip_110 <- raster(paste(w_dir,"/Ty_wilson/Outputs/110_cut.tif",sep=""))
clip_123 <- raster(paste(w_dir,"/Ty_wilson/Outputs/123_cut.tif",sep=""))
clip_126 <- raster(paste(w_dir,"/Ty_wilson/Outputs/126_cut.tif",sep=""))
clip_129 <- raster(paste(w_dir,"/Ty_wilson/Outputs/129_cut.tif",sep=""))
clip_131 <- raster(paste(w_dir,"/Ty_wilson/Outputs/131_cut.tif",sep=""))
clip_132 <- raster(paste(w_dir,"/Ty_wilson/Outputs/132_cut.tif",sep=""))
clip_261 <- raster(paste(w_dir,"/Ty_wilson/Outputs/261_cut.tif",sep=""))
clip_315 <- raster(paste(w_dir,"/Ty_wilson/Outputs/315_cut.tif",sep=""))
clip_316 <- raster(paste(w_dir,"/Ty_wilson/Outputs/316_cut.tif",sep=""))
clip_318 <- raster(paste(w_dir,"/Ty_wilson/Outputs/318_cut.tif",sep=""))
clip_332 <- raster(paste(w_dir,"/Ty_wilson/Outputs/332_cut.tif",sep=""))
clip_356 <- raster(paste(w_dir,"/Ty_wilson/Outputs/356_cut.tif",sep=""))
clip_371 <- raster(paste(w_dir,"/Ty_wilson/Outputs/371_cut.tif",sep=""))
clip_372 <- raster(paste(w_dir,"/Ty_wilson/Outputs/372_cut.tif",sep=""))
clip_373 <- raster(paste(w_dir,"/Ty_wilson/Outputs/373_cut.tif",sep=""))
clip_402 <- raster(paste(w_dir,"/Ty_wilson/Outputs/402_cut.tif",sep=""))
clip_403 <- raster(paste(w_dir,"/Ty_wilson/Outputs/403_cut.tif",sep=""))
clip_407 <- raster(paste(w_dir,"/Ty_wilson/Outputs/407_cut.tif",sep=""))
clip_409 <- raster(paste(w_dir,"/Ty_wilson/Outputs/409_cut.tif",sep=""))
clip_491 <- raster(paste(w_dir,"/Ty_wilson/Outputs/491_cut.tif",sep=""))
clip_531 <- raster(paste(w_dir,"/Ty_wilson/Outputs/531_cut.tif",sep=""))
clip_541 <- raster(paste(w_dir,"/Ty_wilson/Outputs/541_cut.tif",sep=""))
clip_544 <- raster(paste(w_dir,"/Ty_wilson/Outputs/544_cut.tif",sep=""))
clip_581 <- raster(paste(w_dir,"/Ty_wilson/Outputs/581_cut.tif",sep=""))
clip_591 <- raster(paste(w_dir,"/Ty_wilson/Outputs/591_cut.tif",sep=""))
clip_602 <- raster(paste(w_dir,"/Ty_wilson/Outputs/602_cut.tif",sep=""))
clip_611 <- raster(paste(w_dir,"/Ty_wilson/Outputs/611_cut.tif",sep=""))
clip_621 <- raster(paste(w_dir,"/Ty_wilson/Outputs/621_cut.tif",sep=""))
clip_651 <- raster(paste(w_dir,"/Ty_wilson/Outputs/651_cut.tif",sep=""))
clip_655 <- raster(paste(w_dir,"/Ty_wilson/Outputs/655_cut.tif",sep=""))
clip_693 <- raster(paste(w_dir,"/Ty_wilson/Outputs/693_cut.tif",sep=""))
clip_711 <- raster(paste(w_dir,"/Ty_wilson/Outputs/711_cut.tif",sep=""))
clip_731 <- raster(paste(w_dir,"/Ty_wilson/Outputs/731_cut.tif",sep=""))
clip_761 <- raster(paste(w_dir,"/Ty_wilson/Outputs/761_cut.tif",sep=""))
clip_762 <- raster(paste(w_dir,"/Ty_wilson/Outputs/762_cut.tif",sep=""))
clip_802 <- raster(paste(w_dir,"/Ty_wilson/Outputs/802_cut.tif",sep=""))
clip_806 <- raster(paste(w_dir,"/Ty_wilson/Outputs/806_cut.tif",sep=""))
clip_812 <- raster(paste(w_dir,"/Ty_wilson/Outputs/812_cut.tif",sep=""))
clip_832 <- raster(paste(w_dir,"/Ty_wilson/Outputs/832_cut.tif",sep=""))
clip_833 <- raster(paste(w_dir,"/Ty_wilson/Outputs/833_cut.tif",sep=""))
clip_835 <- raster(paste(w_dir,"/Ty_wilson/Outputs/833_cut.tif",sep=""))
clip_837 <- raster(paste(w_dir,"/Ty_wilson/Outputs/837_cut.tif",sep=""))
clip_901 <- raster(paste(w_dir,"/Ty_wilson/Outputs/901_cut.tif",sep=""))
clip_931 <- raster(paste(w_dir,"/Ty_wilson/Outputs/931_cut.tif",sep=""))
clip_951 <- raster(paste(w_dir,"/Ty_wilson/Outputs/951_cut.tif",sep=""))
clip_952 <- raster(paste(w_dir,"/Ty_wilson/Outputs/952_cut.tif",sep=""))

# Stack the rasters
clip_stack<-stack(c(clip_16, clip_97, clip_110, clip_123 , clip_126,clip_129, clip_131, clip_132, clip_261, clip_315,
                    clip_316,clip_318,clip_332,clip_356,clip_371,clip_372,clip_373,clip_402,clip_403,clip_407,
                    clip_409,clip_491,clip_531,clip_541,clip_544,clip_581,clip_591,clip_602,clip_611,
                    clip_621,clip_651,clip_655,clip_693,clip_711,clip_731,clip_761,clip_762,clip_802,clip_806,clip_812,clip_832,clip_833,
                    clip_835,clip_837,clip_901,clip_931,clip_951,clip_952))

has.data = which(!is.na(getValues(max(clip_stack, na.rm=TRUE))))
N_hasdata<-length(has.data)
plot(clip_stack)
clip_stack_df <- as.data.frame(clip_stack)
rm(clip_16, clip_97, clip_110, clip_123 , clip_126,clip_129, clip_131, clip_132, clip_261, clip_315,
   clip_316,clip_318,clip_332,clip_356,clip_371,clip_372,clip_373,clip_391,clip_402,clip_403,clip_407,
   clip_409,clip_421,clip_491,clip_531,clip_541,clip_544,clip_581,clip_591,clip_602,clip_611,
   clip_621,clip_651,clip_655,clip_693,clip_711,clip_731,clip_761,clip_762,clip_802,clip_806,clip_812,clip_832,clip_833,
   clip_835,clip_837,clip_901,clip_931,clip_951,clip_952)
count1=as.data.frame(rowSums(clip_stack_df[,1:11]))
N_zeros_indataframe<-sum(is.na(count1))
N_zero_and_hasdata<-sum(N_zeros_indataframe,N_hasdata)




NumberofRaster<-nrow(clip_stack_df)

# Extract data for each cell of raster stack
cr <- extract(clip_stack, c(1: ncell(clip_stack)))
clip_ras_df <- as.data.frame(cr)

cr[is.na(cr[])] <- 0 # replace NA with zero




Marker<-as.data.frame(1:nrow(cr))
cr_bi <- cr
Sum<-rowSums(cr_bi)
cr_bi<-cbind(cr_bi,Sum)
Threshold=.05
Sumper=Sum*Threshold
cr_bi<-cbind(cr_bi,Sumper)
test1<-cr_bi[459415,]
cr_bi[cr_bi<Sumper]<-0
test2<-cr_bi[459415,]

cr_bi<-as.data.frame(cr_bi[,(-52)])
test1<-as.data.frame((cr_bi[459415,]))
cr_bi<-cbind(cr_bi,Marker)
colnames(cr_bi)<-c('16','97','110','123','126','129','131','132','261'
                   ,'315','316','318','332','356','371','372','373','402','403','407',
                   '409','491','531','541','544','581','591','602','611','621','651','655',
                   '693','711','731','761','762','802','806','812','832','833',
                   '835','837','901','931','951','952',"Sum","Cell")

SP<-c('16','97','110','123','126','129','131','132','261'
      ,'315','316','318','332','356','371','372','373','402','403','407',
      '409','491','531','541','544','581','591','602','611','621','651','655',
      '693','711','731','761','762','802','806','812','832','833',
      '835','837','901','931','951','952')
totalBa<-sum(cr_bi$Sum)

output<-NULL
###This creates a SUM BA for each species for comparison
for(i in SP){
 as<-cr_bi[,paste(i)]
 SumBA<-sum(as)
 PerBA<-SumBA/totalBa
 model<-("TW")
 row<-cbind(i,SumBA,PerBA,model)
 output<-rbind(row,output)
}
###This is the DataFrame With TyWilson Data
 TW<-output
 

 
 #####FIA######
wdir<-"Z:/Robbins/Sapps/Model_Prep/Initial_Communities/FIA_Sorter_Backup/"
setwd(wdir)
outdir<-"/FIA/FIA_Graphing"
IVIDATA<-read.csv(paste(wdir,"AOI_FIA_Plotdata.csv",sep=""))
Uniquespecies<-unique(IVIDATA$SPCD)
Tot_N_species<-length(Uniquespecies)        
LandscapeDF<-NULL
AllBA<-sum(IVIDATA$BA)

for(i in Uniquespecies){

  Block<-IVIDATA[IVIDATA$SPCD==i,]
  SumIVI<-sum(Block$IVI)
  SumBA<-sum(Block$BA)
  PercentTotal<-SumBA/AllBA
  Landscaperow<-cbind(i,SumIVI,SumBA,PercentTotal)
  LandscapeDF<-rbind(Landscaperow,LandscapeDF)
}
###The FIA_Data
FIA_Data<-data.frame(LandscapeDF)

###Switching Drives for the model outputs
####


wdir<-"Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/Inputs/"
setwd(wdir)

##CurtisBray###
###These are the same for each model
##They work by looking at the same system used in Mappingoutputs.R Look there for more intricate explanation

AgeGraphs<-read.csv(paste(wdir,"Outputs/Sapps_BC_AGE_TREE_HT_10_2.csv",sep=""))
Crosswalk<-read.csv(paste(wdir,"Outputs/IC_BC_Cleaned_10_1.csv",sep=""))#[,c("Cell","FIA_site")]
unique(AgeGraphs$calc_age_rounded)
Plts<-unique(AgeGraphs$PLT_CN)
output<-NULL
CBplots<-length(unique(Crosswalk$Closestplot))

BAperha<-(((AgeGraphs$DIA)^2)*.005454)*AgeGraphs$TPA_UNADJ

AgeGraphs$BAperha<-BAperha

output<-NULL
for(i in 1:length(Plts)){
  print(i)
  One<-as.data.frame(AgeGraphs[AgeGraphs$PLT_CN==Plts[i],])
  plt<-Plts[i]
  IC<-aggregate(round(One$CARBON_AG),by=list(SPCD=One$SPCD,AGE=as.numeric(One$calc_age_rounded),BAperha=One$BAperha),FUN=sum)
  IC$PLT_CN<-plt
  colnames(IC)<-c("SPCD","AGE","Basal_Area","AboveGround Carbon","PLT_CN")
  output<-rbind(IC,output)
}
unique(output$AGE)
sp<-unique(output$SPCD)

colnames(Crosswalk)<-c("x","Cell","PLT_CN","index")
uniquespps<-unique(output$SPCD)

One<-as.data.frame(output)
IC_under<-aggregate(One$Basal_Area,by=list(SPCD=One$SPCD,PLT_CN=One$PLT_CN),FUN=sum)

CellswithValues<-join(Crosswalk, IC_under, by="PLT_CN")
Sp<-unique(CellswithValues$SPCD)
print(Sp)
Sp<-Sp[!is.na(Sp)]
CellswithValues$SPCD[is.na(CellswithValues$SPCD)]<-0
colnames(CellswithValues)<-c("X","Cell","PLT_CN","Index","SPCD","BA")
totalBa<-sum(!is.na(CellswithValues$BA))

out<-NULL

for(i in Sp){
  
  SubCWV<-CellswithValues[CellswithValues$SPCD==i,]
  SumBA<-sum(SubCWV$BA)
  PercBA<-SumBA/totalBa
  row<-cbind(i,SumBA,PercBA)
  out<-rbind(row,out)
  }

CurtisBray<-as.data.frame(out)
totalBa<-sum(CurtisBray$SumBA)
CurtisBray$PercBA<-CurtisBray$SumBA/totalBa

###Euclidian Distance
AgeGraphs<-read.csv(paste(wdir,"Outputs/Sapps_Euclidian_FIA_AGE_TREE_HT_10_1.csv",sep=""))
Crosswalk<-read.csv(paste(wdir,"Outputs/Euclidian_DIST_Output_9_29.csv",sep=""))#[,c("Cell","FIA_site")]
unique(AgeGraphs$calc_age_rounded)
Plts<-unique(AgeGraphs$PLT_CN)
output<-NULL

EUplots<-length(unique(Crosswalk$Closestplot))


BAperha<-(((AgeGraphs$DIA)^2)*.005454)*AgeGraphs$TPA_UNADJ
AgeGraphs$BAperha<-BAperha

output<-NULL
for(i in 1:length(Plts)){
  print(i)
  One<-as.data.frame(AgeGraphs[AgeGraphs$PLT_CN==Plts[i],])
  plt<-Plts[i]
  IC<-aggregate(round(One$CARBON_AG),by=list(SPCD=One$SPCD,AGE=as.numeric(One$calc_age_rounded),BAperha=One$BAperha),FUN=sum)
  IC$PLT_CN<-plt
  colnames(IC)<-c("SPCD","AGE","Basal_Area","AboveGround Carbon","PLT_CN")
  output<-rbind(IC,output)
}
unique(output$AGE)
sp<-unique(output$SPCD)

colnames(Crosswalk)<-c("x","Cell","PLT_CN","index")
uniquespps<-unique(output$SPCD)
print(i)
One<-as.data.frame(output)
IC_under<-aggregate(One$Basal_Area,by=list(SPCD=One$SPCD,PLT_CN=One$PLT_CN),FUN=sum)
CellswithValues<-join(Crosswalk, IC_under, by="PLT_CN")
Sp<-unique(CellswithValues$SPCD)
Sp<-Sp[!is.na(Sp)]
CellswithValues$SPCD[is.na(CellswithValues$SPCD)]<-0
colnames(CellswithValues)<-c("X","Cell","PLT_CN","Index","SPCD","BA")
totalBa<-sum(!is.na(CellswithValues$BA))
out<-NULL
for(i in Sp){
  
  SubCWV<-CellswithValues[CellswithValues$SPCD==i,]
  SumBA<-sum(SubCWV$BA)
  PercBA<-SumBA/totalBa
  row<-cbind(i,SumBA,PercBA)
  out<-rbind(row,out)
}
EDist<-as.data.frame(out)
totalBa<-sum(EDist$SumBA)
EDist$PercBA<-EDist$SumBA/totalBa

###Jaccards#
AgeGraphs<-read.csv(paste(wdir,"Outputs/Sapps_Jorgy_FIA_AGE_TREE_HT_10_1.csv",sep=""))


Crosswalk<-read.csv(paste(wdir,"Outputs/Jaccards_Similarity_Output_9_30.csv",sep=""))#[,c("Cell","FIA_site")]
unique(AgeGraphs$calc_age_rounded)

JAplot<-length(unique(Crosswalk$Closestplot))
Plts<-(unique(AgeGraphs$PLT_CN))
BAperha<-(((AgeGraphs$DIA)^2)*.005454)*AgeGraphs$TPA_UNADJ
AgeGraphs$BAperha<-BAperha
print(BAperha)
max(BAperha)
min(BAperha)
output<-NULL
for(i in 1:length(Plts)){
  
  print(i)
  One<-as.data.frame(AgeGraphs[AgeGraphs$PLT_CN==Plts[i],])
  plt<-Plts[i]
  IC<-aggregate(round(One$CARBON_AG),by=list(SPCD=One$SPCD,AGE=as.numeric(One$calc_age_rounded),BAperha=One$BAperha),FUN=sum)
  IC$PLT_CN<-plt
  colnames(IC)<-c("SPCD","AGE","Basal_Area","AboveGround Carbon","PLT_CN")
  output<-rbind(IC,output)
}
unique(output$AGE)
sp<-unique(output$SPCD)
for(i in sp){
  dsa<-output[output$SPCD==i,]
  plot(dsa$`AboveGround Carbon`~dsa$AGE,main=i)
}

colnames(Crosswalk)<-c("x","Cell","PLT_CN","index")
uniquespps<-unique(output$SPCD)
print(i)
One<-as.data.frame(output)
IC_under<-aggregate(One$Basal_Area,by=list(SPCD=One$SPCD,PLT_CN=One$PLT_CN),FUN=sum)
CellswithValues<-join(Crosswalk, IC_under, by="PLT_CN")
Sp<-unique(CellswithValues$SPCD)
Sp<-Sp[!is.na(Sp)]
CellswithValues$SPCD[is.na(CellswithValues$SPCD)]<-0
colnames(CellswithValues)<-c("X","Cell","PLT_CN","Index","SPCD","BA")
totalBa<-sum(!is.na(CellswithValues$BA))
out<-NULL

for(i in Sp){
  
  SubCWV<-CellswithValues[CellswithValues$SPCD==i,]
  SumBA<-sum(SubCWV$BA)
  PercBA<-SumBA/totalBa
  row<-cbind(i,SumBA,PercBA)
  out<-rbind(row,out)
}

Jaccard<-as.data.frame(out[-49,])
totalBa<-sum(Jaccard$SumBA)
Jaccard$PercBA<-Jaccard$SumBA/totalBa

###SORENSEN
AgeGraphs<-read.csv(paste(wdir,"Outputs/Sapps_Sorenson's_FIA_AGE_TREE_HT_10_1.csv",sep=""))
Crosswalk<-read.csv(paste(wdir,"Outputs/New_Sorensons_Similarity_Output_9_30.csv",sep=""))#[,c("Cell","FIA_site")]
unique(AgeGraphs$calc_age_rounded)

SOplot<-length(unique(Crosswalk$Closestplot))
Plts<-(unique(AgeGraphs$PLT_CN))
BAperha<-(((AgeGraphs$DIA)^2)*.005454)*AgeGraphs$TPA_UNADJ
AgeGraphs$BAperha<-BAperha
print(BAperha)
max(BAperha)
min(BAperha)
output<-NULL

for(i in 1:length(Plts)){
  print(i)
  One<-as.data.frame(AgeGraphs[AgeGraphs$PLT_CN==Plts[i],])
  plt<-Plts[i]
  IC<-aggregate(round(One$CARBON_AG),by=list(SPCD=One$SPCD,AGE=as.numeric(One$calc_age_rounded),BAperha=One$BAperha),FUN=sum)
  IC$PLT_CN<-plt
  colnames(IC)<-c("SPCD","AGE","Basal_Area","AboveGround Carbon","PLT_CN")
  output<-rbind(IC,output)
}
unique(output$AGE)
sp<-unique(output$SPCD)
for(i in sp){
  dsa<-output[output$SPCD==i,]
  plot(dsa$`AboveGround Carbon`~dsa$AGE,main=i)
}

colnames(Crosswalk)<-c("x","Cell","PLT_CN","index")
uniquespps<-unique(output$SPCD)
print(i)
One<-as.data.frame(output)
IC_under<-aggregate(One$Basal_Area,by=list(SPCD=One$SPCD,PLT_CN=One$PLT_CN),FUN=sum)
CellswithValues<-join(Crosswalk, IC_under, by="PLT_CN")
Sp<-unique(CellswithValues$SPCD)
Sp<-Sp[!is.na(Sp)]
CellswithValues$SPCD[is.na(CellswithValues$SPCD)]<-0
colnames(CellswithValues)<-c("X","Cell","PLT_CN","Index","SPCD","BA")
totalBa<-sum(!is.na(CellswithValues$BA))
out<-NULL

for(i in Sp){
  
  SubCWV<-CellswithValues[CellswithValues$SPCD==i,]
  SumBA<-sum(SubCWV$BA)
  PercBA<-SumBA/totalBa
  row<-cbind(i,SumBA,PercBA)
  out<-rbind(row,out)
}

Sorensons<-as.data.frame(out[-49,])
totalBa<-sum(Sorensons$SumBA)
Sorensons$PercBA<-Sorensons$SumBA/totalBa




####Gathering Data together
SpeciesLUT<-read.csv("Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/Inputs/Inputs/SpeciesLUT.csv")

##names
Sorensons$model<-"Sorenson"
EDist$model<-"EDist"
Jaccard$model<-"Jaccard"
CurtisBray$model<-"BC"
FIA_Data$model<-"FIA"
FIA_Data<-FIA_Data[,c(-2)]

colnames(FIA_Data)<-c("i","SumBA","PercBA","model")
colnames(TW)<-c("i","SumBA","PercBA","model")
Alltogether<-as.data.frame(rbind(Jaccard,CurtisBray,FIA_Data,TW,EDist,Sorensons))
##Save for graphing
write.csv(Alltogether,paste(wdir,"Multi-model_comparison_10_30.csv",sep=""))
```


```{r fig.width=12.0, fig.height=11.0}



Alltogether<-read.csv("Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/Final_Materials/Meeting_10_20/Multi-model_comparison_10_30.csv")
                   

###create list of the top 20 species
shortsp<-c(129,132,261,316,372,621,711,802,806,833,832,693,901,403,837,131,110,126,409,371,531)
lesstogether<-Alltogether[Alltogether$i %in% shortsp,]

shorter<-lesstogether[order(lesstogether[,1],lesstogether[,2]),]
shorter$SumBA=round(as.numeric(shorter$SumBA,digits=2))
shorter$PercBA=as.numeric(shorter$PercBA)
shorter$percent=100*round(shorter$PercBA,digits=4)

###This might be appendix stuff. 


####Graphics
deltashorter<-NULL
for(sp in shortsp){
  Name<-SPLUT$LANDIS_CODE[SPLUT$Species==sp]
  ag=shorter[shorter$i==sp,]
  TWsum=ag$PercBA[ag$model=='TW']
  ag$deltaPerc=100*as.numeric(round(ag$PercBA-TWsum,digits=4))
  deltashorter=rbind(deltashorter,ag)
}



palette1="Royal1"

par(mfrow=c(2,6))
```



We looked at each method for its comparison of total basal area. All methods somewhat  overestimated the Basal area, with Sorensen's and 
Bray Curtis being the closest. 

```{r,fig.width=12,fig.height=10,message=FALSE,warning=FALSE}

library(plyr)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(plyr)
library(wesanderson)
library(cowplot)
library(raster)
library(ggplot2)
Out_dir<-"Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/Outputs/"
FIA_dir<-"Z:/Robbins/Sapps/Model_Prep/Initial_Communities/FIA_Sorter_Backup/"
IVIDATA<-read.csv(paste(FIA_dir,"AOI_FIA_Plotdata.csv",sep=""))

models<-unique(Alltogether$model)


CBsum<-round(as.numeric(sum(Alltogether$SumBA[Alltogether$model==models[2]])),digits=0)
TWsum<-round(sum(as.numeric(Alltogether$SumBA[209:256])),digits=0)
JACsum<-round(as.numeric(sum(Alltogether$SumBA[Alltogether$model==models[1]])),digits=0)
Edistsum<-round(round(as.numeric(sum(Alltogether$SumBA[Alltogether$model==models[5]])),digits=0),digits=0)
SOrrenSum<-round(as.numeric(sum(Alltogether$SumBA[Alltogether$model==models[6]])),digits=0)


SorrenSim<-read.csv(paste(Out_dir,"New_Sorensons_Similarity_Output_9_30.csv",sep=""))
SOplot<-length(unique(SorrenSim$Closestplot))
CBsim<-read.csv(paste(Out_dir,"Bray_Curtis_Output.csv",sep=""))
CBplots<-length(unique(CBsim$Closestplot))
Jacsim<-read.csv(paste(Out_dir,"Jaccards_Similarity_Output.csv",sep=""))
JAplot<-length(unique(Jacsim$Closestplot))
Edistsim<-read.csv(paste(Out_dir,"Euclidian_DIST_Output.csv",sep=""))
EUplots<-length(unique(Edistsim$Closestplot))
FIA_Over<-length(unique(IVIDATA$PLT_CN))

plots<-rbind(CBplots,FIA_Over,JAplot,EUplots,SOplot)
values<-rbind(CBsum,TWsum,JACsum,Edistsum,SOrrenSum)
#Plots<-rbind(CBplots,EUplots )
names<-rbind("BC","TW","JAC","EDist","Sorrenson")
thing<-as.data.frame(cbind(as.numeric(as.character(values)),names))
colnames(thing)<-c("values","names")



plot3<-ggplot(thing, aes(x=names,y=as.numeric(as.character(values))))+ 
  geom_bar(size = 2,stat = "identity",fill=wes_palette(n=5, name="Zissou1")) + 

  scale_color_manual(values = wes_palette(n=5, name="Zissou1"))+
  labs(fill = "# of cells")+
  theme_minimal()+
  theme(panel.grid.major.x=element_blank())+
  theme(text = element_text(size=20))+
  ggtitle(paste("Total Landscape Basal Area",sep=""))+
  xlab("")+ 
  ylab("ft/acre")
print(plot3)


FIA_Over<-length(unique(IVIDATA$PLT_CN))
plots<-rbind(CBplots,FIA_Over,JAplot,EUplots,SOplot)
names<-rbind("BC","FIA","JAC","EDist","Sorrens")
thing<-as.data.frame(cbind(as.numeric(as.character(plots)),names))
colnames(thing)<-c("plots","names")
```

This plot shows the number of FIA plots utilized in each analysis, with the FIA number being the total number in the evaluation. The Bray Curtis analysis utilized the most, with the Euclidian distance utilizing the least. 

```{r,fig.width=10,fig.height=6,message=FALSE}
plot4<-ggplot(thing, aes(x=names,y=as.numeric(as.character(plots))))+ 
  geom_bar(size = 2,stat = "identity",fill=wes_palette(n=5, name="Zissou1")) + 
  
  scale_color_manual(values = wes_palette(n=5, name="Zissou1"))+
  labs(fill = "# of cells")+
  theme_minimal()+
  theme(panel.grid.major.x=element_blank())+
  theme(text = element_text(size=20))+
  ggtitle(paste("Number of FIA plots",sep=""))+
  xlab("")+ 
  ylab("")

print(plot4)
```

This model prediction of assemblage is a comparison from the output to the FIA and Imputed data we have on species composition.
Because the associations select the least dissimilar plot, there is a possibility for the inclusion or exclusion of species in the
association. We find here the Sorensen's plots are the most accurate in terms of assemblage to both the FIA and imputed maps. 

```{r,fig.width=12,fig.height=6,message=FALSE}

colm<-NULL
SP<-SP[-1]

for(ij in SP){
OneSp<-Alltogether[Alltogether$i==ij,]
VarJACFIA<-(as.numeric(OneSp$PercBA[OneSp$model=="FIA"])-as.numeric(OneSp$PercBA[OneSp$model=="Jaccard"]))^2
VarJAcTW<-(as.numeric(OneSp$PercBA[OneSp$model=="TW"])-as.numeric(OneSp$PercBA[OneSp$model=="Jaccard"]))^2
BAJac<-(as.numeric(OneSp$SumBA[OneSp$model=="TW"])-as.numeric(OneSp$SumBA[OneSp$model=="Jaccard"]))^2
VarEDFIA<-(as.numeric(OneSp$PercBA[OneSp$model=="FIA"])-as.numeric(OneSp$PercBA[OneSp$model=="EDist"]))^2
VarEDTW<-(as.numeric(OneSp$PercBA[OneSp$model=="TW"])-as.numeric(OneSp$PercBA[OneSp$model=="EDist"]))^2
BAED<-(as.numeric(OneSp$SumBA[OneSp$model=="TW"])-as.numeric(OneSp$SumBA[OneSp$model=="EDist"]))^2
VarCBFIA<-(as.numeric(OneSp$PercBA[OneSp$model=="FIA"])-as.numeric(OneSp$PercBA[OneSp$model=="BC"]))^2
VarCBTW<-(as.numeric(OneSp$PercBA[OneSp$model=="TW"])-as.numeric(OneSp$PercBA[OneSp$model=="BC"]))^2
BACB<-(as.numeric(OneSp$SumBA[OneSp$model=="TW"])-as.numeric(OneSp$SumBA[OneSp$model=="BC"]))^2
VarSORFIA<-(as.numeric(OneSp$PercBA[OneSp$model=="FIA"])-as.numeric(OneSp$PercBA[OneSp$model=="Sorenson"]))^2
VarSORTW<-(as.numeric(OneSp$PercBA[OneSp$model=="TW"])-as.numeric(OneSp$PercBA[OneSp$model=="Sorenson"]))^2
BASOR<-(as.numeric(OneSp$SumBA[OneSp$model=="TW"])-as.numeric(OneSp$SumBA[OneSp$model=="Sorenson"]))^2

Row<-cbind(VarJACFIA,VarJAcTW,VarEDFIA,VarSORFIA,VarEDTW,VarCBFIA,VarCBTW,VarSORTW,BAJac,BAED,BACB,BASOR)
colm<-rbind(Row,colm)
}

colm<-as.data.frame(colm)
sumJACFIA<-sum(colm$VarJACFIA)^.5
sumJACTW<-sum(colm$VarJAcTW)^.5
sumEDFIA<-sum(colm$VarEDFIA)^.5
sumEDTW<-sum(colm$VarEDTW)^.5

sumCBFIA<-sum(colm$VarCBFIA)^.5
sumCBTW<-sum(colm$VarCBTW)^.5
sumSORTW<-sum(colm$VarSORTW)^.5
sumSORFIA<-sum(colm$VarSORFIA)^.5
sumBAJAC<-sum(colm$BAJac)^.5
sumBAED<-sum(colm$BAED)^.5
sumBAC<-sum(colm$BACB)^.5
sumBASOR<-sum(colm$BASOR)^.5
Comparison<-rbind(sumJACFIA,sumJACTW,sumEDFIA,sumEDTW,sumCBFIA,sumCBTW,sumSORFIA,sumSORTW)
Name<-rbind("JAC~FIA","JAC~TW","ED~FIA","ED~TW","BC~FIA","BC~TW","SOR~FIA","SOR~TW")
dfa<-as.data.frame(cbind(as.numeric(Comparison),Name))

colnames(dfa)<-c("Numbers","Names")
palette3<-"Darjeeling1"
plot3<-ggplot(dfa, aes(x=Names,y=as.numeric(as.character(Numbers))))+ 
  geom_bar(size = 2,stat = "identity",fill=rep(wes_palette(n=4, name=palette3),2)) + 
  scale_color_manual(values = wes_palette(n=4, name=palette3))+
  labs(fill = "# of cells")+
  theme_minimal()+
  theme(panel.grid.major.x=element_blank())+
  theme(text = element_text(size=20))+
  ggtitle(paste("Model prediction of assembledge",sep=""))+
  xlab("")+ 
  ylab("Sq. variance in species percentage")
print(plot3)
palette3<-"Chevalier1"

Comparison<-rbind(sumBAC,sumBAED,sumBAJAC,sumBASOR)
Name<-rbind("BC","ED","JAC","Sor")
dfa<-as.data.frame(cbind(as.numeric(Comparison),Name))
colnames(dfa)<-c("Numbers","Names")
```

In looking at each species estimated basal from the imputed maps, Sorenson's shows the least variation across the 50 species. 
In the end, we chose the Sorenson's association because it best represented the species assemblage, on a landscape that had many species. 


```{r,fig.width=6,fig.height=5,message=FALSE}
plot4<-ggplot(dfa, aes(x=Names,y=as.numeric(as.character(Numbers))))+ 
  geom_bar(size = 2,stat = "identity",fill=(wes_palette(n=4, name=palette3))) + 
  scale_color_manual(values = wes_palette(n=4, name=palette3))+
  labs(fill = "# of cells")+
  theme_minimal()+
  theme(panel.grid.major.x=element_blank())+
  theme(text = element_text(size=20))+
  ggtitle(paste("Sq variance in species BA",sep=""))+
  xlab("")+ 
  ylab("Variance in BA")
print(plot4)

```


#### Height Age and Site Index Association. 

Once we had the plots associated with each raster we used the values from FIA to get age and biomass,using to Carmean Hann, and Jacobs (1989) method to associate age with height and site index. 
In this method species has unique parameters to its growth curve, which is used with its height and site index to estimate its age. 

$AgeT=(1/c_3)*ln[1-\frac{HT}{c1*SI^{c2}}]^{(\frac{1}{c4})*(SI^{c5})}$

Citation: Carmean, W. H., Hahn, J. T., & Jacobs, R. D. (1989). Site index curves for forest tree species in the eastern United States. General Technical Report NC-128. St. Paul, MN: US Dept. of Agriculture, Forest Service, North Central Forest Experiment Station, 128.

This is used in combination with the allometric biomass for each tree from the FIA database to determine the biomass and age of each cohort.

```{r,warning=FALSE}
SPLUT<-read.csv("Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/Inputs/SpeciesLUT.csv")
library(knitr)
SP_print<-SPLUT[,c(2,4,7,8,9,10,11)]
colnames(SP_print)[2]<-c("Species Name")
kable(SP_print[c(0:10),],align=c('l'))

```



```{r,eval=FALSE}


options(scipen=999) #This removes scientific notation in printing. Plot CNs are very long
wdir<-"Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/"
setwd(wdir)



###Bring in the the Sorenson'sanalysis
Plotdata<-read.csv(paste(wdir,"Outputs/New_Sorensons_Similarity_Output_9_30.csv",sep=""))


ICcount<-unique(Plotdata$Closestplot)
print(length(ICcount))

###Load in plots in area
tree_data_all<-read.csv(paste(wdir,"Inputs/AOI_TREE.csv",sep=""))
length(unique(tree_data_all$PLT_CN))
tree_data_all[is.na(tree_data_all)]<-0
 
#Have to remove the trees that don't have height.  We need height to estimate age.
tree_data_HT<-subset(tree_data_all,tree_data_all[,'HT']>0)
length(unique(tree_data_HT$PLT_CN))
rm(NC_TREE,SC_TREE,VA_TREE,tree_data_all)


 
#Only use recent years
 years<-c(2004,2005, 2006, 2007, 2008, 2009,2010,2011,2012,2013,2014,2015,2016,2017)
 tree_data_SelectYears <- tree_data_HT[tree_data_HT$INVYR_x %in% years,]  
###Get Plots for years
 tree_data_SelectPlots <- tree_data_SelectYears[tree_data_SelectYears$PLT_CN %in% ICcount,]
 PLT_CN_unique_trees<-unique(tree_data_SelectPlots[,"PLT_CN"])
 print(length(PLT_CN_unique_trees))

#This loop selects just the 44 species of interest from all the species in the FIA plots. Ignores other species.
 spp_file<-read.csv(paste(wdir,"Inputs/SpeciesLUT.csv",sep=""))
 spp<-spp_file[,"Species"]
 number_of_species<-length(spp)
###just the species of intrest
 tree_data_SelectSpp <- tree_data_SelectPlots[tree_data_SelectPlots$SPCD %in% spp,]
 PLT_CN_unique_spp_vector<-(unique(tree_data_SelectSpp$PLT_CN))
 print(length(PLT_CN_unique_spp_vector))
###Remove excess
 rm(tree_data_SelectPlots, tree_data_SelectYears)

#Read in all the COND table csv files from FIA.  You need these to get stand age and site index.
 COND_NC<-read.csv(paste(wdir,"Inputs/NC_COND.csv",sep=""))
 COND_SC<-read.csv(paste(wdir,"Inputs/SC_COND.csv",sep=""))
 COND_TN<-read.csv(paste(wdir,"Inputs/TN_COND.csv",sep=""))
 COND_GA<-read.csv(paste(wdir,"Inputs/GA_COND.csv",sep=""))
 COND_all<-rbind(COND_NC, COND_SC,COND_TN,COND_GA)
 COND_only_years <- COND_all[COND_all$INVYR %in% years,]
 print(nrow(COND_only_years))

#Remove plots that are not forested.  COND class 1 is forested.
 COND_only_forests <- subset(COND_only_years, COND_only_years$COND_STATUS_CD==1) 
 print(nrow(COND_only_forests))

#Double-check to see how many PLT_CNs we lost in COND table.
 unique_PLTCN_COND<-length(unique(COND_only_years$PLT_CN))
 print(length(ICcount))
 print(unique_PLTCN_COND)

 check<-(tree_data_SelectSpp$PLT_CN %in%  unique_PLTCN_COND)

#########################
#Use this to fill in the missing data, i.e. avg site index for entire landscape.
 ForestwithIndex<-COND_only_forests[!is.na(COND_only_forests$SICOND),]
 average_Site_Condition<-round(mean(ForestwithIndex$SICOND), digits=)
  
###########################################
#Use this to calculate the average stand age and site index and fill in any missing data.
length( PLT_CN_unique_trees)
COND_matrix<-NULL
for (z in PLT_CN_unique_trees){#for each PLT_CN
  print(z)
  each_plot_subset <- subset(COND_only_forests, COND_only_forests[,"PLT_CN"] == z)
  number_plots<-nrow(each_plot_subset)
  stand_age_mean <- mean(each_plot_subset$STDAGE) #summing across cohort
  site_index_avg <- mean(each_plot_subset$SICOND) #summing across cohort
  if (number_plots==0){
    site_index_mean<-average_Site_Condition
  } else {
    site_index_mean<-site_index_avg
  }
  plot_matrix <- cbind(z, stand_age_mean, site_index_mean)
  colnames(plot_matrix)<-c("PLT_CN", "STDAGE_mean", "SICOND_mean")
  COND_matrix <- rbind(COND_matrix, plot_matrix)
}
COND_matrix<-as.data.frame(COND_matrix)
print(nrow(COND_matrix))
COND_matrix[,3][is.na(COND_matrix[,3])]<-average_Site_Condition
print(length(ICcount))

#Merge tree database and Condition Table database
 Merged_Tree_Cond<-merge(tree_data_SelectSpp, COND_matrix, "PLT_CN", by.y="PLT_CN")
 Merged_NAs_Trees<-Merged_Tree_Cond[!complete.cases(Merged_Tree_Cond),]
 Merged_Tree_Cond$PLT_CN
 colnames(Merged_Tree_Cond)[3]<-"INVYR"
 length(unique(Merged_Tree_Cond$PLT_CN))
#Double-check to see how many PLT_CNs we lost.
 unique_PLTCN_end_COND<-length(unique(Merged_Tree_Cond$PLT_CN))
 print("unique PLT_CNs was originally 279,055")
 print(unique_PLTCN_end_COND)
 
#Clear out memory before proceeding
 rm(COND_all, COND_only_years, COND_only_forests, COND_matrix, COND_NC, COND_SC, COND_GA,COND_TN) 
 
###########################################
 #####Read in Tree Files for infomation on stands
 NC_TREE <- read.csv(paste(wdir,"Inputs/NC_TREE.csv",sep="")) #load NC_Tree table
 SC_TREE <- read.csv(paste(wdir,"Inputs/SC_TREE.csv",sep="")) #load SC_Tree table
 GA_TREE <- read.csv(paste(wdir,"Inputs/GA_TREE.csv",sep=""))  #load VA_Tree table
 TN_TREE <- read.csv(paste(wdir,"Inputs/TN_TREE.csv",sep=""))  #load VA_Tree table
 TREEtbl_all <- rbind(NC_TREE, SC_TREE, GA_TREE,TN_TREE) 
 #####Get only the columns relevent PLT_CN,INVYR,PLOt,SUBP,TREE,CARBON_AG

 Shorter<-TREEtbl_all[,c(2,4,8,9,10,121)]
 

 withcarbon<-merge(Merged_Tree_Cond,Shorter, by=c("PLT_CN","INVYR","PLOT","SUBP","TREE"))
 colnames(TREEtbl_all)
 plot(withcarbon$CARBON_AG~withcarbon$DIA)
 Merged_Tree_Cond<-withcarbon

 tree_data_final<-subset(Merged_Tree_Cond,Merged_Tree_Cond[,"CARBON_AG"]>0) #& dta_all_sp[,"DIA"] > 0 
 rm(TREEtbl_all,NC_TREE,SC_TREE,TN_TREE,GA_TREE)
#Double-check to see how many PLT_CNs we lost in the merge.
  No_Biomass<-tree_data_final[!complete.cases(tree_data_final),]
  unique(No_Biomass$PLT_CN)
  length(unique(tree_data_final$PLT_CN))
###########################
#This is the loop to calculate age of all the trees.

roundUp <- function(x) 10*ceiling(x/10)   #Need to round the age to a multiple of 10.

age_added_matrix<-NULL#This will become new matrix with age added to matrix
for (each_tree in 1:nrow(tree_data_final)){#For every tree in the forested FIA plots in the state (which one is dependent on input file
  ###Here is a chapman Richards nonlinear functional form. This uses height Site index to determine age
  ### using 5 species specific perameters. We found ours in FVS lit. 
  print(each_tree)
  #print(dta_27_spp[each_tree,"each tree"])
  tree<-tree_data_final[each_tree,] #unique tree
  Plot<-tree["PLT_CN"]#Diameter (inches)
  H<-tree["HT"]#Height (ft)
  SIndex<-tree["SICOND_mean"]#Site index
  species<-tree["SPCD"]#species numeric code
  
  for (look in 1:nrow(spp_file)){
   #for every species in look up table
    sp_look<-spp_file[look,"Species"] #unique species number (from lookup table)
    if (sp_look==species){
      
      #age_matrix<-NULL
      #If lookup table species code is equal to tree species code, then...
        name<-(spp_file[look,"X"])#coefficient for b1
        final_spp_code<-(spp_file[look,"Species"])#coefficient for b1
        coef_b1<-(spp_file[look,"b1"])#coefficient for b1
        coef_b2<-(spp_file[look,"b2"])#coeffcient for b2
        coef_b3<-(spp_file[look,"b3"])#coeffcient for b3
        coef_b4<-(spp_file[look,"b4"])#coeffcient for b4
        coef_b5<-(spp_file[look,"b5"])#coeffcient for b5
        longevity<-(spp_file[look,"Longevity"])#longevity values
        if(H <= (coef_b1*SIndex^(coef_b2))) {
          age<-(log (1-(H/(coef_b1 * SIndex^(coef_b2)))^(1/(coef_b4*(SIndex^(coef_b5)))))/coef_b3)
        }
        else {age<-(log (1-(((coef_b1*SIndex^(coef_b2))-1)/(coef_b1 * SIndex^(coef_b2)))^(1/(coef_b4*(SIndex^(coef_b5)))))/coef_b3)
        }
        age<-as.matrix(age)
        colnames(age)<-c("age")
        
        age_rounded10_uncorrected <- roundUp(age)
        H
        (coef_b1*SIndex^(coef_b2))
        #age_rounded10<-round(age, digits=-1)
        
        if(age_rounded10_uncorrected > longevity) {
          age_rounded10<-longevity
        }
        else {age_rounded10<-age_rounded10_uncorrected
        }
        age_rounded10<-as.matrix(age_rounded10)
        colnames(age_rounded10)<-c("age_rounded10")
        
        } #closes loop around if statement for selected species.
    #colnames(age_matrix)<-c("calc_age", "calc_age_rounded")
    } #closes loop around lookup table
age_added_to_tree<-cbind.data.frame(tree,name, final_spp_code, age, age_rounded10) 
#colnames(age_added_to_tree)<-c("CommonName", "Final_spp_Code", "calc_age", "calc_age_rounded")
age_added_matrix<-rbind(age_added_matrix,age_added_to_tree)#row bind tree with calc_age to next row.  This is final matrix
}
age_added_matrix[age_added_matrix$SPCD=="835",]


print("Done with Final age matrix")
length(unique(age_added_matrix$PLT_CN))
colnames(age_added_matrix)<-c(colnames(tree), "CommonName", "Final_spp_Code", "calc_age", "calc_age_rounded")

write.csv(age_added_matrix,(paste(wdir,"Sapps_Sorenson's_FIA_AGE_TREE_HT_10_1.csv",sep="")))
```

To validate we compared the age distribution with that found in the FIA record.

These distribution were determined to be acceptable, though caution should be given in determining the demographics of
undersampled species like Prunus pensylvanica, Picea rubens, and Betula nigra. 


```{r,fig.height=10.0,fig.width=12.0,align="center",message=FALSE,warning=FALSE}
wdir<-"Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/Outputs/"
age_added_matrix<-read.csv(paste(wdir,"Sapps_Sorenson's_FIA_AGE_TREE_HT_10_1.csv",sep=""))

makeTransparent = function(..., alpha) {

  if(alpha<0 | alpha>1) stop("alpha must be between 0 and 1")

  alpha = floor(255*alpha)  
  newColor = col2rgb(col=unlist(list(...)), alpha=FALSE)

  .makeTransparent = function(col, alpha) {
    rgb(red=col[1], green=col[2], blue=col[3], alpha=alpha, maxColorValue=255)
  }

  newColor = apply(newColor, 2, .makeTransparent, alpha=alpha)

  return(newColor)

}

calc_age<-age_added_matrix[,"calc_age_rounded"]
stand_age<-age_added_matrix[,"STDAGE_mean"]
spec<-age_added_matrix[,"CommonName"]
dbh<-age_added_matrix[,"DIA"]

outliercolor<-makeTransparent("lightblue",alpha=.5)
par(mar = c(4,16,2,2))


boxplot(calc_age~spec, cex.axis=0.8, las=2,horizontal=TRUE,cex=1.0,pars=list(outcol=outliercolor),col="brown", main="Age Distribution")


```

Here is the distribution of DBH classes by species. 


```{r,,fig.height=10.0,fig.width=12.0,align="center"}
par(mar = c(4,17,2,2))

boxplot(dbh~spec, cex.axis=0.8, las=2,horizontal=TRUE,cex=1.0,col="brown", main="DBH Distribuion",pars=list(outcol="lightblue"))
pars=list(outcol="red")
```

Once assigned age to each stand  we used the FIA calculation of above ground carbon to estimate aboveground biomass. This is done by multiplying the above ground carbon by the FIA growing trees per acre multiplier(TPA_adj), convert it from ft2 per acre to g/m2 and multiply it by two to represent above ground biomass. 

We can then look at the distribution of age curves versus total carbon, our oaks and pines seem to be the most represented and also
have higher carbon values, we will have to be careful in our landscape runs to check how the sparse species persist on the landscape.


```{r,fig.height=10.0,fig.width=12.0,align="center",warning=FALSE}
#####
## This script makes maps from the Sorenson's and IC_2_get_age outputs
## it makes AGE and Carbon maps, as well as the IC.txt and Initial communities maps##
##
##ZR 2018

##Libraries and Drive
  library(plyr)
  library(dplyr)
  library(sp)
  library(raster); options(scipen=999) # scipen removes scientific notation from FIA data
  library(rgdal)
  library(plyr) #This removes scientific notation in printing. Plot CNs are very long
wdir<-"Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/Outputs"
setwd(wdir)

###The Output from IC 2 Get Age
AgeGraphs<-read.csv(paste(wdir,"/Sapps_Sorenson's_FIA_AGE_TREE_HT_10_1.csv",sep=""))

Plts<-unique(AgeGraphs$PLT_CN)

###Turn DIA to BA
BAperha<-(((AgeGraphs$DIA)^2)*.005454)*AgeGraphs$TPA_UNADJ
AgeGraphs$BAperha<-BAperha


output<-NULL
###This loop aggregates the FIA Plots Age and  Biomass by species in plts
for(i in 1:length(Plts)){

One<-as.data.frame(AgeGraphs[AgeGraphs$PLT_CN==Plts[i],])
plt<-Plts[i]
IC<-aggregate(round(One$CARBON_AG),by=list(SPCD=One$SPCD,AGE=as.numeric(One$calc_age_rounded),BAperha=One$BAperha),FUN=sum)
IC$PLT_CN<-plt
colnames(IC)<-c("SPCD","AGE","Basal_Area","AboveGround Carbon","PLT_CN")
output<-rbind(IC,output)
}


###Check the Carbon and Age ratios# Look at this agian 
sp<-unique(output$SPCD)
```


Here are the results of that association.

```{r,fig.height=10.0,fig.width=12.0,align="center",warning=FALSE}
par(mfrow=c(5,5))
for(i in sp){
dsa<-output[output$SPCD==i,]
Name<-as.character(SPLUT$LANDIS_CODE[SPLUT$Species==i])
plot(dsa$`AboveGround Carbon`~dsa$AGE,main=Name,xlab="Age",ylab="Carbon g",col="darkgreen")
}

```


```{r}
###altered carbon (gets rid of zeros)
output$`AboveGround Carbon`[output$`AboveGround Carbon`<10]<-10

####Read in crosswalk between rastercells and FIA plots
Crosswalk<-read.csv(paste(wdir,"/New_Sorensons_Similarity_Output_9_30.csv",sep=""))

colnames(Crosswalk)<-c("x","Cell","PLT_CN","index")

uniquespps<-unique(output$SPCD)
```




```{r, eval=FALSE}
#
TPA.factor <- 6.018046 #trees/acre adjust (TPA in FIA)
conv.factor <- .112085 #Convert from lbs/acre to g/m-2

#
#Creating Inital Communites
fia.cohort.plot<-AgeGraphs[,c(9,2,22,26)]

fia.cohort.plot$CARBON_AG<-round(fia.cohort.plot$CARBON_AG)*TPA.factor*conv.factor*2

#Remove round up to 20
fia.cohort.plot$CARBON_AG[fia.cohort.plot$CARBON_AG<=20]<-20

fia.cohort.plot <- fia.cohort.plot[complete.cases(fia.cohort.plot),]
###Bring in LUT with lanDiS Code names
SpeciesLUT<-read.csv(paste(wdir,"/SpeciesLUT.csv",sep=""))
colnames(SpeciesLUT)[2]<-"SPCD"
SpeciesLUT.merge<-SpeciesLUT[,c(2,13)]
##Merge Plots and and Species LUT
PLT_CN<-unique(fia.cohort.plot$PLT_CN)
fia.cohort.plot.with.names<-merge(fia.cohort.plot,SpeciesLUT.merge,by="SPCD")
MapCode<-as.numeric(1:length(PLT_CN))
mapcode.plots<-cbind(PLT_CN,MapCode)
###MapPlotcodemerge
fia.ic.merge <- merge(fia.cohort.plot.with.names, mapcode.plots, by = "PLT_CN")
fia.ic.merge<-fia.ic.merge[order(-fia.ic.merge$MapCode),]
fia.ic.merge<-as.data.frame(fia.ic.merge)
#carbon<-as.data.frame(fia.ic.merge$CARBON_AG*conv.factor)
###OutputFile
IC.output.file<-paste(wdir,"/IC_NULL_Github.txt",sep="")

###Conversion factors



####IC files text writing
Log<-NULL
for (l in 1:length(unique(fia.ic.merge$MapCode))){ ##Loop for individual mapcode

  ic.mapcode.select <- subset(fia.ic.merge, fia.ic.merge$MapCode==l)
  IC.mapcode <- noquote(paste("MapCode ", l)) 
  cat(NULL, file=IC.output.file, sep="\n", append=TRUE)#write blank space
  cat(IC.mapcode, file=IC.output.file, "\n", append=TRUE) #write  mapcode
  for (k in unique(ic.mapcode.select$LANDIS_CODE)) {##Loop for individual species
    
    ic.spp.select <- subset(ic.mapcode.select, ic.mapcode.select$LANDIS_CODE==k)
    ic.cohort.biomass.list <-NULL
    ic.spp.list<-NULL
    for (m in unique(ic.spp.select$calc_age_rounded)){
      ic.cohort.select <- subset(ic.spp.select, ic.spp.select$calc_age_rounded==m)
      ic.cohort.biomass.lbs <- as.numeric(sum(ic.cohort.select$CARBON_AG)) #converting to numeric     
      ic.cohort.biomass.gm.expand <- ic.cohort.biomass.lbs #(ic.cohort.biomass.lbs * TPA.factor) #applying expansion factor UPDATE
      ic.cohort.biomass.gm <- ic.cohort.biomass.gm.expand  #converting from lbs/acre to g m-2 
      ic.cohort.biomass <- paste(m, " (", round(ic.cohort.biomass.gm), ")", sep="")
      logrow<-cbind(k,m,ic.cohort.biomass.gm)
      Log<-rbind(Log,logrow)
      ic.cohort.biomass.list <- c(ic.cohort.biomass.list, ic.cohort.biomass)
      indent<-noquote("      ")
      ic.spp.list <- c(indent,k, ic.cohort.biomass.list)
      #cat(ic.cohort.biomass.list, file=IC.output.file, "\n", append=TRUE)
    }
    
    cat(ic.spp.list, file=IC.output.file, "\n", append=TRUE)
  }
}
library(knitr)
IC_in<-as.data.frame(read.csv(paste("Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/IC_NULL_Github.txt",sep=""),header=FALSE))
colnames(IC_in)<-c("Initial Community")
kable(IC_in[c(0:20),],caption="Species Names and FS numbers",align=c('l'))

```



##### Print the Initial Communites map. 

```{r,eval=FALSE}



###This is a log for analysis
write.csv(Log,paste(wdir,"/LogofIC.csv",sep=""))


####Writing the IC map#
MapcodeMap<-merge(CellswithValues,mapcode.plots,by="PLT_CN",all=TRUE)
MapcodeMap$MapCode[is.na(MapcodeMap$MapCode)]<-(-9999)
MapcodeMap2<-MapcodeMap[order(MapcodeMap$Cell),]
Plots<-MapcodeMap2$MapCode

###A Raster we want to write this like
ExampleRaster<-raster("Z:/Robbins/Sapps/Model_Prep/Initial_Communities/Ty_wilson_Backup/Outputs/110_cut.tif")
#proj<-projection(ExampleRaster)

codes_out_unlist <- as.numeric(Plots) 
length(codes_out_unlist)

output_matrix<-matrix(codes_out_unlist,nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) #fir
new_output_raster<-raster(output_matrix,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),ymx=ymax(ExampleRaster), crs=CRS("+init=EPSG:26917"))
#plot(new_output_raster)
new_output_file_name<-paste(wdir,"/InitialCommunities.img",sep="")
#pdf(paste(i,"outputIC.pdf",sep=""))

rast_IC_map<-writeRaster(new_output_raster, filename=new_output_file_name, datatype='FLT4S',overwrite=TRUE)#This will write a raster that should line up correctly with your input raster
new_output_raster[new_output_raster$layer==-9999]<-NA
plot(new_output_raster,main=paste("Intial Communities map"),box=FALSE,col=single_line_col)
#dev.off()
```


We can assign the basal area values from our association to look at some of the landscape features of our species. 


##### The Top Ten Species On The Landscape




```{r,fig.height=20.0,fig.width=14.0,align="center",message=FALSE}
TopTenSP<-c(832,316,621,129,711,806,132,802,833,261)
###Basal Area Maps

par(mar = c(1,1,2,2),mfrow=c(4,3))
adder<-NULL
AOI<-readOGR("Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/Inputs/Ty_wilson/Inputs/Dissolved_AOI.shp",verbose=FALSE)
ExampleRaster<-raster("Z:/Robbins/Sapps/Model_Prep/Initial_Communities/Ty_wilson_Backup/Outputs/110_cut.tif",sep="")

for(i in TopTenSP){
  Name<-as.character(SPLUT$LANDIS_CODE[SPLUT$Species==i])
  One<-as.data.frame(output[output$SPCD==i,])
  IC_under<-aggregate(One$Basal_Area,by=list(PLT_CN=One$PLT_CN),FUN=sum)
  CellswithValues<-join(Crosswalk, IC_under, by="PLT_CN")
  colnames(CellswithValues)<-c("X","Cell","PLT_CN","INDEX","MAX_AGE")
  CellswithValues[is.na(CellswithValues)]<-0
  
  Print<-CellswithValues[order(CellswithValues$Cell),]
  Plots<-as.numeric(CellswithValues$MAX_AGE)

  proj<-projection(ExampleRaster)
  codes_out_unlist <- Plots 
 
  ##maxage<-max(CellswithValues$MAX_AGE)
  
  output_matrix<-matrix(codes_out_unlist,nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) #fir
  new_output_raster<-raster(output_matrix,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),
                            ymx=ymax(ExampleRaster), crs=proj)
  plot(new_output_raster,main=paste(Name,"BA m2/ha ",sep=" "),axes=FALSE, box=FALSE,col=single_line_col, breaks=c(0,20,40,60,80,100) )
  plot(AOI,border="black",add=TRUE)

  breaks=c(0,20,40,60,80,100)
  
  new_output_file_name<-paste(wdir,"/Graphics/",i, "BAmaps.img",sep="")
 # tiff(paste(wdir,"Graphics/",i,"BA.tiff",sep=""),width=9,height=7,units='in',res=300)
  

}

```
 



#### Our total landscape basal area.


Here is our total landscape basal area. 


```{r, fig.height=7.0, fig.width= 7.0}

#### Total Basal Area 
  One<-as.data.frame(output)
  IC_under<-aggregate(One$Basal_Area,by=list(PLT_CN=One$PLT_CN),FUN=sum)
  CellswithValues<-join(Crosswalk, IC_under, by="PLT_CN")
  colnames(CellswithValues)<-c("X","Cell","PLT_CN","INDEX","MAX_AGE")
  CellswithValues[is.na(CellswithValues)]<-0
  
  Print<-CellswithValues[order(CellswithValues$Cell),]
  Plots<-as.numeric(CellswithValues$MAX_AGE)
  
  ExampleRaster<-raster(paste("Z:/Robbins/Sapps/Model_Prep/Initial_Communities/Ty_wilson_Backup/Outputs/110_cut.tif"))
  proj<-projection(ExampleRaster)
  codes_out_unlist <- Plots #unlist the attribute table so that the next step will become a double matrix.
  #Mmax(codes_out_unlist)
  #print(max(CellswithValues$MAX_AGE))
  #print(min(CellswithValues$MAX_AGE))
  maxage<-max(CellswithValues$MAX_AGE)
  
  output_matrix_SOR<-matrix(codes_out_unlist,nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) #fir
  
  new_output_raster_SOR<-raster(output_matrix_SOR,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),
                            ymx=ymax(ExampleRaster), crs=proj)
  
  new_output_file_name<-paste(wdir,"/Graphics/",i, "BAmaps.img",sep="")
 # tiff(paste(wdir,"Graphics/",i,"BA.tiff",sep=""),width=9,height=7,units='in',res=300)
  par(mar = c(1,1,2,2))
  plot(new_output_raster_SOR,main=paste("Total Landscape Basal Area",sep=""),axes=FALSE, box=FALSE,col=single_line_col)

```

We can see much of our spatial distribution is the same, however, we might have a less intense cluster around some  of the national
park areas in the center of the map.

In analyzing the difference in the basal area we can see there is an 11.5 % percent difference in total basal area, this must be taken
into account when assessing the initial conditions of the map, however, given that there is no empirical way to validate either method
of association this seems a reasonale amount of error.  


```{r, fig.height=7.0, fig.width= 7.0}
AOI<-readOGR("Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/Inputs/Ty_wilson/Inputs/Dissolved_AOI.shp",verbose=FALSE)
cr_bi_df<-as.data.frame(cr_bi)
#display.brewer.all()
  raster_col<-brewer.pal(6,"YlGnBu")
  codes_out_unlist <- cr_bi[,51]

  output_matrix_TY<-matrix(codes_out_unlist,nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) #fir
  new_output_raster_TY<-raster(output_matrix_TY,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),ymx=ymax(ExampleRaster),crs=proj)
  
  #new_output_file_name<-paste(wdir,"/Graphics/",i, "BAmaps.img",sep="")
 # tiff(paste(wdir,"Graphics/",i,"BA.tiff",sep=""),width=9,height=7,units='in',res=300)
  
   plot(new_output_raster_TY,main=paste("Total Landscape Basal Area",sep=""),axes=FALSE, box=FALSE,col=single_line_col)
 
```



Here we look at the total differnce on the landscape. 

```{r}
Tba_Sor<-sum(as.data.frame(new_output_raster_SOR$layer))

Tba_TY<-totalBa

print(paste("Basal Area on our landscape",Tba_Sor))
print(paste("Basal Area according to Ty Wilson",Tba_TY))
print(paste("This is a",(round((Tba_TY-Tba_Sor)/Tba_Sor,digits=4)*100),"% difference"))

```

Here is a map looking at which areas the basal areas diverge in negative values indicate where we underestimate the imputation maps, 


```{r,fig.height=10}


#new_output_file_name<-paste(wdir,"/Graphics/",i, "BAmaps.img",sep="")
 # tiff(paste(wdir,"Graphics/",i,"BA.tiff",sep=""),width=9,height=7,units='in',res=300)
new_output_raster<-(new_output_raster_SOR- new_output_raster_TY )
new_output_raster[new_output_raster[] ==0 ] <- NA  
par(mar = c(1,1,2,2))
plot(new_output_raster,main=paste("Divergent Basal Area g/m2",sep=""),axes=FALSE, box=FALSE,col=raster_col)
plot(AOI,border="black",add=TRUE)
```


We can also look at the above ground biomass for our most prevalent species and the total carbon on the landscape. 


```{r,fig.height=20.0,fig.width=14.0,align="center",message=FALSE,warning=FALSE}
### Carbon Maps
par(mar = c(1,1,2,2),mfrow=c(4,3))
adder<-NULL
AOI<-readOGR("Z:/Robbins/Sapps/Model_Prep/sAppsIC_Active/Inputs/Ty_wilson/Inputs/Dissolved_AOI.shp",verbose=FALSE)
ExampleRaster<-raster("Z:/Robbins/Sapps/Model_Prep/Initial_Communities/Ty_wilson_Backup/Outputs/110_cut.tif",sep="")
for(i in TopTenSP){
  
  One<-as.data.frame(output[output$SPCD==i,])
  IC_under<-aggregate(One$`AboveGround Carbon`,by=list(PLT_CN=One$PLT_CN),FUN=sum)
  CellswithValues<-join(Crosswalk, IC_under, by="PLT_CN")
  colnames(CellswithValues)<-c("X","Cell","PLT_CN","INDEX","Carbon")
  CellswithValues[is.na(CellswithValues)]<-0
  Print<-CellswithValues[order(CellswithValues$Cell),]
  Plots<-CellswithValues$Carbon

  proj<-projection(ExampleRaster)
  codes_out_unlist <- as.numeric(Plots)
  output_matrix<-matrix(codes_out_unlist,nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) #fir
  
  new_output_raster<-raster(output_matrix,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),ymx=ymax(ExampleRaster), crs=proj)
 
  
  #new_output_file_name<-paste(wdir,i, "PRACITCEEMaxage.",sep="")
  #tiff(paste(wdir,"/Graphics/",i,"AB_CARBBON.tiff",sep=""),width=9,height=7,units='in',res=300)
  plot(new_output_raster,main=paste("AB_Carbon",i,sep="   "),axes=FALSE, box=FALSE,col=single_line_col,breaks=c(0,200,2000,4000,6000,8000,10000,14000),bg="black"  )
  plot(AOI,border="white",add=TRUE)
  #dev.off()
}

```



Here we can also see the total above carbon ground on the landscape.

```{r}
#### Total Landscape Carbon
  One<-as.data.frame(output)
  IC_under<-aggregate(One$`AboveGround Carbon`,by=list(PLT_CN=One$PLT_CN),FUN=sum)
  CellswithValues<-join(Crosswalk, IC_under, by="PLT_CN")
  colnames(CellswithValues)<-c("X","Cell","PLT_CN","INDEX","MAX_AGE")
  CellswithValues[is.na(CellswithValues)]<-0
  
  Print<-CellswithValues[order(CellswithValues$Cell),]
  Plots<-as.numeric(CellswithValues$MAX_AGE)
  
  ExampleRaster<-raster(paste("Z:/Robbins/Sapps/Model_Prep/Initial_Communities/Ty_wilson_Backup/Outputs/110_cut.tif"))
  proj<-projection(ExampleRaster)
  codes_out_unlist <- Plots #unlist the attribute table so that the next step will become a double matrix.
  #Mmax(codes_out_unlist)
  #print(max(CellswithValues$MAX_AGE))
  #print(min(CellswithValues$MAX_AGE))
  maxage<-max(CellswithValues$MAX_AGE)
  
  output_matrix<-matrix(codes_out_unlist,nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) #fir
  new_output_raster<-raster(output_matrix,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),ymx=ymax(ExampleRaster), crs=proj)
  
  new_output_file_name<-paste(wdir,"/Graphics/",i, "BAmaps.img",sep="")
 # tiff(paste(wdir,"Graphics/",i,"BA.tiff",sep=""),width=9,height=7,units='in',res=300)
  
  plot(new_output_raster,main=paste("Total Carbon g/m2",sep=""),axes=FALSE, box=FALSE,col=single_line_col)
  
```

##### Appendix

A) 
Individual species association by similarity index

This is the comparison of each species in each method to its values in FIA, and the imputation maps. 

```{r}
#Individual Species association by similarity index
for(asds in shortsp){
Name<-as.character(SPLUT$LANDIS_CODE[SPLUT$Species==asds])

Onesp<-deltashorter[deltashorter$i==asds,]
Onesp$SumBA=round(as.numeric(Onesp$SumBA,digits=2))
Onesp$PercBA=as.numeric(Onesp$PercBA)
Onesp$percent=100*round(Onesp$PercBA,digits=4)
Onesp<-as.data.frame(Onesp)
Onesp$model<-(Onesp$model)
plot1<-ggplot(Onesp, aes(x=model,y=Onesp$percent))+ 
  geom_bar(size = 2,stat = "identity",fill=rep(wes_palette(n=3, name=palette1),2)) + 
  scale_color_manual(values = wes_palette(n=3, name=palette1),2)+
  labs(fill = "# of cells")+
  theme_minimal()+
  theme(panel.grid.major.x=element_blank())+
  theme(text = element_text(size=10))+
  ggtitle(paste("Percent of landscape ",Name,sep=" "))+
  xlab("")+ 
  ylab("Percent")+
  geom_label_repel(aes(label=(round(Onesp$percent,digits=4)),vjust=1.0))


palette2="IsleofDogs2"

plot2<-ggplot(Onesp, aes(x=model,y=Onesp$SumBA))+ 
    geom_bar(size = 2,stat = "identity",fill=rep(wes_palette(n=3, name=palette2),2)) + 
    scale_color_manual(values = wes_palette(n=3, name=palette2),2)+
    labs(fill = "# of cells")+
    theme_minimal()+
    theme(panel.grid.major.x=element_blank())+
    theme(text = element_text(size=10))+
    ggtitle(paste("Basal Area ",Name,sep=" "))+
    xlab("")+ 
    ylab("Ba ft2/acre")+
    geom_label_repel(aes(label=(round(Onesp$SumBA,digits=4)),vjust=1.0))



print(plot_grid(plot1,plot2))
}

```



