---
title: "Climate Model PET"
author: "Zachary Robbins"
date: "2/9/2020"
output: github_document
    
---
```{r,echo=FALSE}
knitr::opts_chunk$set(echo=F,warning = F)

```

```{r library}
Data_dir<-("Z:/Robbins/Sapps/Chapter3/Code/Landscape_Fire_Paper/Climate_Section_Paper/")
library(dplyr)
library(lubridate)
library(RColorBrewer)
library(scales)
###Color pallette
Color3<-brewer.pal(10,"Paired")
```

#### Defining the PET function 

```{r,Thornwaite,echo=TRUE}
ThornwaitePET<-function(Tmax,Tmin){
    ### Calculate the Temperature mean 
    
    Tmean<-(Tmax+Tmin)/2
    ### Set up the data 
    Temp<-data.frame(Dates=as.Date(TmaxAOI85$Timestep),Temps=Tmean)
    colnames(Temp)<-c("Dates","Temps")
    MonthlyMean<-Temp %>% 
      group_by(month=floor_date(Dates, "month")) %>%
      dplyr::summarize(amoun=mean(Temps,na.rm = T))
    
    #MonthlyMean$amoun[is.na(MonthlyMean$amoun)]
    ### Heat index i = (t/5)**1.514
    mm<-as.matrix(MonthlyMean[2])
    mm[mm<0,]<-0
    MonthlyMean$amoun<-mm
    Heatindex<-(mm/5)**1.514
    #Heatindex[is.na(Heatindex),]<-mean(Heatindex,na.rm=T)
    Datai<-data.frame(Date=MonthlyMean[1],hi=Heatindex)
    ### I is equal to the sum of i over each month 
    Output<-Datai %>%
      group_by(Year=floor_date(month,"year"))%>%
      dplyr::summarize(amount=sum(amoun))
    Output$Year<-year(Output$Year)
    
    ### Get the years for monthly means 
    MonthlyMean$Year<-year(MonthlyMean$month)
    
    merged<-merge(MonthlyMean,Output,by="Year")
    merged[is.na(merged)]
    ###Isolate back out the variables 
    i=merged$amoun
    I=merged$amount
    ###Alpha
    alpha=(6.75*10**-7)*(I**3)-(7.71*(10**-5)*(I**2))+(1.792*10**-2)*I+0.49239
    alpha[is.na(alpha)]
    ### Final uncorrected equation
    PETnon_corrected<-16*((10*i)/I)**alpha
    
    d<-PETnon_corrected[is.na(PETnon_corrected)]
    ##mm/month
    PET_df<-data.frame(date=merged$month,PET=PETnon_corrected)
    
    PET_df$Month<-month(PET_df$date)
    PET_df<-PET_df[PET_df$Month%in% c(5,6,7,8,9,10),]
    PET_df<-PET_df[-3]
    colnames(PET_df)<-c("date","PET")
    ### Agg to year 
    Yearly<-PET_df %>%
      group_by(Year=floor_date(date,"year"))%>%
      dplyr::summarize(amount=sum(PET,na.rm=T))
    return(Yearly)
}
```

We start with the climate files we have processed for each of the rcp 8.5 climate
models availble from MACA. 

This is minimum temperature, maximum temperature and pecipitation. 


```{r pressure, echo=FALSE}
TmaxAOI85<-read.csv(paste0(Data_dir,"outputs/Processed/AOI_Tmax_85.csv"),stringsAsFactors = F)
TmaxAOI85<-na.omit(TmaxAOI85)
TminAOI85<-read.csv(paste0(Data_dir,"outputs/Processed/AOI_Tmin_85.csv"),stringsAsFactors = F)
TminAOI85<-na.omit(TminAOI85)
PAOI85<-read.csv(paste0(Data_dir,"outputs/Processed/AOI_PPT_85.csv"),stringsAsFactors = F)
PAOI85<-na.omit(PAOI85)
```

#### Candidate Climate models 

Here are those models 

```{r}
modelnames<-colnames(TmaxAOI85)[c(-1,-2)]
modelnames2<-colnames(TminAOI85)[c(-1,-2)]
modelnames<-modelnames2[modelnames2 %in% modelnames]
print(modelnames)
```

Temp to daily mean 
```{r}
t=1
AllModels<-NULL
for(model in modelnames){
  print(model)
  Tmax<-(TmaxAOI85[model])
  Tmin<-TminAOI85[model]
  Tmean<-(Tmax+Tmin)/2
  Oneyear<-cbind(TmaxAOI85[,2],Tmean)
  colnames(Oneyear)<-c("Date","Model")
  Oneyear<-Oneyear%>%
    mutate(Year=year(Date))%>%
    group_by(Year)%>%
    dplyr::summarise(mean=mean(Model))
  #print(Oneyear)
  colnames(Oneyear)<-c("Year",model)
  if(t==1){
  AllModels<-Oneyear
  t<-t+1
  }else{
   
    colnames(AllModels)[1]<-"Year"
    AllModels<-merge(AllModels,Oneyear,by="Year")
  }
}

```

```{r}
print(lm(AllModels$HadGEM2.ES365_rcp85~seq(1:length(AllModels$HadGEM2.ES365_rcp85))))
print(lm(AllModels$IPSL.CM5A.MR_rcp85~seq(1:length(AllModels$HadGEM2.ES365_rcp85))))
print(lm(AllModels$MRI.CGCM3_rcp85~seq(1:length(AllModels$HadGEM2.ES365_rcp85))))
print(lm(AllModels$CNRM.CM5_rcp85~seq(1:length(AllModels$HadGEM2.ES365_rcp85))))
```


#### Calculate PET function from Tmean for each model: (Tmax+Tmin)/2

We then evaluate the Thornwaite model for PET using the T mean. 

Each model is shown as calculated PET for the follow steps. 

```{r}

```

```{r,fig.width=20.0,fig.height=20.0}
t<-1

for(model in modelnames){
  #print(model)
  Tmax<-(TmaxAOI85[model])
  Tmin<-TminAOI85[model]
  Oneyear<-ThornwaitePET(Tmax = Tmax,Tmin=Tmin)
  colnames(Oneyear)<-c("Year",model)
  if(t==1){
  AllModels<-Oneyear
  t<-t+1
  }else{
   
    colnames(AllModels)[1]<-"Year"
    AllModels<-merge(AllModels,Oneyear,by="Year")
  }
}

#AllModels
par(mfrow=c(2,2),mar=c(5.1, 5.1, 4.1, 2.1))
plot(as.Date(AllModels$Year),AllModels$bcc.csm1.1.m_rcp85,col=Color3[1],type="l",lwd=2.0,ylim=c(400,1200),cex.axis=2.0,cex.lab=1.8,
     ylab="PET mm/year",xlab="Year")
lines(as.Date(AllModels$Year),AllModels$bcc.csm1.1_rcp85,col=Color3[1],lwd=2.0)
lines(as.Date(AllModels$Year),AllModels$BNU.ESM_rcp85,col=Color3[3],lwd=2.0)
plot(as.Date(AllModels$Year),AllModels$CanESM2_rcp85,col=Color3[4],lwd=2.0,type="l",ylim=c(400,1200),cex.axis=2.0,cex.lab=1.8,
     ylab="PET mm/year",xlab="Year")
lines(as.Date(AllModels$Year),AllModels$CCSM4_rcp85,col=Color3[5],lwd=2.0)
lines(as.Date(AllModels$Year),AllModels$CNRM.CM5_rcp85,col=Color3[6],lwd=2.0)
lines(as.Date(AllModels$Year),AllModels$CSIRO.Mk3.6.0_rcp85,col=Color3[7],lwd=2.0)
plot(as.Date(AllModels$Year),AllModels$GFDL.ESM2G_rcp85,col=Color3[8],lwd=2.0,type="l",ylim=c(400,1200),cex.axis=2.0,cex.lab=1.8,
     ylab="PET mm/year",xlab="Year")
lines(as.Date(AllModels$Year),AllModels$GFDL.ESM2M_rcp85,col=Color3[9],lwd=2.0)
lines(as.Date(AllModels$Year),AllModels$HadGEM2.CC365_rcp85,col=Color3[10],lwd=2.0)
plot(as.Date(AllModels$Year),AllModels$MIROC5_rcp85,type="n",axes=F,xlab=NA,ylab=NA)
legend(as.Date(AllModels$Year)[1],750,legend=c(modelnames),col=c(Color3,Color3[1:10]),
       lty=c(1,1,1,1,1,1,1,1,1,1,4,4,4,4,4,4,4,4,4,4),lwd=c(4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4),cex=2.0)
plot(as.Date(AllModels$Year),AllModels$HadGEM2.ES365_rcp85,col=Color3[1],lty=4,lwd=2.0,type="l",ylim=c(400,1200),cex.axis=2.0,cex.lab=1.8,
     ylab="PET mm/year",xlab="Year")
lines(as.Date(AllModels$Year),AllModels$inmcm4_rcp85,col=Color3[2],lty=4,lwd=2.0)
lines(as.Date(AllModels$Year),AllModels$IPSL.CM5A.LR_rcp85,col=Color3[3],lty=4,lwd=2.0)
lines(as.Date(AllModels$Year),AllModels$IPSL.CM5A.MR_rcp85,col=Color3[4],lty=4,lwd=2.0)
plot(as.Date(AllModels$Year),AllModels$IPSL.CM5B.LR_rcp85,col=Color3[5],type="l",lty=4,lwd=2.0,ylim=c(400,1200),cex.axis=2.0,cex.lab=1.8,
     ylab="PET mm/year",xlab="Year")
lines(as.Date(AllModels$Year),AllModels$MIROC.ESM.CHEM_rcp85,col=Color3[6],lty=4,lwd=2.0)
lines(as.Date(AllModels$Year),AllModels$MIROC.ESM_rcp85,col=Color3[7],lty=4,lwd=2.0)
plot(as.Date(AllModels$Year),AllModels$MRI.CGCM3_rcp85,col=Color3[8],lty=4,lwd=2.0,type="l",ylim=c(400,1200),cex.axis=2.0,cex.lab=1.8,
     ylab="PET mm/year",xlab="Year")
lines(as.Date(AllModels$Year),AllModels$NorESM1.M_rcp85,col=Color3[9],lty=4,lwd=2.0)
lines(as.Date(AllModels$Year),AllModels$MIROC5_rcp85,col=Color3[10],lty=4,lwd=2.0)
plot(as.Date(AllModels$Year),AllModels$MIROC5_rcp85,type="n",axes=F,xlab=NA,ylab=NA)
legend(as.Date(AllModels$Year)[1],750,legend=c(modelnames),col=c(Color3,Color3[1:10]),
       lty=c(1,1,1,1,1,1,1,1,1,1,4,4,4,4,4,4,4,4,4,4),lwd=c(4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4),cex=2.0)
```


```{r}
print(lm(AllModels$HadGEM2.CC365_rcp85 ~seq(1:length(AllModels$HadGEM2.ES365_rcp85))))

print(lm(AllModels$IPSL.CM5A.MR_rcp85~seq(1:length(AllModels$HadGEM2.ES365_rcp85))))
print(lm(AllModels$MRI.CGCM3_rcp85~seq(1:length(AllModels$HadGEM2.ES365_rcp85))))
print(lm(AllModels$CNRM.CM5_rcp85~seq(1:length(AllModels$HadGEM2.ES365_rcp85))))
```

#### Precipitation 

We also look at precipitation using the same models. 

```{r,fig.width=20.0,fig.height=20.0}
DFP<-AllModels$Year
for(model in modelnames){
  Precip<-PAOI85[model]
  PETone<-AllModels[model]
  Precip<-data.frame(Dates=as.Date(PAOI85$Timestep),Precip=Precip) 
  colnames(Precip)<-c("Dates","Precip")
  Outputs<-Precip %>% group_by(Year=floor_date(Dates,"month"))%>%
    dplyr::summarize(amount=sum(Precip,na.rm = T))
  Outputs$Month<-month(Outputs$Year)
  Outputs<-Outputs[Outputs$Month %in% c(5,6,7,8,9,10),]
  Outputs<-Outputs %>% group_by(Year=floor_date(Year,"year"))%>%
    dplyr::summarize(amount=sum(amount,na.rm = T))
  #Ratio<-Outputs$amount/PETone
  colnames(Outputs)[2]<-model
  DFP<-cbind(DFP,Outputs[model])
}


```

```{r,fig.width=20.0,fig.height=20.0}
#Plotting this
par(mfrow=c(2,2),mar=c(5.1, 5.1, 4.1, 2.1))
plot(AllModels$Year,DFP$bcc.csm1.1.m_rcp85,col=Color3[1],type="l",lwd=2.0,ylim=c(400,1500),cex.axis=2.0,cex.lab=1.8,
     ylab="PPT mm/year",xlab="Year")
lines(AllModels$Year,DFP$bcc.csm1.1_rcp85,col=Color3[1],lwd=2.0)
lines(AllModels$Year,DFP$BNU.ESM_rcp85,col=Color3[3],lwd=2.0)
plot(AllModels$Year,DFP$CanESM2_rcp85,col=Color3[4],lwd=2.0,type="l",ylim=c(400,1500),cex.axis=2.0,cex.lab=1.8,
     ylab="PPT mm/year",xlab="Year")
lines(AllModels$Year,DFP$CCSM4_rcp85,col=Color3[5],lwd=2.0)
lines(AllModels$Year,DFP$CNRM.CM5_rcp85,col=Color3[6],lwd=2.0)
lines(AllModels$Year,DFP$CSIRO.Mk3.6.0_rcp85,col=Color3[7],lwd=2.0)
plot(AllModels$Year,DFP$GFDL.ESM2G_rcp85,col=Color3[8],lwd=2.0,type="l",ylim=c(400,1500),cex.axis=2.0,cex.lab=1.8,
     ylab="PPT mm/year",xlab="Year")
lines(AllModels$Year,DFP$GFDL.ESM2M_rcp85,col=Color3[9],lwd=2.0)
lines(AllModels$Year,DFP$HadGEM2.CC365_rcp85,col=Color3[10],lwd=2.0)
plot(AllModels$Year,DFP$MIROC5_rcp85,type="n",axes=F,xlab=NA,ylab=NA)
legend(AllModels$Year[1],1200,legend=c(modelnames),col=c(Color3,Color3[1:10]),
       lty=c(1,1,1,1,1,1,1,1,1,1,4,4,4,4,4,4,4,4,4,4),lwd=c(4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4),cex=2.0)
plot(AllModels$Year,DFP$HadGEM2.ES365_rcp85,col=Color3[1],lty=4,lwd=2.0,type="l",ylim=c(400,1500),cex.axis=2.0,cex.lab=1.8,
     ylab="PPT mm/year",xlab="Year")
lines(AllModels$Year,DFP$inmcm4_rcp85,col=Color3[2],lty=4,lwd=2.0)
lines(AllModels$Year,DFP$IPSL.CM5A.LR_rcp85,col=Color3[3],lty=4,lwd=2.0)
lines(AllModels$Year,DFP$IPSL.CM5A.MR_rcp85,col=Color3[4],lty=4,lwd=2.0)


plot(AllModels$Year,DFP$IPSL.CM5B.LR_rcp85,col=Color3[5],type="l",lty=4,lwd=2.0,ylim=c(400,1500),cex.axis=2.0,cex.lab=1.8,
     ylab="PPT mm/year",xlab="Year")

lines(AllModels$Year,DFP$MIROC.ESM.CHEM_rcp85,col=Color3[6],lty=4,lwd=2.0)
lines(AllModels$Year,DFP$MIROC.ESM_rcp85,col=Color3[7],lty=4,lwd=2.0)
plot(AllModels$Year,DFP$MRI.CGCM3_rcp85,col=Color3[8],lty=4,lwd=2.0,type="l",ylim=c(400,1500),cex.axis=2.0,cex.lab=1.8,
     ylab="PPT mm/year",xlab="Year")
lines(as.Date(AllModels$Year),DFP$NorESM1.M_rcp85,col=Color3[9],lty=4,lwd=2.0)
lines(as.Date(AllModels$Year),DFP$MIROC5_rcp85,col=Color3[10],lty=4,lwd=2.0)
plot(as.Date(AllModels$Year),DFP$MIROC5_rcp85,type="n",axes=F,xlab=NA,ylab=NA)
legend(as.Date(AllModels$Year)[1],1200,legend=c(modelnames),col=c(Color3,Color3[1:10]),
       lty=c(1,1,1,1,1,1,1,1,1,1,4,4,4,4,4,4,4,4,4,4),lwd=c(4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4),cex=2.0)
```

Looking at the linear change

```{r}

print(lm(DFP$HadGEM2.ES365_rcp85~seq(1:length(AllModels$HadGEM2.ES365_rcp85))))
print(lm(DFP$IPSL.CM5A.MR_rcp85~seq(1:length(AllModels$HadGEM2.ES365_rcp85))))
print(lm(DFP$MRI.CGCM3_rcp85~seq(1:length(AllModels$HadGEM2.ES365_rcp85))))
print(lm(DFP$CNRM.CM5_rcp85~seq(1:length(AllModels$HadGEM2.ES365_rcp85))))


```


#### Ratio of PPT to PET over time 

To look at the patterns in drought over time we looked at the relationship between
PET and PPT over time

This is obviously simplified and does not account for PPT stored within
the system 

Not accounting for Runoff
Greater than 1 =Storage
1= PPT=PET
<1 = Water Deficit

```{r}
modelnames3<-colnames(PAOI85)[c(-1,-2)]
modelnames3<-modelnames[modelnames %in% modelnames3]

DF<-AllModels$Year


for(model in modelnames3){
  Precip<-PAOI85[model]
  PETone<-AllModels[model]
  Precip<-data.frame(Dates=as.Date(PAOI85$Timestep),Precip=Precip) 
  colnames(Precip)<-c("Dates","Precip")
  Outputs<-Precip %>% group_by(Year=floor_date(Dates,"year"))%>%
    summarize(amount=sum(Precip,na.rm = T))
  Ratio<-Outputs$amount/PETone
  DF<-cbind(DF,Ratio[model])
}

```


```{r,fig.width=20.0,fig.height=20.0}
par(mfrow=c(2,2),mar=c(5.1, 5.1, 4.1, 2.1))
plot(as.Date(AllModels$Year),DF$bcc.csm1.1.m_rcp85,col=Color3[1],type="l",lwd=2.0,ylim=c(1,3.5),cex.axis=2.0,cex.lab=1.8,
     ylab="Ratio of PPT to PET",xlab="Year")
lines(as.Date(AllModels$Year),DF$bcc.csm1.1_rcp85,col=Color3[1],lwd=2.0)
lines(as.Date(AllModels$Year),DF$BNU.ESM_rcp85,col=Color3[3],lwd=2.0)
plot(as.Date(AllModels$Year),DF$CanESM2_rcp85,col=Color3[4],lwd=2.0,type="l",ylim=c(1,3.5),cex.axis=2.0,cex.lab=1.8,
     ylab="Ratio of PPT to PET",xlab="Year")
lines(as.Date(AllModels$Year),DF$CCSM4_rcp85,col=Color3[5],lwd=2.0)
lines(as.Date(AllModels$Year),DF$CNRM.CM5_rcp85,col=Color3[6],lwd=2.0)
lines(as.Date(AllModels$Year),DF$CSIRO.Mk3.6.0_rcp85,col=Color3[7],lwd=2.0)
plot(as.Date(AllModels$Year),DF$GFDL.ESM2G_rcp85,col=Color3[8],lwd=2.0,type="l",ylim=c(1,3.5),cex.axis=2.0,cex.lab=1.8,
     ylab="Ratio of PPT to PET",xlab="Year")
lines(as.Date(AllModels$Year),DF$GFDL.ESM2M_rcp85,col=Color3[9],lwd=2.0)
lines(as.Date(AllModels$Year),DF$HadGEM2.CC365_rcp85,col=Color3[10],lwd=2.0)
plot(as.Date(AllModels$Year),DF$MIROC5_rcp85,type="n",axes=F,xlab=NA,ylab=NA)
legend(as.Date(AllModels$Year)[1],3.8,legend=c(modelnames),col=c(Color3,Color3[1:10]),
       lty=c(1,1,1,1,1,1,1,1,1,1,4,4,4,4,4,4,4,4,4,4),lwd=c(4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4),cex=2.0)
plot(as.Date(AllModels$Year),DF$HadGEM2.ES365_rcp85,col=Color3[1],lty=4,lwd=2.0,type="l",ylim=c(1,3.5),cex.axis=2.0,cex.lab=1.8,
     ylab="Ratio of PPT to PET",xlab="Year")
lines(as.Date(AllModels$Year),DF$inmcm4_rcp85,col=Color3[2],lty=4,lwd=2.0)
lines(as.Date(AllModels$Year),DF$IPSL.CM5A.LR_rcp85,col=Color3[3],lty=4,lwd=2.0)
lines(as.Date(AllModels$Year),DF$IPSL.CM5A.MR_rcp85,col=Color3[4],lty=4,lwd=2.0)


plot(as.Date(AllModels$Year),DF$IPSL.CM5B.LR_rcp85,col=Color3[5],type="l",lty=4,lwd=2.0,ylim=c(1,3.5),cex.axis=2.0,cex.lab=1.8,
     ylab="Ratio of PPT to PET",xlab="Year")

lines(as.Date(AllModels$Year),DF$MIROC.ESM.CHEM_rcp85,col=Color3[6],lty=4,lwd=2.0)
lines(as.Date(AllModels$Year),DF$MIROC.ESM_rcp85,col=Color3[7],lty=4,lwd=2.0)
plot(as.Date(AllModels$Year),DF$MRI.CGCM3_rcp85,col=Color3[8],lty=4,lwd=2.0,type="l",ylim=c(1,3.5),cex.axis=2.0,cex.lab=1.8,
     ylab="Ratio of PPT to PET",xlab="Year")
lines(as.Date(AllModels$Year),DF$NorESM1.M_rcp85,col=Color3[9],lty=4,lwd=2.0)
lines(as.Date(AllModels$Year),DF$MIROC5_rcp85,col=Color3[10],lty=4,lwd=2.0)
plot(as.Date(AllModels$Year),DF$MIROC5_rcp85,type="n",axes=F,xlab=NA,ylab=NA)
legend(as.Date(AllModels$Year)[1],3.8,legend=c(modelnames),col=c(Color3,Color3[1:10]),
       lty=c(1,1,1,1,1,1,1,1,1,1,4,4,4,4,4,4,4,4,4,4),lwd=c(4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4),cex=2.0)
```

#### Linear models of PET/PPT 

Here we fit a linear regression to this relationship over time. 

```{r,fig.width=20.0,fig.height=20.0}
par(xpd=F)
par(mfrow=c(2,2),mar=c(5.1, 5.1, 4.1, 2.1))
plot(as.Date(AllModels$Year),DF$bcc.csm1.1.m_rcp85,type="n",ylim=c(1,3),cex.axis=2.0,cex.lab=1.8,
     ylab="Ratio of PPT/PET",xlab="Year")
abline(lm(DF$bcc.csm1.1.m_rcp85~AllModels$Year),col=Color3[1],lwd=2.0)
abline(lm(DF$bcc.csm1.1_rcp85~AllModels$Year),col=Color3[2],lwd=2.0)
abline(lm(DF$BNU.ESM_rcp85~AllModels$Year),col=Color3[3],lwd=2.0)
abline(lm(DF$CanESM2_rcp85~AllModels$Year),col=Color3[4],lwd=2.0)
abline(lm(DF$CCSM4_rcp85~AllModels$Year),col=Color3[5],lwd=2.0)
abline(lm(DF$CNRM.CM5_rcp85~AllModels$Year),col=Color3[6],lwd=2.0)
abline(lm(DF$CSIRO.Mk3.6.0_rcp85~AllModels$Year),col=Color3[7],lwd=2.0)
abline(lm(DF$GFDL.ESM2G_rcp85~AllModels$Year),col=Color3[8],lwd=2.0)
abline(lm(DF$GFDL.ESM2M_rcp85~AllModels$Year),col=Color3[9],lwd=2.0)
plot(as.Date(AllModels$Year),DF$bcc.csm1.1.m_rcp85,type="n",ylim=c(1,3),cex.axis=2.0,cex.lab=1.8,
     ylab="Ratio of PPT/PET",xlab="Year")
abline(lm(DF$HadGEM2.CC365_rcp85~AllModels$Year),col=Color3[10],lwd=2.0)
abline(lm(DF$HadGEM2.ES365_rcp85~AllModels$Year),col=Color3[1],lty=4,lwd=2.0)
abline(lm(DF$inmcm4_rcp85~AllModels$Year),col=Color3[2],lty=4,lwd=2.0)
#abline(lm(DF$X_bcc.csm1.1_r1~AllModels$Year),col=Color3[3],lty=4,lwd=2.0)
abline(lm(DF$IPSL.CM5A.LR_rcp85~AllModels$Year),col=Color3[3],lty=4,lwd=2.0)
abline(lm(DF$IPSL.CM5A.MR_rcp85~AllModels$Year),col=Color3[4],lty=4,lwd=2.0)
abline(lm(DF$IPSL.CM5B.LR_rcp85~AllModels$Year),col=Color3[5],lty=4,lwd=2.0)
abline(lm(DF$MIROC.ESM.CHEM_rcp85~AllModels$Year),col=Color3[6],lty=4,lwd=2.0)
abline(lm(DF$MIROC.ESM_rcp85~AllModels$Year),col=Color3[7],lty=4,lwd=2.0)
abline(lm(DF$MIROC5_rcp85~AllModels$Year),col=Color3[8],lty=4,lwd=2.0)
abline(lm(DF$MRI.CGCM3_rcp85~AllModels$Year),col=Color3[9],lty=4,lwd=2.0)
abline(lm(DF$NorESM1.M_rcp85~AllModels$Year),col=Color3[10],lty=4,lwd=2.0)


plot(as.Date(AllModels$Year),DF$MIROC5_rcp85,type="n",axes=F,xlab=NA,ylab=NA)
legend(as.Date(AllModels$Year)[1],3.2,legend=c(modelnames),col=c(Color3,Color3[1:10]),
       lty=c(1,1,1,1,1,1,1,1,1,1,4,4,4,4,4,4,4,4,4,4),lwd=c(4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4),cex=2.0)
```


#### Fixed intercept

here I fixed the intercept to the mean of the slopes, then compared the slopes. Note: This order is the same
whether you fix the slope or not. 

```{r,fig.width=10.0,fig.height=10.0}
### Looking at variation in slope 
#interse
model<-modelnames[1]
Slopes<-NULL
Models<-NULL
Ints<-NULL
for(model in modelnames){
Onemodel<-as.matrix(DF[model])
Onemodellm<-lm(Onemodel~ AllModels$Year)
#abline(Onemodellm)
Int<-Onemodellm$coefficients[1]
Slope<-Onemodellm$coefficients[2]
Models<-c(model,Models)
Slopes<-c(Slope,Slopes)
Ints<-c(Int,Ints)
}
mean(Ints)


Slopes<-NULL
Models<-NULL
for(model in modelnames){
Onemodel<-as.matrix(DF[model])
Onemodellm<-lm(Onemodel~0+AllModels$Year+offset(rep(3.165642,94)) )
Slope<-Onemodellm$coefficients[1]
Models<-c(model,Models)
Slopes<-c(Slope,Slopes)
}
combined<-as.data.frame(cbind(Models,Slopes))
colnames(combined)<-c("Models","Slopes")
combined$Slopes<-as.numeric(as.character(Slopes))
par(las=2) # make label text perpendicular to axis
par(mar=c(5,15,4,2))
barplot(combined$Slopes[order(combined$Slopes)],horiz=T,cex.names=1.2,names.arg =combined$Models[order(combined$Slopes)])

```

#### Here is the decadal means for the PPT/PET rato

```{r}

t<-1
###How to group by decade
for(model in modelnames3){
  #model=modelnames3[1]
  Ratio=DF[model]
  Yearly<-data.frame(Dates=DF$DF,Ratio=Ratio)
  colnames(Yearly)<-c("Dates","Ratio")
 # print(Yearly)
  Dec_Means<-Yearly %>% group_by(Year=floor_date(Dates,years(10)))%>%
    summarize(amount=mean(Ratio))
    #summarize(Variation=stats::var(Precip))
  colnames(Dec_Means)<-c("Year",model)
  if(t==1){
    DF2<-Dec_Means
    t<-t+1
  }else{
    colnames(DF2)[1]<-"Year"
    DF2<-merge(DF2,Dec_Means,by="Year")
  #DF2<-cbind(DF,Ratio[model])
  }
}
```

```{r,fig.width=20.0,fig.height=20.0}
par(mfrow=c(2,2),mar=c(5.1, 5.1, 4.1, 2.1))
plot(as.Date(DF2$Year),DF2$bcc.csm1.1.m_rcp85,col=Color3[1],type="l",lwd=2.0,ylim=c(1,3.5),cex.axis=2.0,cex.lab=1.8,
     ylab="Ratio of PPT/PET",xlab="Year")
lines(as.Date(DF2$Year),DF2$bcc.csm1.1_rcp85,col=Color3[1],lwd=2.0)
lines(as.Date(DF2$Year),DF2$BNU.ESM_rcp85,col=Color3[3],lwd=2.0)
plot(as.Date(DF2$Year),DF2$CanESM2_rcp85,col=Color3[4],lwd=2.0,type="l",ylim=c(1,3.5),cex.axis=2.0,cex.lab=1.8,
     ylab="Ratio of PPT/PET",xlab="Year")
lines(as.Date(DF2$Year),DF2$CCSM4_rcp85,col=Color3[5],lwd=2.0)
lines(as.Date(DF2$Year),DF2$CNRM.CM5_rcp85,col=Color3[6],lwd=2.0)
lines(as.Date(DF2$Year),DF2$CSIRO.Mk3.6.0_rcp85,col=Color3[7],lwd=2.0)
plot(as.Date(DF2$Year),DF2$GFDL.ESM2G_rcp85,col=Color3[8],lwd=2.0,type="l",ylim=c(1,3.5),cex.axis=2.0,cex.lab=1.8,
     ylab="Ratio of PPT/PET",xlab="Year")
lines(as.Date(DF2$Year),DF2$GFDL.ESM2M_rcp85,col=Color3[9],lwd=2.0)
lines(as.Date(DF2$Year),DF2$HadGEM2.CC365_rcp85,col=Color3[10],lwd=2.0)
plot(as.Date(DF2$Year),DF2$MIROC5_rcp85,type="n",axes=F,xlab=NA,ylab=NA)
legend(as.Date(DF2$Year)[1],2.4,legend=c(modelnames),col=c(Color3,Color3[1:10]),
       lty=c(1,1,1,1,1,1,1,1,1,1,4,4,4,4,4,4,4,4,4,4),lwd=c(4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4),cex=2.0)


plot(as.Date(DF2$Year),DF2$HadGEM2.ES365_rcp85,col=Color3[1],lty=4,lwd=2.0,type="l",ylim=c(1,3.5),cex.axis=2.0,cex.lab=1.8,
     ylab="PET mm/year",xlab="Year")
lines(as.Date(DF2$Year),DF2$inmcm4_rcp85,col=Color3[2],lty=4,lwd=2.0)
lines(as.Date(DF2$Year),DF2$IPSL.CM5A.LR_rcp85,col=Color3[3],lty=4,lwd=2.0)
lines(as.Date(DF2$Year),DF2$IPSL.CM5A.MR_rcp85,col=Color3[4],lty=4,lwd=2.0)


plot(as.Date(DF2$Year),DF2$IPSL.CM5B.LR_rcp85,col=Color3[5],type="l",lty=4,lwd=2.0,ylim=c(1,3.5),cex.axis=2.0,cex.lab=1.8,
     ylab="Ratio of PPT/PET",xlab="Year")

lines(as.Date(DF2$Year),DF2$MIROC.ESM.CHEM_rcp85,col=Color3[6],lty=4,lwd=2.0)
lines(as.Date(DF2$Year),DF2$MIROC.ESM_rcp85,col=Color3[7],lty=4,lwd=2.0)
plot(as.Date(DF2$Year),DF2$MRI.CGCM3_rcp85,col=Color3[8],lty=4,lwd=2.0,type="l",ylim=c(1,3.5),cex.axis=2.0,cex.lab=1.8,
     ylab="Ratio of PPT/PET",xlab="Year")
lines(as.Date(DF2$Year),DF2$NorESM1.M_rcp85,col=Color3[9],lty=4,lwd=2.0)
lines(as.Date(DF2$Year),DF2$MIROC5_rcp85,col=Color3[10],lty=4,lwd=2.0)
plot(as.Date(DF2$Year),DF2$MIROC5_rcp85,type="n",axes=F,xlab=NA,ylab=NA)
legend(as.Date(DF2$Year)[1],3.4,legend=c(modelnames),col=c(Color3,Color3[1:10]),
       lty=c(1,1,1,1,1,1,1,1,1,1,4,4,4,4,4,4,4,4,4,4),lwd=c(4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4),cex=2.0)
```

```{r}
### Need to find each in relation to decadal mean 

year<-year(as.Date(DF$DF))
Decade<- year-year %% 10
#colnames(DF)floor_date(DF["DF"],years(10))
DF$Decade<-Decade
year2<-year(as.Date(DF2$Year))
Decade2<-year2-year2 %%10
DF2$Decade<-Decade2



Decadal_DF<-DF2$Year
Variation_DF<-DF$DF
Var2_DF<-DF$DF
for(model in modelnames3){
  Means<-DF2[c("Decade",model)]
  Values<-DF[c("Decade",model)]
  MV_merged<-merge(Values,Means,by="Decade")
  Variation<-MV_merged[2]-MV_merged[3]
  Var2<-Variation**2
  MV_merged<-cbind(MV_merged,Variation,Var2)
  colnames(MV_merged)
  DecadalVariance<-aggregate(MV_merged[5],by=list(D=MV_merged$Decade),FUN=sum)
  Decadal_DF<-cbind(Decadal_DF,DecadalVariance[2])
  Variation_DF<-cbind(Variation,Variation_DF)
  Var2_DF<-cbind(Var2_DF,Var2)
}

```

### Mean Intradecadal Variance

So this takes the mean for each decade and calculates the square variance,
from that mean. Then that is meaned for each model 

```{r,fig.width=10.0,fig.height=10.0}

MeanDecadalVaraincesq<-colMeans(Decadal_DF[2:21])
par(las=2) # make label text perpendicular to axis
par(mar=c(5,15,4,2))
barplot(MeanDecadalVaraincesq[order(MeanDecadalVaraincesq,decreasing = T)],horiz=T,cex.names=1.2)
```

### Decadal Fixed slope models 



```{r,fig.width=10.0,fig.height=10.0}
Models<-NULL
Slopes<-NULL
Ints<-NULL
for(model in modelnames){
  Onemodel<-as.matrix(DF2[model])
  Onemodellm<-lm(Onemodel~ DF2$Year)
  #abline(Onemodellm)
  Int<-Onemodellm$coefficients[1]
  Slope<-Onemodellm$coefficients[2]
  Models<-c(model,Models)
  Slopes<-c(Slope,Slopes)
  Ints<-c(Int,Ints)
}
mean(Ints)


Slopes<-NULL
Models<-NULL
for(model in modelnames){
  Onemodel<-as.matrix(DF2[model])
  Onemodellm<-lm(Onemodel~0+DF2$Year+offset(rep(3.165642,10)) )
  Slope<-Onemodellm$coefficients[1]
  Models<-c(model,Models)
  Slopes<-c(Slope,Slopes)
}

par(las=2) # make label text perpendicular to axis
par(mar=c(5,15,4,2))
barplot(combined$Slopes[order(combined$Slopes)],horiz=T,cex.names=1.2,names.arg =combined$Models[order(combined$Slopes)])
```

### Candidate Models 
We selected four models from this, finding models that have Steep/Low Slope,
and High Variance and Low Variance. 

HAD_GEMES365 is steep slope/ high variance

MRI_CGCM3 is low slope/low variance

CNRM_CM5 is Low slope/high variance 

IPSL CM5A_MR Steep slope/ Low variance



```{r,fig.width=20.0,fig.height=20.0}

#show_col(hue_pal()(6))
#png("PET_PPTRatio.png",width=1500,height=1500)
par(mfrow=c(2,2),mar=c(7,8,5,2))
colorblind=c("#F8766D","#7CAE00","#00BA38","#00BFC4")

plot(as.Date(AllModels$Year),DF$MRI.CGCM3_rcp85,col=colorblind[4],lwd=10.0,type="l",ylim=c(.8,3.9),cex.axis=3.0,cex.lab=3.0,
     ylab="PPT/PET Ratio",xlab="Year",main="a) Low drought / low variance" ,cex.main=4.0,mgp=c(4,1.8,0))
plot(as.Date(AllModels$Year),DF$CNRM.CM5_rcp85,col=Color3[5],type="l",lwd=10.0,ylim=c(.8,3.9),cex.axis=3.0,cex.lab=3.0,
     ylab=NA,xlab="Year", main=" b) Low drought / high variance",cex.main=4.0,mgp=c(4,1.8,0))
plot(as.Date(AllModels$Year),DF$IPSL.CM5A.MR_rcp85,col=colorblind[3],lwd=10.0,type="l",ylim=c(.8,3.9),cex.axis=3.0,cex.lab=3.0,
     ylab="PPT/PET Ratio",xlab="Year", main="c) High drought / low variance",cex.main=4.0,mgp=c(4,1.8,0))

plot(as.Date(AllModels$Year),DF$HadGEM2.ES365_rcp85,col=colorblind[2],lwd=10.0,type="l",ylim=c(.8,3.9),cex.axis=3.0,cex.lab=3.0,
     ylab=NA,xlab="Year", main="d) High drought / high variance",cex.main=4.0,mgp=c(4,1.8,0))


#dev.off()


```




HAD_GEMES365 is Steep Slope/ High Variance

MRI_CGCM3 is low slope/Low Variance

CNRM_CM5 is Low slope/High Variance

IPSL CM5A_MR Steep slope/ Low variance


```{r,fig.width=20.0,fig.height=20.0}

#png("PET_PPT_Alone.png",width=1500,height=1500)
par(mfrow=c(2,2),mar=c(7,5,5,2))
#colorblind=c("#0072B2", "#009E73", "#D55E00",
#              "#CC79A7", "#F0E442", "#56B4E9")

plot(as.Date(AllModels$Year),DFP$MRI.CGCM3_rcp85,col=colorblind[4],ylim=c(300,1600),ylab=NA,lwd=5.0,type="l",cex.axis=2.7,cex.lab=2.5,
     xlab="Year",main="a) Low drought / low variance",cex.main=2.7)
lines(as.Date(AllModels$Year),AllModels$MRI.CGCM3_rcp85,col=colorblind[4],lwd=5.0,lty=4)


plot(as.Date(AllModels$Year),DFP$CNRM.CM5_rcp85,col=Color3[5],ylim=c(300,1600),ylab=NA,type="l",lwd=5.0,cex.axis=2.7,cex.lab=2.5,
     xlab="Year", main="b) Low drought / high variance",cex.main=2.7)
lines(as.Date(AllModels$Year),AllModels$CNRM.CM5_rcp85,col=Color3[5],lwd=5.0,lty=4)
legend(as.Date(AllModels$Year)[1],1600,legend=c("Percipitation","PET"),lty=c(1,4),col=c("black","black"),cex=2.0,lwd=c(4.0,4.0))

#dev.off()

plot(as.Date(AllModels$Year),DFP$IPSL.CM5A.MR_rcp85,col=colorblind[3],lwd=5.0,ylim=c(300,1600),type="l",cex.axis=2.7,cex.lab=2.5,
     ylab="PPT or PET mm/yr",xlab="Year", main="c) High drought / low variance",cex.main=2.7)
lines(as.Date(AllModels$Year),AllModels$IPSL.CM5A.MR_rcp85,col=colorblind[3],lwd=5.0,lty=4)



plot(as.Date(AllModels$Year),DFP$HadGEM2.ES365_rcp85,col=colorblind[2],ylim=c(300,1600),lwd=5.0,type="l",cex.axis=2.7,cex.lab=2.5,
     ylab="PPT or PET mm/yr",xlab="Year", main="d) High drought / high variance",cex.main=2.7)
lines(as.Date(AllModels$Year),AllModels$HadGEM2.ES365_rcp85,col=colorblind[2],lwd=5.0,lty=4)
#dev.off()
```
### Variance of candidate models

```{r,fig.width=20.0,fig.height=20.0}
par(mar=c(5,5,4,2))


plot(as.Date(Decadal_DF$Decadal_DF),Decadal_DF$CNRM.CM5_rcp85.x,lty=4,type="l",col=Color3[2],ylim=c(0,3.5),cex.axis=2.0,cex.lab=1.8,
     ylab="Var^2",xlab="Year", main="Variance 2 per decade",cex.main=2.0)
lines(as.Date(Decadal_DF$Decadal_DF),Decadal_DF$HadGEM2.ES365_rcp85.x,lty=4,col=Color3[6],lwd=2.0)
lines(as.Date(Decadal_DF$Decadal_DF),Decadal_DF$IPSL.CM5A.MR_rcp85.x,col=Color3[5],lwd=2.0)
lines(as.Date(Decadal_DF$Decadal_DF),Decadal_DF$MRI.CGCM3_rcp85.x,col=Color3[1],lwd=2.0)
##lines(as.Date(Decadal_DF$Decadal_DF),Decadal_DF$bcc.csm1.1_rcp85.x,col=Color3[3],lwd=2.0)
##lines(as.Date(Decadal_DF$Decadal_DF),Decadal_DF$MIROC.ESM.CHEM_rcp85.x,col=Color3[4],lwd=2.0)
legend(as.Date(DF2$Year)[1],5.0,legend=c(modelnames),col=c(Color3,Color3[1:6]),
       lty=c(1,1,1,1,1,1,1,1,1,1,4,4,4,4,4,4),cex=.2)

```

### Slopes of candidate models

HAD_GEMES365 is Steep Slope/ High Variance

MRI_CGCM3 is Low slope/Low Variance

CNRM_CM5 is Low slope/High Variance

IPSL CM5A_MR Steep slope/ Low variance

```{r,fig.width=10.0,10.0}
par(xpd=F)
par(mar=c(5.1, 5.1, 4.1, 2.1))
plot(as.Date(AllModels$Year),DF$bcc.csm1.1.m_rcp85,type="n",ylim=c(1,3),cex.axis=2.0,cex.lab=1.8,
     ylab="PET mm/year",xlab="Year")

abline(lm(DF$CNRM.CM5_rcp85~AllModels$Year),lty=4,col=Color3[2],lwd=2.0)
abline(lm(DF$HadGEM2.ES365_rcp85~AllModels$Year),col=Color3[6],lty=4,lwd=2.0)
abline(lm(DF$IPSL.CM5A.MR_rcp85~AllModels$Year),col=Color3[5],lwd=2.0)
abline(lm(DF$MRI.CGCM3_rcp85~AllModels$Year),col=Color3[1],lwd=2.0)

```

