---
title: "Harvest_RMD"
author: "Zjrobbin"
date: "9/9/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The harvest module was parameterized using hte EVALIDATOR data tool.
Evalidator use sql to query the most recent FIA census for an area. 
I broke down the data by county, and used a map of the counties within our study area to associate the data. 


```{r cars}
library(reshape2)
library(ggplot2)
library(rgdal)
w_dir<-"Z:/Robbins/Sapps/Model_Prep/Harvest_Work/"
setwd(w_dir)
Countyshape<-readOGR(paste(w_dir,'Clip_county_correct.shp',sep=""))
plot(Countyshape)
Countyshapedf<-as.data.frame(Countyshape)
Countys_in<-paste(Countyshapedf$STATEFP,Countyshapedf$COUNTYFP,sep="")

```

```{r,fig.width=10.0,fig.height=10.0}
#Plots

TL_AgeClass_DF<-read.csv(paste(w_dir,"TL_Age_Class_DF.csv",sep=""))
TL_Ownership_DF<-read.csv(paste(w_dir,"TL_Ownership_DF.csv",sep=""))

AgeClass_DF<-read.csv(paste(w_dir,'Age_Class_DF.csv',sep=""))
Ownership_DF<-read.csv(paste(w_dir,"Ownership_DF.csv",sep=""))

TL_AgeClass_DF$Landtype<-"Timberlands"
AgeClass_DF$Landtype<-"Forestlands"
TL_Ownership_DF$Landtype<-"Timberlands"
Ownership_DF$Landtype<-"Forestlands"


colnames(AgeClass_DF)
colnames(TL_AgeClass_DF)
AgeClass_DF<-AgeClass_DF[,c(-18)]
TL_AgeClass_DF<-TL_AgeClass_DF[,c(-17,-18)]
TL_AgeClass_DF$AsBir<-NA
AllAgeClass<-rbind(TL_AgeClass_DF)

AllAgeClass[,c(2:16)]<-AllAgeClass[,c(2:16)]*224.17 ##(covert short tons per acre to g/m2)

theme_set(theme_gray(base_size = 18))
AA_melt<-melt(AllAgeClass, id.vars = c("Age_Class","Landtype"), measure.vars = c(colnames(AllAgeClass[,c(2:16)])))
AA_melt_sub<-AA_melt[AA_melt$Age_Class!='Sum',]
colnames(AllAgeClass)
ggplot(AA_melt_sub, aes(fill=Age_Class, y=value, x=variable)) + 
  geom_bar(stat="identity")+
  ylab("Dry Biomass Harvested g/m2")+
  xlab("Forest Type")+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=90, hjust=1)) 
```
WRJP= Jack Pine, Red pine ,easter white pine, eastern white pine hemlock, hemlock
SpFir= Balsam, White spruce, red spruce, redspiurce/basam, black spruce, tamarack northern white ceder. 
#Longleaf/Slash pine= 
#Lobllogy/Shortleaf pine=
#Other eastern soft= Eastern redcedar. 
#OakPine: Pine component needs to be 25-49 percent.
#Oak Hickory:
#Oak Gum Cypress:
#Elm/ash/Cottonwood
#MapleBeech Birch
###Aspen Birch-pin cherry and paper birch. 
#other hardwoods

So looking at this it seems like most of the harvest is in the white pine/red pine, Loblolly/Shortleaf pine, 
Oak Pine/Oak Hicokory, and Some Maple. 

StandRanking  Economic

 Species  | Economic Rank | MinimumAge  |
|----------|---------------|------------|
| PinuStro  | 80            | 40         |
| PinuTaed | 80            | 20         |
| PinuEnch | 60            | 20         |   
| QuerAlba | 30            | 20         |   
|	QuerCocc	| 30           |   20 |
|		QuerFalc |	 30         |     20 |
|		QuerRubr |	 30          |    20 |
|		QuerStel	| 30            |  20 |
|		QuerVelu	|  30         |     20 |
|		AcerSacc   |      30		| 40 |
|		CaryAlba   |      20		| 40 |
|		CaryOvat	 | 20		     | 40	 |
|		CaryCodi	 | 20	         |40 |
|	CaryGlab     |     20		  | 40 |
|		JuglNigr   |      10     |30 |



```{r,fig.width=10.0,fig.height=5.0}
colnames(TL_Ownership_DF) 
colnames(Ownership_DF)
TL_Ownership_DF<-TL_Ownership_DF[,c(-17,-18)]
Ownership_DF<-Ownership_DF[,c(-18)]
TL_Ownership_DF$AsBir<-NA
AllOwnership<-rbind(TL_Ownership_DF)
AllOwnership[,c(2:16)]<-AllOwnership[,c(2:16)]*224.17 ##(covert short tons per acre to g/m2)
library(reshape2)
library(ggplot2)
library(RColorBrewer)
Own_melt<-melt(AllOwnership, id.vars = c("Ownership","Landtype"), measure.vars = c(colnames(AllAgeClass[,c(2:16)])))
Own_melt_sub<-Own_melt[Own_melt$Ownership!='Total',]
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

ggplot(Own_melt_sub, aes(fill=variable, y=value, x=Ownership)) + 
  geom_bar(aes(fill = variable), position = position_dodge(0.6),stat="identity")+
  ylab("Dry Biomass Harvested g/m2")+
  xlab("Ownership")+
  scale_fill_manual(values=c(cbPalette,brewer.pal(7,'Paired')))
```

Here are the totals by ownership. 

```{r}
barplot(AllOwnership$Total,names=AllOwnership$Ownership,las=2,ylab="g/m2",
        main="Harvest Evalidator")
```

This was used to validate the amount of commercial harvest on the landscape. 

#### Making the Map 

##### [Landownership](https://www.fs.usda.gov/rds/archive/Product/RDS-2017-0007)

From the FS Website


This data publication contains 250 meter raster data depicting the spatial 
distribution of forest ownership types in the conterminous United States. 
The data are a modeled representation of forest land by ownership type, and include 
three types of public ownership: federal, state, and local; 
three types of private: family (includes individuals and families), corporate, and 
other private (includes conservation and natural resource 
organizations, and unincorporated partnerships and associations); as well as Native 
American tribal lands. The most up-to-date data available
were used in creating this data publication. 

A plurality of the ownership data were from 2014, but some data were as old as 2004.


```{python,eval=F}
####Import libraries
import rasterio as rt 
import geopandas as gp
import gdal
from rasterio.mask import mask
###Get coordinate features and geometry
def getFeatures(gdf):
    """Function to parse features from GeoDataFrame in such a manner that rasterio wants them"""
    import json
    return [json.loads(gdf.to_json())['features'][0]['geometry']]

##Work Drive
w_dir="E:/Harvest_Work/"
###The orgininal Ownership raster
Ownership=(w_dir+"/RDS-2017-0007/Data/forown2016/hdr.adf")

###Study Area
AOI=gp.read_file(w_dir+"Dissolved_AOI.shp")
##Get CRS
ShpCRS=AOI.crs
###Warp raster
### I entered CRS manually
input_raster = gdal.Open(Ownership)
output_raster=(w_dir+"Ownership_reproj.tif")
gdal.Warp(output_raster,input_raster,dstSRS='EPSG:26917')
###Bring back reshaped raster
reshape_Ownership=rt.open(w_dir+"Ownership_reproj.tif")
###Get geometry from Study Area
coords=getFeatures(AOI)

###Get meta from raster
out_meta = reshape_Ownership.meta.copy()
###Mask raster to study area
out_img,out_transform=mask(raster=reshape_Ownership,shapes=coords,crop=True)
out_meta = reshape_Ownership.meta.copy()
epsg_code = int(reshape_Ownership.crs.data['init'][5:])
###Update meta data for new mask raster
out_meta.update({"driver": "GTiff",
                 "height": out_img.shape[1],
                 "width": out_img.shape[2],
                 "transform": out_transform}
                    )
###Set drive for masked raster
out_tif=w_dir+"Oship_cut.tif"
###Write Raster
with rt.open(out_tif, "w", **out_meta) as dest:
    dest.write(out_img)    


```


```{r}
library(raster)
library(rgdal)
library(raster)
library(sf)
library(utils)
library(ggplot2)
library(RColorBrewer)
library(rgdal)
```

```{r,eval=F}
Oshipcut<-raster::raster(paste(w_dir,'Oship_cut.tif',sep=""))
crs(Oshipcut)<-CRS("+init=EPSG:26917")
SampleEcoregion<-raster::raster(paste(w_dir,'Inputs/MR_FourEcoregions.tif',sep=""))
crs(SampleEcoregion)<-CRS("+init=EPSG:26917")
resampled<-resample(Oshipcut,SampleEcoregion,method='ngb')
filename<-paste(w_dir,"Ownership_Resampled.tif")
writeRaster(resampled, filename=filename, datatype='INT4S',overwrite=TRUE)#Th
```


```{r}
Ownership<-raster(paste0(w_dir,'Ownership_Resampled.tif'))
plot(Ownership,zlim=c(0,9))
```

#>>1-Federal *
#  >>2-State
#>>3-Local
#>>4- Family *
#  >>5-Corporate*
#  >> 6- Other Private
#>>7- Tribal
#>>8- Off



To create the stand map I crossed the Ownership map with the HUC Watershed map, so that each owneship with a water shed is its own stand. 


https://viewer.nationalmap.gov/basic/?basemap=b1&category=nhd&title=NHD%20View


```{r}
library(RColorBrewer)
Random<-brewer.pal(13,"Set3")
plot(raster::raster(paste0(w_dir,"Watersheds.tif")),main="HUC 8 Watershed map ",col=rep(Random,10000) )

```

```{r}

Stands3<-raster::raster(paste0(w_dir,"Stands3.tif"))
plot(Stands3,col=rep(Random,10000))
length(unique(Stands3))
```
That gives us 22,000 stands


```{r}
### Stand Size
StandSize<-sqrt((650000*62500)/22000)
### Gap size
sqrt(.20*(StandSize**2))
```

Each stand is therefore like 1.358km x 1.358km
if our patch size is 20% we are areound 607m x 607m or ~ a 4x4 grid

### Comparing to the Data. 

```{r}
library(reshape2)
library(ggplot2)
library(rgdal)
library(dplyr)
library(plyr)
w_dir<-"C:/Users/zacha/Documents/GitHub/Project-Southern-Appalachians-2018/Parameterizing/Harvest/"
```

```{r}
TL_AgeClass_DF<-read.csv(paste(w_dir,"TL_Age_Class_DF.csv",sep=""))
TL_Ownership_DF<-read.csv(paste(w_dir,"TL_Ownership_DF.csv",sep=""))
AllOwnership<-rbind(TL_Ownership_DF)
AllOwnership[,c(2:16)]<-AllOwnership[,c(2:16)]*224.17 ##(covert short tons per acre to g/m2)
```




```{r}
LANDIS_summary<-read.csv(paste0(w_dir,"biomass-harvest-summary-log_100.csv"))
#colnames(LANDIS_summary)
keep<-c(1:7,56:103)
LS_s<-LANDIS_summary[,keep]
LS_s<-LS_s[,c(-3)]
LS_s<-LS_s %>%
    group_by(Time, ManagementArea) %>% 
    summarise_each(funs(sum))


Ownership<-raster(paste0(w_dir,'Ownership_Resampled.tif'))
Ownershipcells<-as.data.frame(
    table(
      as.data.frame(
          Ownership)))

Ownershipcells$Area<-Ownershipcells$Freq*62500
colnames(Ownershipcells)<-c("ManagementArea","Cells","Area(m)")

Managements<-unique(LS_s$ManagementArea)
Prescriptions<-unique(LS_s$Prescription)
HL_DF<-NULL
for(Management in Managements){
#    Harv<- LS_s[LS_s$Prescription==Prescription,]
    sus<-LS_s[LS_s$ManagementArea==Management,]
    
    MergedOneM<-merge(
      sus,
      Ownershipcells,
      by="ManagementArea",
      all.x=T
    )
    MO_Columns<-colnames(MergedOneM)
    Names<-MO_Columns[8:55]
    Names<-gsub("Mg","g_m2_",Names)
    GramMetersq<-(MergedOneM[8:55]*1000000)/MergedOneM$`Area(m)`
    
    GramMean<-t(as.data.frame(colMeans(GramMetersq)))
    colnames(GramMean)<-Names
    OutRow<-cbind(MergedOneM[1,1:3],GramMean)
    HL_DF<-rbind(OutRow,HL_DF)
  }

HL_DF$Total<-rowSums(HL_DF[4:51])
HL_DF<-HL_DF[complete.cases(HL_DF),]
```

```{r}
LUT<-data.frame(ManagementArea=c(1,2,3,4,5,6,7,8),
                Name=c("Federal","State","Local","Family",
                       "Corporate","Other_Private","Tribal","Off"))
HL_DF<-merge(HL_DF,
        LUT,
        by="ManagementArea",
        all.x=T)

ComThin<-HL_DF[HL_DF$Prescription==" CommercialThin",]



EcoHarvest<-HL_DF
```
```{r,fig.width=10.0,fig.height=10.0}
par(mfrow=c(2,1),mar=c(5.1,4.1,4.1,.1))
barplot(EcoHarvest$Total,names=EcoHarvest$Name,las=3,ylab="g/m2",
        main="Economic Harvest LANDIS")
barplot(AllOwnership$Total,names=AllOwnership$Ownership,las=2,ylab="g/m2",
        main="Harvest Evalidator")
```


```{r,fig.height=7.0}
Private_DF<-data.frame(names=c("Evalidator Private","LANDIS-Corporate","LANDIS-Family","LANDIS-Other_Private","LANDIS_mean"),
           values=c(AllOwnership$Total[AllOwnership$Ownership=="Private"],EcoHarvest$Total[EcoHarvest$ManagementArea==5],
                    EcoHarvest$Total[EcoHarvest$ManagementArea==4],EcoHarvest$Total[EcoHarvest$ManagementArea==6],
                    mean(c(EcoHarvest$Total[EcoHarvest$ManagementArea==5],
                    EcoHarvest$Total[EcoHarvest$ManagementArea==4],EcoHarvest$Total[EcoHarvest$ManagementArea==6]))))




#print(LUT)
par(mar=c(10.1,4.1,4.1,.1))
barplot(Private_DF$values,names=Private_DF$names,las=3,ylab="g/m2",
        main="Private harvest LANDIS")


```


```{r,fig.height=7.0}
print(LUT)
unique(AllOwnership$Ownership)
Fed_DF<-data.frame(names=c("Evalidator National","Evalidator Other fed",'Evalidator federal sum',"LANDIS-Federal"),
          values=c(AllOwnership$Total[AllOwnership$Ownership=="National"],
                    AllOwnership$Total[AllOwnership$Ownership=="Other_Fed"],
                    mean(AllOwnership$Total[AllOwnership$Ownership=="National"],AllOwnership$Total[AllOwnership$Ownership=="DOD"],AllOwnership$Total[AllOwnership$Ownership=="Other_Fed"]),EcoHarvest$Total[EcoHarvest$ManagementArea==1]))

par(mar=c(10.1,4.1,4.1,.1))
barplot(Fed_DF$values,names=Fed_DF$names,las=3,ylab="g/m2",
        main="Economic Harvest LANDIS")

```

```{r,fig.height=7.0}
StateLocal_DF<-data.frame(names=c("Evalidator State","LANDIS State",'Evalidator Local',"LANDIS-County"),
          values=c(AllOwnership$Total[AllOwnership$Ownership=="State"],EcoHarvest$Total[EcoHarvest$ManagementArea==2],
                    AllOwnership$Total[AllOwnership$Ownership=="County"],EcoHarvest$Total[EcoHarvest$ManagementArea==3]
                   ))
#EcoHarvest$Total[EcoHarvest$ManagementArea==3]
par(mar=c(10.1,4.1,4.1,.1))
barplot(StateLocal_DF$values,names=StateLocal_DF$names,las=3,ylab="g/m2",
        main="Economic Harvest LANDIS")
```

