---
title: "Climate Regions"
output: 
  html_document:
    keep_md: true
    
---

> Climate

> Climate regions were selected by clustering together the growing season normals for temperature and precipitaiton. 30 yr normal values for mean
temperature and precipitaiton were gatheredfrom Prism (http://www.prism.oregonstate.edu/normals/), these were summed over the growing season. 
We then preformed k-means clustering based on these values, with clusters ranging between 5 and 20. These were analyzed to see how much variance each one
encapsulated. We ultimately decided on 10 ecoregions. 
Climate models were downloaded from the MACA portls using the NKN Thredd Server, and the mean value for each day accessed for each of the twelve ecoregions. The variables used were precipitation, temperature(minimum), temperature(maximum),minimum relative humidity, maximum relative humidity,eastward wind speed, and northward wind speed. 

Citations

* Daly, C., & Bryant, K. (2013). The PRISM climate and weather system—an introduction. Corvallis, OR: PRISM climate group.

* Abatzoglou J.T. and Brown T.J. A comparison of statistical 
downscaling methods suited for wildfire applications, International 
Journal of Climatology (2012), 32, 
772-780https://climate.northwestknowledge.net/MACA/





)
Start by defining the growing season temperatur eand percipitaiton
We got normals values from prism 
http://www.prism.oregonstate.edu/normals/

for each month and summed precipitation and meaned temperature over the growing season 



```{r}
knitr::opts_chunk$set(echo=F,warning=F)
library(raster)
library(RColorBrewer)
library(plotrix)
Uniques<-brewer.pal(11,"Spectral")
Drive='Z:/Robbins/Sapps/Model_Prep/New_Normal/Folder/'
#setwd(Drive)

```

Here is how we selected the climate regions. 

Start by defining the growing season temperatur eand percipitaiton
We got normals values from prism 
http://www.prism.oregonstate.edu/normals/

for each month and summed precipitation and meaned temperature over the growing season 
```{r}

allfiles=list.files(Drive,pattern="\\.bil$")
tmean=allfiles[grep("tmean",allfiles)]
ppt=allfiles[grep("ppt",allfiles)]
Prism_Normals_Tmean=raster::stack(paste0(Drive,tmean))
Prism_Normals_PPt=raster::stack(paste0(Drive,ppt))
PPT_mean=sum(Prism_Normals_PPt)
Tmean_mean=mean(Prism_Normals_Tmean)

Ecoregions=raster::raster(paste0(Drive,'/MR_FourEcoregions.tif'))
Template=raster::raster(paste0(Drive,'/MRSOM1soilCmap.tif'))
projection(Template)
dataType(Ecoregions)
Fixy_Mapy<-function(Input,Ecoregion){
  PN_repro<-raster::projectRaster(Input,Ecoregion)
  PN_clip<-mask(PN_repro,Ecoregion)
  plot(PN_clip,axes=F,box=F)
  PN_Match<-resample(PN_clip,Ecoregion)
  return(PN_Match)
}

```

```{r}

#plot(Tmean_mean)
#plot(PPT_mean)
```

Here is the mean growing season temperature for the area of intrest

```{r}
Tmean_adj<-Fixy_Mapy(Tmean_mean,Ecoregions)
```

And the summed precipitation

```{r}
PP_adj<-Fixy_Mapy(PPT_mean,Ecoregions)
```

Then we scaled the variables to be comparible 

```{r}
Stack<-stack(Tmean_adj,PP_adj,Template)
#plot(Template)
Stack$layer.1[Stack$MRSOM1soilCmap==-9999,]<-0
Stack$layer.2[Stack$MRSOM1soilCmap==-9999,]<-0
#plot(Stack$layer.1)
Tmean_scale<-scale(Stack$layer.1)
PP_scale<-scale(Stack$layer.2)
```

Then preformed a kmeans clustering algrothim for both varaibles. 
We looked at the means and variances clustered within each ecoregion.

```{r}
Stackofvariables<-stack(Tmean_scale,PP_scale)
DF_ofVariables<-as.data.frame(Stackofvariables)
DF_Original<-as.data.frame(Stack)
Classification<-kmeans(na.omit(DF_ofVariables), 11, iter.max = 10, nstart = 25)
cluster<-Classification$cluster
#hist(cluster)
output_matrix<-matrix(cluster,nrow=nrow(Ecoregions),ncol=ncol(Ecoregions),byrow=T) #fir

new_output_raster<-raster(output_matrix,xmn=xmin(Ecoregions),ymn=ymin(Ecoregions),
                          xmx=xmax(Ecoregions),ymx=ymax(Ecoregions), crs=proj)

```

Here is the clustering with 10 ecoregions 

```{r}

Tmean_template<-cbind(as.numeric(cluster),DF_ofVariables$layer.1)
MeanEcoregion<-aggregate(Tmean_template[,2],by=list(Tmean_template[,1]),FUN=mean)
VarTempEcoregion<-aggregate(Tmean_template[,2],by=list(Tmean_template[,1]),FUN=var)
SETempEcoregion<-aggregate(Tmean_template[,2],by=list(Tmean_template[,1]),FUN=std.error)

PPT_template<-cbind(as.numeric(cluster),DF_ofVariables$layer.2)
MeanPPTEcoregion<-aggregate(PPT_template[,2],by=list(PPT_template[,1]),FUN=mean)
VarPPTEcoregion<-aggregate(PPT_template[,2],by=list(PPT_template[,1]),FUN=var)
SEPPTEcoregion<-aggregate(PPT_template[,2],by=list(PPT_template[,1]),FUN=std.error)
plot(new_output_raster,col=Uniques)
Stats<-cbind(MeanEcoregion,VarTempEcoregion[,2],SETempEcoregion[,2],MeanPPTEcoregion[,2],
      VarPPTEcoregion[,2],SEPPTEcoregion[,2])
colnames(Stats)<-c("Ecoregion","MeanTemp","VarTemp","SETemp",
                   "Mean PPT","Var PPT","SE PPT")

```

And the distribution of the variables(Normalized)

```{r}
print(Stats)
```

We experimented with values from 5 to 20 ecoregions, to find the minimum number that minizied the variance while accounting for computational cost. 



```{python, eval=F}
## Librarys
import xarray as xr
import os
import time
import numpy as np

### It says you have to import netcdf4 before rasterio or else an error will occur
from netCDF4 import Dataset
from datetime import datetime, timedelta
#from netCDF4 import num2date, date2num
#import matplotlib.pyplot as plt
import geopandas as gp
import rasterio as rt 
from rasterio.transform import from_origin
from rasterio.mask import mask
from rasterio.crs import CRS
import pandas as pd
import dask
from functools import partial
from joblib import Parallel, delayed ,cpu_count
#import matplotlib.pyplot as plt


####  This is my work on top of K. Jones xrray grab for netcdfs from the maca threads
####  Authors K. Jones, Z. Robbins 2020 ***Pandemic Code***



### Below I am reading in individual URL's from NKN Thredd Server, however, this could be modified to take in the text file produced 
### by the MACA portal download and 
### read the url list within the text file. Since the URLs can be generated to download netcdfs at a smaller bounding 
### box extent (from the maca website), it would eliminate the need to do the
### "slicing" operation in the loop at the bottom of this script.

## Functions


def getFeatures(gdf):
    """Function to parse features from GeoDataFrame in such a manner that rasterio wants them"""
    import json
    return [json.loads(gdf.to_json())['features'][0]['geometry']]

def Loadinandcut(httpline,latmin,latmax,lonmin,lonmax):
   ##Function to take a MACA data library line, change the server,cut it to the"""
   ##Appropriate size for your study extent and turn into netcdf4"""
    ###Setup outputs
    #httpline=lines[5]
    start=time.time()
    trimmed_name = httpline.split('macav2metdata_')[1]
    modelname = trimmed_name.split('_daily')[0]
    ###GetNetcddf
    removespatial=httpline.split("?")[0]
        ### Here we are readjusting the server
    Gethalf=removespatial.split("ncss/grid/")[0]
    GetOtherHalf=removespatial.split("ncss/grid/")[1]
        ### Get a new filename to search
    file=Gethalf+"dodsC/"+GetOtherHalf
    ###Xarray File
    print('Load',(time.time() - start))
    
    Testfile = xr.open_dataset(file)
#    with xr.open_dataset(file) as ds:
 #       ds.load()

    ### Cut to the area 
    print('Slice',(time.time() - start))
    file_slice = Testfile.sel(lon=slice(lonmin, lonmax), lat=slice(latmin, latmax))
    ###Print and cover your tracks
    print('Write',(time.time() - start))    
    #file_slice.chunk(chunks={'time':500})
    #start=time.time()
    file_slice.to_netcdf(Drive+modelname+".nc",engine="scipy")
    print('Done',(time.time() - start))  
    ##Time is 6:11
    print("1")
    file_slice.close()
    print("2")
    Testfile.close()
    print("3")

    
    
def FormatNetCdf(input_cdf,key):
    ##Function to take Netcdf and format for rasterio as a multiband tiff"""
    #start=time.time()
    #print("start")
    ##Load in netcdf4
    Precip = Dataset(input_cdf,"r")
    
    #Get the array from the NETCDF
    Array= np.array(Precip.variables[key])
    ## Not sure why I have to flip, but it seems to be writing in reverse order
    ## This fix works 
    Array=np.flip(Array,axis=1)
    ### Get Variables 
    Time=np.array(Precip.variables['time'])
    dates = [datetime(1900,1,1)+n*timedelta(hours=24) for n in Time]
    ## Get geo for locating 
    lat=np.array(Precip.variables['lat'])
    lon=np.array(Precip.variables['lon'])
    lon2=-(360-lon)
    
    ##Adjust dates
    #days since 1900-01-01
    ### Set standard dates
    ### Set resolutions
    reslon=(max(lon2)-min(lon2))/len(lon2)
    reslat=(max(lat)-min(lat))/len(lat)
    ### Transform structure in form West North, Widthres  Heighres. 
    transform_Structure=from_origin(min(lon2), max(lat), reslon, reslat)
    
    ### Get meta data 
    out_meta={'crs':CRS.from_epsg(4269),
    'driver': 'GTiff',
    'count':34333,
    'dtype': 'float32',
    'height': len(lat),
    'nodata': None,
    'transform':transform_Structure, 
    #'transform': (min(lat), max(lat),(max(lat)-min(lat))/len(lat),min(lon),max(lon),(max(lon2)-min(lon2))/len(lon),max(lon)),
    'width': len(lon2)}
       ###Write array as raster stack
      
    new_output=rt.open(Drive+'All.tif', 'w', **out_meta) 
    new_output.write(Array)
    new_output.close()
    Template=rt.open(Drive+'All.tif')
    return(Template,dates)

def MaskandWrite(shapefile,key,Template,dates,label):
    ##Function to mask the Tiff by a shapefile, and return a set of ecoregion variable data"""
    start=time.time()
    print("start")
    ###Ensure shapefile is dissolved
    geoshape=shapefile.dissolve(by='DN')
    coords=getFeatures(geoshape)   
    ### Get the Rasterstack
               

    ### Create nulls   
    #something=pd.DataFrame([[dates]],columns=["Timestep"])
    MeanStack=pd.DataFrame(columns=["Timestep"])
    VarStack=pd.DataFrame(columns=["Timestep"])
    StdStack=pd.DataFrame(columns=["Timestep"])    
                    
    ###Mask
    out_img,out_transform=mask(Template,shapes=coords,crop=True,nodata=-9999)
    print('MaskDone',(time.time() - start))
    for i in list(range(1,len(dates))):
        
        Timestep=dates[i]
        #print(Timestep)
        band1=out_img[i,:,:]
        #print(band1)
         ### Fix temp K to C    
        meancalc=band1[band1!=-9999]
        if key == 'air_temperature':
            meancalc= meancalc-273.15
            #print(np.mean(meancalc))
           # print(meancalc)
        ### Get the Mean
        mean=(np.mean(meancalc))
        #print(np.mean(mean))
        ### Variance 
        variance=(np.var(meancalc))
        ### Standard Deviation
        STD=(np.std(meancalc))
        ###Create Outputs
        Mean=pd.DataFrame([[Timestep,mean]],columns=["Timestep",label])
        StTime=pd.DataFrame([[Timestep,STD]],columns=['Timestep',label+"STD"])
        VarTime=pd.DataFrame([[Timestep,variance]],columns=['Timestep',(label+"VAR")])  
        ###Append to list    
        MeanStack=MeanStack.append(Mean)
        StdStack=StdStack.append(StTime)
        VarStack=VarStack.append(VarTime)
    print('Writingdone',(time.time() - start))    
    #### Make into one dataframe        
    stepone=None    
            
    stepone=pd.merge(MeanStack,VarStack,how='inner', on='Timestep')
    one_eco=pd.merge(stepone,StdStack, how='inner',on='Timestep')
    print('Done',(time.time() - start))  
    return(one_eco)

##### Running the stuff 


### Set drive Location
Drive="C:/Users/zjrobbin/Desktop/New_Climate/"
#### Load in Shapes
Shape1= gp.read_file((Drive+'New_Climate_Regions/done/Eco_1.shp'))
Shape2= gp.read_file((Drive+'New_Climate_Regions/done/Eco_2.shp'))
Shape3= gp.read_file((Drive+'New_Climate_Regions/done/Eco_3.shp'))
Shape4= gp.read_file((Drive+'New_Climate_Regions/done/Eco_4.shp'))
Shape5= gp.read_file((Drive+'New_Climate_Regions/done/Eco_5.shp'))
Shape6= gp.read_file((Drive+'New_Climate_Regions/done/Eco_6.shp'))
Shape8= gp.read_file((Drive+'New_Climate_Regions/done/Eco_8.shp'))
Shape9= gp.read_file((Drive+'New_Climate_Regions/done/Eco_9.shp'))
Shape10= gp.read_file((Drive+'New_Climate_Regions/done/Eco_10.shp'))
Shape11= gp.read_file((Drive+'New_Climate_Regions/done/Eco_11.shp'))


Full_start=time.time()
### This is the Text File
filepath =Drive+ 'macav2_OneModel_Test.txt'

with open(filepath) as fp:
    Lineread = fp.readlines()### This is the individual files we need to dl
    
### the last line is always blank, remove it. 
del Lineread[-1]

### Here I am removing the Last Lines    


#Inputs
#Loadinandcut2(lines[0], latmin, latmax, lonmin, lonmax)
### Set a reasonable bounding box for the first cut. 
lonmin=274.4312 
lonmax=279.8369 
latmin=33.9681
latmax=37.0724


### Create a partial (ei a model with all but one varaible for parallel processing)
partLoadandCut=partial(Loadinandcut,latmin=latmin,latmax=latmax,lonmin=lonmin,lonmax=lonmax)

Models=1


for j in list(range(0,Models)):
    Full_start=time.time()
    start=0+(8*j)
    end=start+8
    ### I put this in to manage memeory 
    ### (Only process one models worth of varibles at a time)

    
    lines=Lineread[start:end]
    httplut=[lines[0],lines[1],lines[2],lines[3],lines[4],lines[5],lines[6],lines[7]]
    
    
    ### I have had trouble getting the par to reliably not get locked out or 
    ### post a HDF error. So for now we are singular.
    #Parallel(n_jobs=6)(delayed(partLoadandCut)(httpline=i) for i in httplut)

    ### I set up this version to to load in of all netCDF's then process each 
    ### of them. This was where I was having the most problems. 
    for i in httplut:
        start1=time.time()
        print("Loading in Data",time.time()-start1,)
        partLoadandCut(httpline=i)
        
        #httpline=i
        print("DataLoaded",time.time()-start1)
    
    
    
    
    for i in httplut:
        print(i)
        
        start1=time.time()
        httpline=i
        print("Preparing Variables",time.time()-start1)
        ### Set up lookups 
        trimmed_name = httpline.split('macav2metdata_')[1]
        #print(trimmed_name)
        modelname = trimmed_name.split('_daily')[0]
        #print(modelname)
        variablename=modelname.split('_')[0]
        #print(variablename)
        ### 
        NC_path=(Drive+modelname+".nc")
        par=variablename
        #print(par)
        if "pr" == par:
            key='precipitation'
            #model=file[16:]
            #model=model.replace('_2006_2099_CONUS_daily_aggregated.nc',"")
        if "tasmin"== par:
            key='air_temperature'
            #model=file[20:]
            #model=model.replace('_2006_2099_CONUS_daily_aggregated.nc',"")      
        if "tasmax" == par:
            key='air_temperature' 
            #model=file[20:]
            #model=model.replace('i1p1_rcp85_2006_2099_CONUS_daily_aggregated.nc',"")
        if"rhsmax"== par:
            key='relative_humidity'
        if"rhsmin"== par:
            key='relative_humidity' 
        if"vpd"== par:    
            key='vpd'
        if "uas"== par:
            key="eastward_wind"
        if "vas"== par:
            key="northward_wind"
        
        
        Template,dates=FormatNetCdf(NC_path, key)
        
        ### masking and writing matrices
        #MaskandWritepart=partial(MaskandWrite, key, Template, dates,"eco2")
        #start=time.time()
        #shapes=[Shape1,Shape2,Shape3,Shape4]
        #Ecos=zip(*Parallel(n_jobs=4)(delayed(MaskandWritepart)(shapefile=i) for i in shapes))
        #elapsed = (time.time() - start)    
        print("Cutting_Begins",time.time() - start1) 
        practiceoneeco1=MaskandWrite(Shape1,key,Template,dates,"eco2")
        practiceoneeco2=MaskandWrite(Shape2,key,Template,dates,"eco3")
        practiceoneeco3=MaskandWrite(Shape3,key,Template,dates,"eco4")
        practiceoneeco4=MaskandWrite(Shape4,key,Template,dates,"eco5")
        practiceoneeco5=MaskandWrite(Shape5,key,Template,dates,"eco6")
        practiceoneeco6=MaskandWrite(Shape6,key,Template,dates,"eco7")
        practiceoneeco7=MaskandWrite(Shape8,key,Template,dates,"eco8")
        practiceoneeco8=MaskandWrite(Shape9,key,Template,dates,"eco9")
        practiceoneeco9=MaskandWrite(Shape10,key,Template,dates,"eco10")
        practiceoneeco10=MaskandWrite(Shape11,key,Template,dates,"eco11")
        elapsed = (time.time() - start1)
        print("Cutting done",elapsed)
        
        ###ECOLUT
        ##High Elevation is eco 5
        ##NorthMontane is 2
        ## Mid Montane is 3
        ## Low Elevation is 4
        
        
        
        ### Merging one dataframe this could be cleaned 
        stepone=pd.merge(practiceoneeco1,practiceoneeco2,how='inner', on='Timestep')
        steptwo=pd.merge(stepone,practiceoneeco3,how='inner', on='Timestep')
        stepthree=pd.merge(steptwo,practiceoneeco4,how='inner', on='Timestep')
        step4=pd.merge(stepthree,practiceoneeco5,how='inner', on='Timestep')
        step5=pd.merge(step4,practiceoneeco6,how='inner', on='Timestep')
        step6=pd.merge(step5,practiceoneeco7,how='inner', on='Timestep')
        step7=pd.merge(step6,practiceoneeco8,how='inner', on='Timestep')
        step8=pd.merge(step7,practiceoneeco9,how='inner', on='Timestep')
        step9=pd.merge(step8,practiceoneeco10,how='inner', on='Timestep')
        step9.columns.tolist()
        
        ### Order Columns 
        colorder=["Timestep","eco2","eco3","eco4","eco5","eco6","eco7","eco8","eco9",
                  "eco10","eco11","eco2VAR","eco3VAR","eco4VAR","eco5VAR","eco6VAR","eco7VAR",
                  "eco8VAR","eco9VAR","eco10VAR","eco11VAR",
                  "eco2STD","eco3STD","eco4STD","eco5STD","eco6STD","eco7STD","eco8STD","eco9STD",
                  "eco10STD","eco11STD"]
        ### Make it pretty 
        Print_Ready=step9[colorder]
        
        
        Print_Ready.to_csv(Drive+"Outputs/"+modelname+".csv")
        os. remove(Drive+modelname+".nc") 
    
    print("Model finished")
    print(time.time()-Full_start)
```

