---
title: "LANDIS-II landscape documentation"
author: "Zjrobbin"
date: "3/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
```

### Landscape Validation

Here is a landscape run of 50 years at a 5 year timestep. This run has fire turned off. 


#### AGNPP

```{r cars,fig.width=10.0,fig.height=7.0}
HistoricDrive<-"C:/Users/zacha/Desktop/50_yr_Historic/"
NECN_s<-read.csv(paste0(HistoricDrive,"NECN-succession-log.csv"))
NECN_s<-NECN_s[!NECN_s$Time==0,]
AG_NPP<-NECN_s[,c("Time","ClimateRegionName","AG_NPPC")]
AG_NPP[,"AG_NPPC"]<-AG_NPP[,"AG_NPPC"]/100
theme_set(theme_classic(base_size = 20))

p<-ggplot(AG_NPP, aes(x=Time, y=AG_NPPC, group=ClimateRegionName)) +
  geom_line(aes(color=ClimateRegionName))+
  geom_point(aes(color=ClimateRegionName))+
  labs(title="Abover Ground Net Primariy Productivity",
        x ="Timestep", y = "AG_NPP C(gC m-2 yr-1)")
p
```
```{r}
mean(c(11.8,9.8,9.6,9.8,9.2,8.1,8.1,7.5,8.3,5.2,8.4,11.2,11.6,9.8,9.3,9.8))
mean(c(AG_NPP$AG_NPPC))
```
The mean from our ecoregions which  is ~ 7.0 which includes ecoregions in various sucessional states. 

Bolstad in studying 16 sites at the Coweeta Hydrologic labratory in western North Carolina found ANPP values between 5.2-11.8 with a mean ~9.2. However these represent sites that have not been disturbed since the mid 1920s and all were closed canopies. 
Clinton Yeakley and Apsely in the same study area found that follwoing disturbance primary productivity was much lower 2.2-4.2 Mg/ha/yr in the multiple decades following disturbance. It is therefore likely that our landscape level values represent composition of various states of forest successional states. 

Busing, Clebesch and White 1993, in studying cove forests of the southern Applachians found young decidious stands to have an ANPP of between 11.7-13.1 MG/ha/yr For Old decidious stands to have between 6.3-11.8 Mg/ha/yr. and for Old coniferous-deciduous stands to have between 8.0-10.1 Mg/ha/yr. 


Citation:
Bolstad, P. V., Vose, J. M., & McNulty, S. G. (2001). Forest productivity, leaf area, and terrain in southern Appalachian deciduous forests. Forest Science, 47(3), 419-427.

#### Mineral Nitrogen 

```{r,fig.width=10.0,fig.height=7.0}
AG_NPP<-NECN_s[,c("Time","ClimateRegionName","MineralN")]
theme_set(theme_classic(base_size = 20))
p<-ggplot(AG_NPP, aes(x=Time, y=MineralN, group=ClimateRegionName)) +
  geom_line(aes(color=ClimateRegionName))+
  geom_point(aes(color=ClimateRegionName))+
  labs(title="Mineral Nitrogen",
        x ="Timestep", y = "g N m-2")
p
```

#### Leaf Area Index 



```{r}
LAI5<-raster("C:/Users/zacha/Desktop/50_yr_Historic/NECN/LAI-5.img")
LAI5[LAI5$LAI.5==0]<-NA
hist(LAI5$LAI.5)
```


```{r}
LAI1<-raster("C:/Users/zacha/Desktop/50_yr_Historic/NECN/LAI-1.img")
LAI1<-mean(as.data.frame(LAI1[!LAI1$LAI.1==0])[,1])
LAI5<-raster("C:/Users/zacha/Desktop/50_yr_Historic/NECN/LAI-5.img")
LAI5<-mean(as.data.frame(LAI5[!LAI5$LAI.5==0])[,1])
LAI10<-raster("C:/Users/zacha/Desktop/50_yr_Historic/NECN/LAI-10.img")
LAI10<-mean(as.data.frame(LAI10[!LAI10$LAI.10==0])[,1])
LAI15<-raster("C:/Users/zacha/Desktop/50_yr_Historic/NECN/LAI-15.img")
LAI15<-mean(as.data.frame(LAI15[!LAI15$LAI.15==0])[,1])
LAI20<-raster("C:/Users/zacha/Desktop/50_yr_Historic/NECN/LAI-20.img")
LAI20<-mean(as.data.frame(LAI20[!LAI20$LAI.20==0])[,1])
LAI25<-raster("C:/Users/zacha/Desktop/50_yr_Historic/NECN/LAI-25.img")
LAI25<-mean(as.data.frame(LAI25[!LAI25$LAI.25==0])[,1])
LAI30<-raster("C:/Users/zacha/Desktop/50_yr_Historic/NECN/LAI-30.img")
LAI30<-mean(as.data.frame(LAI30[!LAI30$LAI.30==0])[,1])
LAI35<-raster("C:/Users/zacha/Desktop/50_yr_Historic/NECN/LAI-35.img")
LAI35<-mean(as.data.frame(LAI35[!LAI35$LAI.35==0])[,1])
LAI40<-raster("C:/Users/zacha/Desktop/50_yr_Historic/NECN/LAI-40.img")
LAI40<-mean(as.data.frame(LAI40[!LAI40$LAI.40==0])[,1])
LAI45<-raster("C:/Users/zacha/Desktop/50_yr_Historic/NECN/LAI-45.img")
LAI45<-mean(as.data.frame(LAI45[!LAI45$LAI.45==0])[,1])

LAIS<-c(LAI5,LAI10,LAI15,LAI20,LAI25,LAI30,LAI35,LAI40,LAI45)

plot(seq(5,45,5),LAIS,xlab="Years",ylab="LAI m2/m",cex.lab=1.5,cex.axis=1.5,main="Landscape mean LAI")



mean(6.9,5.4,5.4,6.7,6.0,5.2,4.7,4.5,7.2,2.7,4.1,5.2,8.2,6.0)
mean(as.data.frame(LAI5[!is.na(LAI5$LAI.5)])[,1])
```

Bolstad, Vose and McNulty site LAI between 2.7 and 8.2 with a median of 5.8 m2, our landscape averaged 6.13 in the first time NECN time step (timestep 5). In calibration runs with no disturbance, Landscape mean LAI got up to 9.84 in 50 years. 



```{r}
# LAI1<-raster("C:/Users/zacha/Desktop/50_yr_Historic/NECN/LAI-1.img")
# LAI1[LAI1$LAI.1==0]<-NA
# hist(LAI1$LAI.1)
# LAI_DF<-as.data.frame(LAI1$LAI.1)
# 
# AG_NPP1<-raster("C:/Users/zacha/Desktop/50_yr_Historic/NECN/AG_NPP-1.img")
# 
# AG_NPP1[AG_NPP1$AG_NPP.1==0]<-NA
# AG_NPP_DF<-as.data.frame(AG_NPP1$AG_NPP.1)
# 
# NPP_LAI<-cbind(AG_NPP_DF,LAI_DF)
# NPP_LAI<-na.omit(NPP_LAI)
# Sampledraw<-sample(seq(1:446966),10000)
# 
# plot(NPP_LAI$LAI.1[Sampledraw],NPP_LAI$AG_NPP.1[Sampledraw]/100,ylim=c(0,12))
# Model<-lm(NPP_LAI$AG_NPP.1[Sampledraw]/100~NPP_LAI$LAI.[Sampledraw])
# summary(Model)
# 
# plot(seq(1,10),5.00+.297614*seq(1,10),ylim=c(0,13))
# points(seq(1,10),3.6+0.94*seq(1,10),col="red")
```

#### Net ecosystem exchange. 



```{r,fig.width=10.0,fig.height=7.0}
AG_NPP<-NECN_s[,c("Time","ClimateRegionName","NEEC")]
theme_set(theme_classic(base_size = 20))
p<-ggplot(AG_NPP, aes(x=Time, y=NEEC, group=ClimateRegionName)) +
  geom_line(aes(color=ClimateRegionName))+
  geom_point(aes(color=ClimateRegionName))
p
```

#### Soil organic matter total carbon. 

```{r pressure,fig.width=10.0,fig.height=7.0}
AG_NPP<-NECN_s[,c("Time","ClimateRegionName","SOMTC")]
theme_set(theme_classic(base_size = 20))
p<-ggplot(AG_NPP, aes(x=Time, y=SOMTC, group=ClimateRegionName)) +
  geom_line(aes(color=ClimateRegionName))+
  geom_point(aes(color=ClimateRegionName))+
  labs(title="Soil Organic Matter Total Carbon",
        x ="Timestep", y = "g C m-2")
p
```



```{r}
AG_NPP<-NECN_s[,c("Time","ClimateRegionName","C_SOM2")]
theme_set(theme_classic(base_size = 20))
p<-ggplot(AG_NPP, aes(x=Time, y=C_SOM2, group=ClimateRegionName)) +
  geom_line(aes(color=ClimateRegionName))+
  geom_point(aes(color=ClimateRegionName))
p
```

```{r}
head(NECN_s)
```
 
 