---
title: "Generating Baseflow & Stormflow Rasters"
author: "kj"
date: "9/23/2020"
output:
  html_document:
    toc: true
    number_sections: true
---
This Rmd explains the data sources and processing to create these rasters for NECN.<br>

# Data Sources 
## Baseflow Data Sources:<br>

1. An existing baseflow raster
  + Downloaded here: https://water.usgs.gov/GIS/metadata/usgswrd/XML/bfi48grd.xml
    + This dataset was simply downloaded and resampled. We did not have an existing baseflow raster.

## Stormflow Data Sources:<br>

1) SSURGO Soils Data 
  + Downloaded NC, TN, SC, GA here: https://websoilsurvey.sc.egov.usda.gov/App/WebSoilSurvey.aspx
    + Under "US General Soils Map - STATSGO2" selected states
  
2) NLCD Data
  + Downloaded here: https://www.mrlc.gov/data
    + Selected 2016 NLCD CONUS
  
3) Slope Data
  + Downloaded here: https://dwtkns.com/srtm/
    + Selected the 2 90m res tiles that overlap southern Apps AOI
  

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)

```


# Baseflow

```{r}
library(tidyverse)
library(raster)
library(rgdal)
library(gdalUtils)
library(gdalUtilities)


wd<-"C:\\Users\\thebrain\\Dropbox\\DEAL_lab\\S_Apps_Project\\NECN\\bfi48grd\\bfi48grd\\arctar00000\\bfi48grd"
#open the downloaded baseflow raster
dpath<-paste0(wd)#,"\\bfi48grd\\bfi48grd")
#retrieving driver for adf format
x <- new("GDALReadOnlyDataset", dpath)
getDriver(x)
getDriverLongName(getDriver(x))
xx<-asSGDF_GROD(x)
#assign to baseflow object
baseflow <- raster(xx)


#read in ecoreg map to set map criteria (hardcoded this path, but it can be any S.Apps map - just use it
#as template for extent/res)
ecoreg <- raster("C:\\Users\\thebrain\\Dropbox\\DEAL_lab\\S_Apps_Project\\Project-Southern-Appalachians-2018\\Models\\LANDIS_Sapps_Active_v1_3\\MR_FourEcoregions.tif")

#creating bounding box around ecoreg raster
e <- extent(ecoreg)

# coerce to a SpatialPolygons object
to_crop_to <- as(e, 'SpatialPolygons')  

#declare it's crs (same as ecoreg raster that it was created from)
crs(to_crop_to)<-crs(ecoreg)


#reading this in because cropping makes for much smaller raster handling
#since reprojecting baseflow raster is time consuming, 
#set cropping extent polygon to projection of baseflow
to_crop<-spTransform(to_crop_to,crs(baseflow))

#crop baseflow to a app raster map extents 
bf_shrink <- crop(baseflow, to_crop)

#now, project the cropped baseflow raster to s.app map project (using ecoreg raster)
baseflow_utm <- projectRaster(bf_shrink,crs=crs(ecoreg),res=res(ecoreg)[1])

#reasmple for correct resolution, extent
baseflow_resamp<-resample(baseflow_utm, ecoreg, method="bilinear")

baseflow_resamp
#summary yields there are no missing values (min&max not NA's)


fun <- function(x) { x /100 }
baseflow_01 <- calc(baseflow_resamp, fun)

#check extent and res match ecoregion map
extent(baseflow_01)== extent(ecoreg)
res(baseflow_01) == res(ecoreg)

#write it out
#writeRaster(baseflow_01,"Baseflow.tif",overwrite=T)

```

# Runoff Coefficient

## Raw Slope Data
```{r eval= FALSE}

wd<-"C:\\Users\\thebrain\\Dropbox\\DEAL_lab\\S_Apps_Project\\NECN"


#read in the DEM data (donwloaded in two tiles)
dem_south<-raster(paste0(wd,"\\creating_runoff_coefficient\\90mresDEM\\srtm_20_06\\srtm_20_06.tif"))
dem_north<-raster(paste0(wd,"\\creating_runoff_coefficient\\90mresDEM\\srtm_20_05\\srtm_20_05.tif"))

#merge the dems
dem<-merge(dem_north,dem_south)


#project data to match ecoreg raster (read in above for baseflow - used as template throughout)
dem_utm <- projectRaster(dem,crs=crs(ecoreg),res=res(ecoreg)[1])

#get extent, res, etc. correct
dem_resamp<-resample(dem_utm, ecoreg, method="bilinear")

#create outpath
out_path<-paste0(wd,"\\creating_runoff_coefficient\\dem_utm_resamp.tif")
#write it out cause it takes awhile
writeRaster(dem_resamp,out_path,overwrite=TRUE)
```

### Converting to Percent Slope
Read in the resampled DEM raster from previous chunk to do operations.

```{r}

#path ro previously created raster
out_path<-paste0(wd,"\\creating_runoff_coefficient\\dem_utm_resamp.tif")

#read back in 
dem_forslopecalc<-raster(out_path)

#convert this raster to slope
slope_degrees<-terrain(dem_forslopecalc, opt= "slope",unit="degrees", neighbors=8)

#function for converting degrees to percent slope
perc_slope<-function(x){
   tan(x*pi/180)
}

#use raster calc to create percentage slope raster using function above
slope_percent<-calc(slope_degrees, fun=perc_slope)

#write out the percent slope raster
#writeRaster(slope_percent,"perc_slope.tif")

```

## Raw NLCD Data

```{r, eval=FALSE}

wd<-"C:\\Users\\thebrain\\Dropbox\\DEAL_lab\\S_Apps_Project\\NECN\\creating_runoff_coefficent"

#read in NLCD 
nlcd <- raster("NLCD_2016_Land_Cover_L48_20190424\\NLCD_2016_Land_Cover_L48_20190424.img")

#create the template extent from standard ecoregion raster
e <- extent(ecoreg)

#coerce e to a SpatialPolygons object
to_crop_to <- as(e, 'SpatialPolygons') 

#set the crs the same as ecoreg
crs(to_crop_to)<-crs(ecoreg)

#project it to match nlcd projection because quicker to project e, crop/resample, then project back
to_crop<-spTransform(to_crop_to,crs(nlcd))

#crop dem to sapp aoi to make smaller for projecting/resampling raster
nlcd_shrink <- crop(nlcd, to_crop)

#now project data back to match ecoreg, using ngb method because it is categorical
nlcd_utm <- projectRaster(nlcd_shrink,crs=crs(ecoreg),res=res(ecoreg)[1],method='ngb')

#and finally, making a smaller nlcd at the correct extent/res for ecoregion
nlcd_resamp <- resample(nlcd_utm,ecoreg,method="ngb")

#create outpath
out_path<-paste0(wd,"\\creating_runoff_coefficient\\nlcd_resampled.tif")

#write it out cause it takes awhile
writeRaster(nlcd_resamp,out_path,overwrite=TRUE)

```


### Converting to 3 Forest Classes

There are pixels within our AOI maps that are not designated as forest in 2016 NLCD. WIth LANDIS's assumptions of a forested landscape, we want to convert all landcover within the AOI to forest. Since there are different runoff coefficient implications across types of forest, below I try to assure that each pixel, if not already forested, gets assigned the forest type closest to it. If two forest types are equidistant, the pixel gets assigned to the dominant forest class in the map. 

This process works by setting forest types to NA's, then doing different distance calculations on a per cell basis to each forest type, then stacking those 3 distance rasters and choosing the raster (reflects forest type) with the shortest distance. 

```{r,eval=FALSE}

#reclassifying deciduous forest (everywhere there's a 41, make it NA)
decid <- reclassify(nlcd_forreclass, cbind(41, NA))
#reclassifying deciduous forest (everywhere there's a 42, make it NA)
ever <- reclassify(nlcd_forreclass, cbind(42, NA))
#reclassifying deciduous forest (everywhere there's a 43, make it NA)
mix <- reclassify(nlcd_forreclass, cbind(43, NA))

#distance to decid forest NA's 
decid_dist <- distance(decid) #this takes considerable time
writeRaster(decid_dist,paste0(wd,"\\creating_runoff_coefficient\\decid_dist.tif")) #so writing it out
#distance to evergreen forest NA's 
ever_dist <- distance(ever) #this takes considerable time
writeRaster(ever_dist,paste0(wd,"\\creating_runoff_coefficient\\ever_dist.tif")) #so writing it out
#distance to mixed forest NA's 
mix_dist<- distance(mix)
writeRaster(mix_dist,paste0(wd,"\\creating_runoff_coefficient\\mix_dist.tif"))

```


```{r}

#since above chunk turned to eval=F, reading in the created nlcd raster
nlcd_forreclass<-raster(out_path)


#reading in distance rasters created in above chunk (eval=FALSE)
#distance to decidious forest NA cells
decid_dist<-raster(paste0(wd,"\\creating_runoff_coefficient\\decid_dist.tif"))
#distance to evergreen forest NA cells
ever_dist<-raster(paste0(wd,"\\creating_runoff_coefficient\\ever_dist.tif"))
#distance to mixed forest NA cells
mix_dist<-raster(paste0(wd,"\\creating_runoff_coefficient\\mix_dist.tif"))

#stack up the distance rasters
s <- stack(decid_dist,mix_dist,ever_dist)
#name them to keep things straight
names(s) <- c("decid_dist","mix_dist","ever_dist")

#find the minimum distance (from raster stack) to a given cell
x<-which.min(s)
# x_master<-x
# copy<-x

#where the first raster is the minimum dist, assign class 43 (deciduous forest)
r1 <- reclassify(x, cbind(1, 43))
#where the second raster is the minimum dist, assign class 41 (mixed forest)
#bump by 100 for easier deciphering in the final reclass
r2<- reclassify(r1 , cbind(2, 141))

#create a reclassification matrix based on the original nlcd valuesd
#0-40.5 = 0
#44-100 = 0
mat<-c(0,40.5,0,43.5,100,0)
rclmat <- matrix(mat, ncol=3, byrow=TRUE)
rec_nlcd<-reclassify(nlcd_resamp,rclmat)


#change only non-forest values from the original nlcd
rec_nlcd<-reclassify(nlcd_forreclass,rclmat)

#stack of the forest type reclassified raster, and the reclassified original nlcd
stack_to_sum<-stack(r2,rec_nlcd)
#sum them up
rs1<-calc(stack_to_sum, sum)

#based on the output values and knowing we only want the 3 forest types, reclassify based on the possible combinations
mat<-c(84,41,85,42,86,43,141,41,182,41,183,42,184,43)
rclmat <- matrix(mat, ncol=2, byrow=TRUE)
hopeful<-reclassify(rs1,rclmat)

plot(hopeful,col=c("forest green","dark green","light green"))

out_path<-paste0(wd,"\\creating_runoff_coefficient\\nlcd_forestfilled.tif")
writeRaster(hopeful,out_path)

```

## Soils Data
Similar to code developed in Soils.Rmd to handle SSURGO data, but wrote this such that entire workflow is within this RMD. Source of data referenced at top of RMD. 

### Reading in TN, GA, SC, & NC soils shapefiles and tables

This code chunk creates a shapefile where every MUKEY polygon has one of the 12 dominant soil textures assigned to it. 

```{r, eval=FALSE}

#make a list of all the states you want to read in and join data for
states<-c("NC","TN","GA","SC")

#create empty list to receive list of datasets within loop
merged<-list()

#iterate through the number of states in the states list above
for (i in 1:length(states)){
  #checking loop iteration
print(i)
  #get the state in string format to build the file paths below
state<-states[i]

#go get the states shapefile
shp<-shapefile(paste0("wss_gsmsoil_",state,"_[2016-10-13]\\wss_gsmsoil_",state,"_[2016-10-13]\\spatial\\gsmsoilmu_a_",state,".shp"))

#got get the states tables, in this case, want the :

#table and their fields of interest for join
#1)component = mukey
#2)chorizon = cokey
#3)chtexturegrp = chkey
#4)chtexture = chtgkey

#state<-"GA" #used this to test the loop

component<-paste0("wss_gsmsoil_",state,"_[2016-10-13]\\wss_gsmsoil_",state,"_[2016-10-13]\\tabular\\comp.txt")
cokey<-paste0("wss_gsmsoil_",state,"_[2016-10-13]\\wss_gsmsoil_",state,"_[2016-10-13]\\tabular\\chorizon.txt")
chkey<-paste0("wss_gsmsoil_",state,"_[2016-10-13]\\wss_gsmsoil_",state,"_[2016-10-13]\\tabular\\chtexgrp.txt")

#could be hte chtext table
chtgkey<-paste0("wss_gsmsoil_",state,"_[2016-10-13]\\wss_gsmsoil_",state,"_[2016-10-13]\\tabular\\chtextur.txt")

### testing
#used this to look at a specific state table out of a loop
# testing_tab<-"wss_gsmsoil_NC_[2016-10-13]\\wss_gsmsoil_NC_[2016-10-13]\\tabular\\chorizon.txt"
# tab_test<-as.data.frame(read.table(testing_tab,sep="|",header=FALSE))
#####Reading in soils tables, will merge once everything is read in 
### finished testing

###Read in the component table
#get the table information from the text file
tab_mukey<-as.data.frame(read.table(component,sep="|",header=FALSE))
tab_cokey<-as.data.frame(read.table(cokey,sep="|",header=FALSE))
tab_chkey<-as.data.frame(read.table(chkey,sep="|",header=FALSE))
tab_chtgkey<-as.data.frame(read.table(chtgkey,sep="|",header=FALSE))

#the table data is messy and doesnt read in with column headers, but
# i know i want the MUKEY (based the format) and the columns that specify A,B,C,D
tab_mukey<-tab_mukey[,c(length(tab_mukey)-1,length(tab_mukey))]
tab_cokey<-tab_cokey[,c(length(tab_cokey)-1,length(tab_cokey))]
tab_chkey<-tab_chkey[,c(length(tab_chkey)-1,length(tab_chkey))]
tab_chtgkey<-tab_chtgkey[,c(1,length(tab_chtgkey)-1,length(tab_chtgkey))]


#set the column names to join to the spatial data by

#set mukey 
names(tab_mukey)<-c("MUKEY","COKEY")
#set cokey
names(tab_cokey)<-c("COKEY","CHKEY")
#names(tab_cokey)[length(names(tab_cokey))-1]<-"MUKEY"
#set chkey
names(tab_chkey)<-c("CHKEY","CHTGKEY")
#names(tab_chkey)[length(names(tab_chkey))-2]<-"soil_text"
#names(tab_cokey)[length(names(tab_cokey))-1]<-"COKEY"
names(tab_chtgkey)<-c("soil_text","CHTGKEY","CHKEY")


#### MERGING SOILS TABLE WITH SHAPEFILE DATA
#merge the 3 tables first
muk_cok<-merge(tab_mukey,tab_cokey,"COKEY")
muk_cok_chkey<-merge(muk_cok,tab_chkey,"CHKEY")
muk_cok_ch_chtg<-merge(muk_cok_chkey,tab_chtgkey,"CHTGKEY")


#then merge single table with shapefile
#assign the new output spatial data to a list variable
merged[i]<-merge(shp,muk_cok_ch_chtg,key="MUKEY",duplicateGeoms=TRUE)

}


#merge shapefiles in list, to create one master shapefile
all_states1<-rbind(merged[[1]],merged[[2]],merged[[3]],merged[[4]])

#create copy so no need to remake shapefile as I iterated on this process
all_states<-all_states1

#clean up the soil textures, removing na's and blanks
all_states<-all_states[!is.na(all_states$soil_text),]
all_states<-all_states[all_states$soil_text!="",]


#soil type lookup table, want only the main descriptors
textures_toedit<-unique(all_states$soil_text)

#have to change some of the terminology to map to the appropriate, existing soil texture name
all_states$soil_text[all_states$soil_text=="Fine sandy loam"]<-"Sandy loam"
all_states$soil_text[all_states$soil_text=="Very fine sandy loam"]<-"Sandy loam"
all_states$soil_text[all_states$soil_text=="Coarse sandy loam"]<-"Sandy loam"
all_states$soil_text[all_states$soil_text=="Loamy coarse sand"]<-"Loamy sand"
all_states$soil_text[all_states$soil_text=="Loamy fine sand"]<-"Loamy sand"
all_states$soil_text[all_states$soil_text=="Coarse sand"]<-"Sand"
all_states$soil_text[all_states$soil_text=="Fine sand"]<-"Sand"

#make sure textures are in ascending order of runoff!
#make sure all textures are mapped to one of the representative 12 textures 
textures_toedit<-unique(all_states$soil_text)

#assign them values (integers to rasterize)
soil_drain_value<-c(9,11,12,8,3,10,7,4,5,1,2,6)

#now, replace everywhere in the dataframe where the 12 texture exist with numbers
#create a table to merge (has soil text, and drain values to average)
my_lookup<-as.data.frame(cbind(textures_toedit,as.numeric(soil_drain_value)))


#name columns correctly so merge will work
names(my_lookup)<-c("soil_text","drain_value_toavg")
my_lookup$drain_value_toavg<-as.integer(my_lookup$drain_value_toavg)

#my_lookup<-my_lookup[order(my_lookup$drain_value_toavg),]

#want to select a single row for each MUKEY, then remove all other columns
#this serves as the basis for the join
just_mukey<-all_states[,"MUKEY"]
all_states2<- aggregate(just_mukey, "MUKEY") #aggregate function is super useful for polygons!

#selecting dominant soil texture per MUKEY polygon, since it is a many to one relationship
all_states_bymuk <- 
  
  all_states@data %>%                    # take the data.frame "data"  # Using "data", filter out all rows with NAs in aa 
  group_by(MUKEY,soil_text) %>%          # Then, with the filtered data, group it by "bb"
  add_tally(sort=TRUE) %>%
  group_by(MUKEY)%>%
  slice(1)# Now summarise with unique elements per group

#join!
joined<-merge(all_states2,all_states_bymuk,by="MUKEY",duplicateGeoms=F)


#NOW, need to rasterize the vector
#reproject shapefile to match ecoreg raster
all_states_proj3<- spTransform(joined,
crs(ecoreg))

#only want MUKEY id and soil_texture
all_states_proj<-all_states_proj3[,c(1,8)]
colnames(all_states_proj@data)<-c("MUKEY","soil_text")

out_path<-paste0(wd,"\\creating_runoff_coefficient\\with_simple_text5.shp")

#write out to shapefile for safe keeping
shapefile(all_states_proj,out_path,overwrite=TRUE)

```

### Converting created soils shapefile to raster

Now, for use in the runoff coefficient, we need to rasterize the shapefile. 

```{r, eval=FALSE}

require(sf)
require(rgeos)
require(rgdal)
library(fasterize)

#create empty raster
r<-raster()
#set the crs, extent, and resolution
crs(r)<-crs(ecoreg)
extent(r)<-extent(ecoreg)
res(r)<-res(ecoreg)

#read in shapefile created above
all_states_proj<-shapefile(out_path)

#reassignmnt to save backtracking objects while troubleshooting
all_states_proj4<-all_states_proj


#need to create factor levels to rasterize
all_states_proj4$soil_fact<-factor(all_states_proj4$soil_text)
levels(all_states_proj4$soil_fact) <- 1:11
all_states_proj4$soil_int<-as.numeric(all_states_proj4$soil_fact)

#convert to sf object to rasterize
shp <- st_as_sf(all_states_proj4)

# rasetrize and write
r.fas <- fasterize(shp, r, field = "soil_int")

out_path<-paste0(wd,"\\creating_runoff_coefficient\\fasterize_filename3.tif")
writeRaster(r.fas, out_path, format="GTiff", overwrite=TRUE)



# code below is just testing which of the soils values exist in our AOI, instead of the entire map
# soil values were of use when creating lookup tables in the final step to assign runoff coefficient values


#read in dissolved aoi for masking
diss_aoi<-shapefile("C:\\Users\\thebrain\\Dropbox\\DEAL_lab\\S_Apps_Project\\diss_aoi\\buffered3.shp")
#clip raster to AOI to determine what soils are in area, this will inform how many dimensions i need in the final table
soils_inaoi<-raster::mask(r.fas,diss_aoi)

table(getValues(soils_inaoi))

#values 1,2,3,7,8,9,10,11 are left...
#determine which original values these map back to

#1 = Clay
#2 = Clay loam
#3 = Loam
#7 = Sandy clay loam
#8 = Sandy Loam
#9 = Silt loam
#10 = Silty clay
#11 = Silty clay loam

```

# Creating Runoff Coeefficint Raster

This code chunk stacks the rasters generated above (slope, nlcd, and soils), then assigns runoff coeffiecient values based on a lookup table. Lookup table from this pub: 

Y. B. Liu and F. D. Smedt, “WetSpa Extension, A GIS-based Hydrologic Model for Flood Prediction and Watershed Management,” p. 126.


```{r}

#read in soils raster created above 
soils<-raster(out_path)

#make sure rasters are stacked: 
#r1 = soil
#r2 = nlcd
#r3 = slope
st<-stack(soils,hopeful,slope_percent)

```

The lookup table bases the runoff coefficient values on slope and soil type. From other literature, the general difference between forest type, all other conditions equal is ~0.02. Below are matrices create for each forest type, with soil type and slope, with an adjustment of + 0.2 for evergreen forest (more runoff) and -0.02 for deciduous forest (less runoff), all relative to mixed forest. 

```{r}
#the nlcd values should be just a tweak up or down 
#in the overall raster calculation, since all forested
#refer to the paper for reclassification methods

#for the soils raster, these are the soils associated with values

#1 = Clay
#2 = Clay loam
#3 = Loam
#7 = Sandy clay loam
#8 = Sandy Loam
#9 = Silt loam
#10 = Silty clay
#11 = Silty clay loam

#need to adjust matrice indexing below so only loop through the above soil types

#hence making 3 different matrices for forest cover type
mixed_forest_0.5<-c(0.03,0.07,0.10,0.13,0.17,0.20,0.23,0.27,0.30,0.33,0.37,0.40)
mixed_forest_0.5to5<-mixed_forest_0.5+0.04
mixed_forest_5to10<-mixed_forest_0.5to5+0.06
mixed_forest_10to25<-mixed_forest_5to10+0.12
mixed_forest_25andup<-mixed_forest_10to25+0.14

mixed_forest_mat<-matrix(c(mixed_forest_0.5,mixed_forest_0.5to5,mixed_forest_5to10,mixed_forest_10to25,mixed_forest_25andup),nrow=5,ncol=12)

decid_forest_0.5<-mixed_forest_0.5 - 0.02
decid_forest_0.5to5<-mixed_forest_0.5to5 - 0.02
decid_forest_5to10<-mixed_forest_5to10 - 0.02
decid_forest_10to25<-mixed_forest_10to25 - 0.02
decid_forest_25andup<-mixed_forest_25andup - 0.02

decid_forest_mat<-matrix(c(decid_forest_0.5,decid_forest_0.5to5,decid_forest_5to10,decid_forest_10to25,decid_forest_25andup),nrow=5,ncol=12)

ever_forest_0.5<-mixed_forest_0.5 + 0.02
ever_forest_0.5to5<-mixed_forest_0.5to5 + 0.02
ever_forest_5to10<-mixed_forest_5to10 + 0.02
ever_forest_10to25<-mixed_forest_10to25 + 0.02
ever_forest_25andup<-mixed_forest_25andup + 0.02

ever_forest_mat<-matrix(c(ever_forest_0.5,ever_forest_0.5to5,ever_forest_5to10,ever_forest_10to25,ever_forest_25andup),nrow=5,ncol=12)

```

Once the matrices are created, the final raster is generated by looping through these forest type matrices and assigning values to each cell. 

```{r}

### now for conditionals to create final raster
final<-raster()
extent(final)<-extent(ecoreg)
res(final)<-res(ecoreg)
crs(final)<-crs(ecoreg)

r1=st[[1]]
r2=st[[2]]
r3=st[[3]]

forest_vals<-c(41,42,43)
forest_mat<-list(mixed_forest_mat,decid_forest_mat,ever_forest_mat)

for (i in 1:length(forest_vals)){
  
  for_val<-forest_vals[i]
  for_mat<-forest_mat[[i]]
  
###clay (column 12 in matrix) & value 1 in soil raster, mixed forest value 42 nlcd
final[r1== 1 & r2==for_val & r3<0.5] <- for_mat[1,12]
final[r1== 1 & r2==for_val & (0.5<=r3 & r3<5)] <- for_mat[2,12]
final[r1== 1 & r2==for_val & (5<=r3 & r3<10) ] <- for_mat[3,12]
final[r1== 1 & r2==for_val & (10<=r3 & r3<25)] <- for_mat[4,12]
final[r1== 1 & r2==for_val & (25<=r3 & r3<100)] <- for_mat[5,12]

###clay loam (column 8 in matrix) & value 2 in soil raster, mixed forest value 42 nlcd
final[r1==2  & r2==for_val & r3<0.5] <- for_mat[1,8]
final[r1==2  & r2==for_val & (0.5<=r3 & r3<5)] <- for_mat[2,8]
final[r1==2   & r2==for_val & (5<=r3 & r3<10) ] <- for_mat[3,8]
final[r1==2   & r2==for_val & (10<=r3 & r3<25)] <- for_mat[4,8]
final[r1==2  & r2==for_val & (25<=r3 & r3<100)] <- for_mat[5,8]

###loam (column 4 in matrix) & value 3 in soil raster, mixed forest value 42 nlcd
final[r1==3  &  r2==for_val & r3<0.5] <- for_mat[1,4]
final[r1==3 &  r2==for_val & (0.5<=r3 & r3<5)] <- for_mat[2,4]
final[r1==3  &  r2==for_val & (5<=r3 & r3<10)] <- for_mat[3,4]
final[r1==3 &  r2==for_val & (10<=r3 & r3<25)] <- for_mat[4,4]
final[r1==3 &  r2==for_val & (25<=r3 & r3<100)] <- for_mat[5,4]

###sandy loam (column 3 in matrix) & value 8 in soil raster, mixed forest value 42 nlcd
final[r1==8  &  r2==for_val & r3<0.5] <- for_mat[1,3]
final[r1==8  &  r2==for_val & (0.5<=r3 & r3<5)] <- for_mat[2,3]
final[r1==8  &  r2==for_val & (5<=r3 & r3<10)] <- for_mat[3,3]
final[r1==8  &  r2==for_val & (10<=r3 & r3<25)] <- for_mat[4,3]
final[r1==8  &  r2==for_val & (25<=r3 & r3<100)] <- for_mat[5,3]

###sandy loam (column 3 in matrix) & value 8 in soil raster, mixed forest value 42 nlcd
final[r1==8  &  r2==for_val & r3<0.5] <- for_mat[1,3]
final[r1==8  &  r2==for_val & (0.5<=r3 & r3<5)] <- for_mat[2,3]
final[r1==8  &  r2==for_val & (5<=r3 & r3<10)] <- for_mat[3,3]
final[r1==8  &  r2==for_val & (10<=r3 & r3<25)] <- for_mat[4,3]
final[r1==8  &  r2==for_val & (25<=r3 & r3<100)] <- for_mat[5,3]

###silt loam (column 5 in matrix) & value 9 in soil raster, mixed forest value 42 nlcd
final[r1==9 &  r2==for_val & r3<0.5] <- for_mat[1,11]
final[r1==9  &  r2==for_val & (0.5<=r3 & r3<5)] <- for_mat[2,5]
final[r1==9 &  r2==for_val & (5<=r3 & r3<10) ] <- for_mat[3,5]
final[r1==9  &  r2==for_val & (10<=r3 & r3<25)] <- for_mat[4,5]
final[r1==9  &  r2==for_val & (25<=r3 & r3<100)] <- for_mat[5,5]

###silty clay (column 11 in matrix) & value 10 in soil raster, mixed forest value 42 nlcd
final[r1==10  &  r2==for_val & r3<0.5] <- for_mat[1,11]
final[r1==10 &  r2==for_val & (0.5<=r3 & r3<5)] <- for_mat[2,11]
final[r1==10  &  r2==for_val & (5<=r3 & r3<10) ] <- for_mat[3,11]
final[r1==10 &  r2==for_val & (10<=r3 & r3<25)] <- for_mat[4,11]
final[r1==10  &  r2==for_val & (25<=r3 & r3<100)] <- for_mat[5,11]

###Silty clay loam (column 9 in matrix) & value 11 in soil raster, mixed forest value 42 nlcd
final[r1==11 &  r2==for_val & r3<0.5] <- for_mat[1,9]
final[r1==11 &  r2==for_val & (0.5<=r3 & r3<5)] <- for_mat[2,9]
final[r1==11 &  r2==for_val & (5<=r3 & r3<10)] <- for_mat[3,9]
final[r1==11 &  r2==for_val & (10<=r3 & r3<25)] <- for_mat[4,9]
final[r1==11&  r2==for_val & (25<=r3 & r3<100)] <- for_mat[5,9]
}

plot(final)

out_path<-paste0(wd, "\\creating_runoff_coefficient\\Stormflow.tif")
writeRaster(final,out_path)

```
