---
title: "Southern Appalachians Soils"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

> Soils File 

> To create the NECN soil inputs we combined SSURGO data, deadwood data from the US Forest Invettory and Analysis Program , baseflow and storm flow approximations from ( KATE), and data on soil carbon and nitrogen. This process can be seen at https://github.com/LANDIS-II-Foundation/Project-Southern-Appalachians-2018/tree/master/Parameterizing/Soils. Maps for depth, drainage, flood frequency sand, and clay percentage, field capacity and wilting point were derived from the USGS gssurgo dataset, subset to the study extent. These soils maps were aggregated from there an original resolution of (10m) were aggregated to the study resolution of 250m. Total carbon was calculated using the CONUS level carbon maps scale to the resolution of the study area (West, 2014). The guidelines in the Century
the manual was used to divide the SOM into the fast, slow, and passive pools and then calculate the
total N in each pool (Parton 2013). Deadwood and roots were calculated by interpolating between FIA sites for dead wood and assuming dead roots made up 1/3 or dead wood values. 
-ZR


* Parton, W. 2013. CENTURY Soil Organic Matter Model Environment. Technical
Documentation. Agroecosystem Version 3.0. USDA-ARS, Forest Collins, CO. 
* West, T.O. 2014. Soil Carbon Estimates in 20-cm Layers to 1-m Depth for the Conterminous US, 1970-1993. Data set. Available on-line [http://daac.ornl.gov] from Oak Ridge National Laboratory Distributed Active Archive Center, Oak Ridge, Tennessee, USA. http://dx.doi.org/10.3334/ORNLDAAC/1238
* Soil Survey Staff, Natural Resources Conservation Service, United States Department of Agriculture. Soil Survey Geographic (SSURGO) Database for [TN,GA,NC,SC]. Available online. Accessed [10/17/2019].






This is a methodology for creating the soil and hydrology maps necessary to Run LANDIS-II NECN. These methods were provided by Melissa Lucash and I want to thank her for sharing them. 


The Maps needed to run LANDIS-II are 

* Soil Depth ^1^
* Soil Drain ^1^
* Base Flow to Streams ^4^
* Storm Flow to Streams ^4^
* Field Capacity ^1^
* Wilting Point ^1^
* Percent Sand  ^1^
* Percent Clay  ^1^
* Soil Maps representing 4 layers of carbon pools ^2^
* Soil Maps representing 4 layers of nitrogen pools ^2^
* Dead Wood on the Surface ^3^
* Dead Wood of Coarse Roots ^3^

All of the Maps 1 are derived from the USGS ggsurgo database. The Maps 2 are derived from total soil carbon maps and estimations of each pool. The Maps 3 is interpolated from FIA data.
BaseFlow and Storm Flow are treated as stationary variables in this simulation. 

For more information on these parameters visit https://drive.google.com/file/d/1RrDSn0xIA7p5hHxcWx-bWnaBzNo5SwdA/view




I began by getting the carbon and nitrogen Maps. I started with a total soil carbon map(West 2014), reprojected it, cut to the extent
and then used estimated ratios of carbon in each pool (surface, fast, medium and slow) as well as C: N ratios and Dr. Lucash's work to
create the soil maps. 

As a fraction of total carbon each carbon pool is:

* SOM1surfC=.01
* SOM1soilC=.02
* SOM2C=.59
* SOM3C=.38

Each nitrogen map is then created by multiplying the carbon in that pool by: 

* SOM1surfN=.1
* SOM1soilN=.1
* SOM2N=.04
* SOM3N=.118

A minimum value of 2.0 was set for the nitrogen value to avoid complete lack of N in some stands by having low soil carbon 



Source: West, T.O. 2014. Soil Carbon Estimates in 20-cm Layers to 1-m Depth for the Conterminous US, 1970-1993. Data set. Available on-line [http://daac.ornl.gov] from Oak Ridge National Laboratory Distributed Active Archive Center, Oak Ridge, Tennessee, USA. http://dx.doi.org/10.3334/ORNLDAAC/1238



```{r python stuff,message=FALSE,warning=FALSE,include=FALSE,eval=FALSE}

knitr::opts_chunk$set(echo=FALSE)

library(reticulate)
use_condaenv("basic")


virtualenv_list()
```



```{python,include=FALSE,eval=FALSE,message=FALSE,warning=FALSE}


import geopandas as gp
import rasterio as rt
import rasterio.mask
import gdal 
from rasterio.mask import mask
from rasterio.crs import CRS
import numpy as np
import pandas as pd
import matplotlib.pyplot as pltb
```




```{python,include=FALSE,eval=FALSE,message=FALSE,warning=FALSE}

InDir="R:/fer/rschell/Robbins/Sapps/Model_Prep/Sapps_maps_2_18"
##########Functions

def getFeatures(gdf):
    """Function to parse features from GeoDataFrame in such a manner that rasterio wants them"""
    import json
    return [json.loads(gdf.to_json())['features'][0]['geometry']]


##Imports
CarbonLayers=["0_20","40_60","60_80","80_100"]
CarDir=(InDir+"/Carbon/")

```


```{python,include=FALSE,eval=FALSE,message=FALSE,warning=FALSE}

for Clayer in CarbonLayers:
    filename=CarDir+"/"+Clayer+".tif"
    input_raster=gdal.Open(filename)
    "create a temp map, This is a weird gdal/rasterio work around"
    output_raster=CarDir+"/temp.tif"
    "reformat raster to the format of AOI"
    gdal.Warp(output_raster,input_raster,dstSRS='EPSG:26917')
    "bring um back"
    data=rt.open(output_raster)
    " get the CRS cod for our projection"    
    crs = CRS.from_epsg(26917)
    #print(CRS.to_string(crs))
    #Lut_tif="C:/Users/zjrobbin/Desktop/Geopandas/temp/practice"+ecoregion+".tif"
    "load in the AOI shape"
    AOI=gp.read_file(InDir+"/Dissolved_AOI.shp",crs={'init':'EPSG:26917'})
   
    "get AOI's crs code"
    geo=AOI.to_crs(crs=data.crs.data)
    
    coords=getFeatures(geo)
    ###Copy the meta data
    out_meta = data.meta.copy()
    
    ####Preform a mask on the raster
    out_img,out_transform=mask(raster=data,shapes=coords,crop=True,nodata=-9999)
    out_meta = data.meta.copy()
    epsg_code = int(data.crs.data['init'][5:])
    out_meta.update({"driver": "GTiff",
                             "height": out_img.shape[1],
                             "width": out_img.shape[2],
                             "transform": out_transform}
                                )
    ######
    out_tif=CarDir+"/"+Clayer+"AOI.tif"
    #######
    with rasterio.open(out_tif, "w", **out_meta) as dest:
        dest.write(out_img)
```


```{python,include=FALSE,eval=FALSE,message=FALSE,warning=FALSE}

SOM1surfC=.01
SOM1soilC=.02
SOM2C=.59
SOM3C=.38
SOM1surfN=.1
SOM1soilN=.1
SOM2N=.04
SOM3N=.118
```



```{python,include=FALSE,eval=FALSE,message=FALSE,warning=FALSE}

final=pd.DataFrame()

for Clayer in CarbonLayers:
    
    Clip=rt.openBugs=rt.open(CarDir+"/"+Clayer+"AOI.tif")
    Clip=np.reshape(Clip.read(1),((Clip.shape[0]*Clip.shape[1]),1))
    clip=pd.DataFrame(Clip)
    clip.columns=[Clayer]
    final=pd.concat([clip,final],axis=1)
Template=rt.open(CarDir+"/"+Clayer+"AOI.tif")
width=Template.width
height=Template.height
projection=Template.crs
RasterStack=final.fillna(-9999)

CarbonTotal=np.sum(RasterStack,axis=1)
CarbonTotal[CarbonTotal==-39996]=-9999
noninenine=CarbonTotal[CarbonTotal!=-9999]
```

```{python,include=FALSE,eval=FALSE,message=FALSE,warning=FALSE}
out_meta.update({"dtype":"float32"})
print( data.meta.copy())
##Needs to be atleast 2000 for the minimum N to be 2.0
 
                                
CarbonTotal[(CarbonTotal < 100)&(CarbonTotal > (-9999))]=100
new_output=rt.open(InDir+'/Outputs/CarbonTotal.tif', 'w', driver='GTiff',height=height, width=width, count=1, dtype='float32', crs=projection) 
###driver, width(n columns in dataset),height(nrows indataet),count(a count of dataset bands),type, crs,        
Print=np.reshape(CarbonTotal.values,(height,width))
Print=np.float32(Print)
plt.imshow(Print,cmap='inferno',interpolation='nearest')
new_output.write(Print,1)
new_output.close()


SOM1surfCmap=CarbonTotal*SOM1surfC
SOM1surfCmap[SOM1surfCmap==-9999*SOM1surfC]=-9999

SOM1soilCmap=CarbonTotal*SOM1soilC
SOM1soilCmap[SOM1soilCmap==-9999*SOM1soilC]=-9999

SOM2Cmap=CarbonTotal*SOM2C
SOM2Cmap[SOM2Cmap==-9999*SOM2C]=-9999

SOM3Cmap=CarbonTotal*SOM3C
SOM3Cmap[SOM3Cmap==-9999*SOM3C]=-9999

SOM1surfNmap=SOM1surfCmap*SOM1surfN
SOM1surfNmap[SOM1surfNmap==-9999*SOM1surfN]=-9999

SOM1surfNmap[(SOM1surfNmap < 2.0)&(SOM1surfNmap > (-9999))]=2.0

SOM1soilNmap=SOM1soilCmap*SOM1soilN
SOM1soilNmap[SOM1soilNmap==-9999*SOM1soilN]=-9999


cN=SOM1surfCmap/SOM1surfNmap
np.min(cN[(cN!= (1.0))])
np.max(cN[(cN!= (1.0))])

SOM2Nmap=SOM2Cmap*SOM2N
SOM2Nmap[SOM2Nmap==-9999*SOM2N]=-9999

SOM3Nmap=SOM3Cmap*SOM3N
SOM3Nmap[SOM3Nmap==-9999*SOM3N]=-9999

new_output=rt.open(InDir+'/Outputs/SOM1surfCmap.tif', 'w',**out_meta) 
###driver, width(n columns in dataset),height(nrows indataet),count(a count of dataset bands),type, crs,        
Print=np.reshape(SOM1surfCmap.values,(height,width))
Print=np.float32(Print)
plt.imshow(Print,cmap='inferno',interpolation='nearest')
new_output.write(Print,1)
new_output.close()

new_output=rt.open(InDir+'/Outputs/SOM1soilCmap.tif', 'w',**out_meta) 
###driver, width(n columns in dataset),height(nrows indataet),count(a count of dataset bands),type, crs,        
Print=np.reshape(SOM1soilCmap.values,(height,width))
Print=np.float32(Print)
plt.imshow(Print,cmap='inferno',interpolation='nearest')
new_output.write(Print,1)
new_output.close()

new_output=rt.open(InDir+'/Outputs/SOM2Cmap.tif', 'w',**out_meta) 
###driver, width(n columns in dataset),height(nrows indataet),count(a count of dataset bands),type, crs,        
Print=np.reshape(SOM2Cmap.values,(height,width))
plt.imshow(Print,cmap='inferno',interpolation='nearest')
Print=np.float32(Print)
new_output.write(Print,1)
new_output.close()

new_output=rt.open(InDir+'/Outputs/SOM3Cmap.tif', 'w', **out_meta) 
###driver, width(n columns in dataset),height(nrows indataet),count(a count of dataset bands),type, crs,        
Print=np.reshape(SOM3Cmap.values,(height,width))
plt.imshow(Print,cmap='inferno',interpolation='nearest')
Print=np.float32(Print)
new_output.write(Print,1)
new_output.close()

new_output=rt.open(InDir+'/Outputs/SOM1surfNmap.tif', 'w', **out_meta) 

###driver, width(n columns in dataset),height(nrows indataet),count(a count of dataset bands),type, crs,        

Print=np.reshape(SOM1surfNmap.values,(height,width))
plt.imshow(Print,cmap='inferno',interpolation='nearest')
Print=np.float32(Print)
new_output.write(Print,1)
new_output.close()


new_output=rt.open(InDir+'/Outputs/SOM1soilNmap.tif', 'w',**out_meta) 

###driver, width(n columns in dataset),height(nrows indataet),count(a count of dataset bands),type, crs, 

Print=np.reshape(SOM1soilNmap.values,(height,width))
plt.imshow(Print,cmap='inferno',interpolation='nearest')
Print=np.float32(Print)
new_output.write(Print,1)
new_output.close()

new_output=rt.open(InDir+'/Outputs/SOM2Nmap.tif', 'w',**out_meta) 

###driver, width(n columns in dataset),height(nrows indataet),count(a count of dataset bands),type, crs,      

Print=np.reshape(SOM2Nmap.values,(height,width))
plt.imshow(Print,cmap='inferno',interpolation='nearest')
Print=np.float32(Print)
new_output.write(Print,1)
new_output.close()

new_output=rt.open(InDir+'/Outputs/SOM3Nmap.tif', 'w', **out_meta) 

###driver, width(n columns in dataset),height(nrows indataet),count(a count of dataset bands),type, crs,        


Print=np.reshape(SOM3Nmap.values,(height,width))
plt.imshow(Print,cmap='inferno',interpolation='nearest')
Print=np.float32(Print)
new_output.write(Print,1)
new_output.close()

```


Include here are the rasters that this resulted in: 


```{r, fig.height=10.0,fig.width=12.0,align="center",message=FALSE,echo=FALSE,warning=FALSE}
library(raster)
library(RColorBrewer)
```


```{r, fig.height=10.0,fig.width=12.0,align="center",echo=FALSE}
Ramp<-brewer.pal(9,"YlOrBr")

RasterDir<-"Z:/Robbins/Sapps/Model_Prep/Sapps_maps_2_18"
maps=c('SOM1surfCmap','SOM1surfNmap','SOM1soilCmap','SOM1soilNmap','SOM2Cmap','SOM2Nmap','SOM3Cmap','SOM3Nmap')
par(mfrow=c(2,2))
for(map in maps){
Im1<-raster(paste(RasterDir,'/Outputs/',map,'.tif',sep=""))
mv<-max(matrix(Im1))
plot(Im1,zlim=c(0,mv),main=map,col=Ramp)
}
```


****Soils maps in grams per meter 2 

#### USGS SSurgo work



We need to pull together a file for Feild Capacity, Wilt Point, Soil Depth, Flood Frequency, Sand Percentage, and Clay Percentage. These are done using the gssurgo and ssurgo database. The Metadata for the ggsurgo and ssurgo fields can be found at

[SSURGO/STATSGO2 Structural Metadata and Documentation](https://www.nrcs.usda.gov/wps/portal/nrcs/detail/soils/survey/geo/?cid=nrcs142p2_053631)


ggsurgo is gridded to a 10m resolution which is much smaller than we need. So for processing, I aggregated it 50m.

ggsurgo works on a component and map key system, requiring attribute joins to create a map of a single trait. The four tables I join here are the chorizon,component,conmonth, and corestriction tables. 

This is a key to the fields used


* Draiange = component:drainagecl
* Flood Frequency=Conmonth:Flodfreqdcl
* Wiltpoint= chorizon:wfifteenbar:r 
* Feild capacity= wthirdbar:r
* Sand Percentage= Chorizon:sandtotal_R:RV 
* Clay Percentage= Chorizon:claytotal_R:RV 
* Soil depth = corestriction:resdept_r 


Running this requires the map key raster( later noted as *State*\_Raster\_Sub.tif) and the geodatabase file associated with that state 





```{r,message=FALSE,warning=FALSE}

library(rgdal)
library(raster)
library(sf)
library(utils)
library(ggplot2)
w_dir<-"Z:/Robbins/Sapps/Model_Prep/Sapps_maps_2_18/"

setwd(w_dir)
```


```{r,eval=FALSE}
Listofstates<-c("NC","TN","SC","GA")
for(i in Listofstates){

State<-i
NCDB <-paste(w_dir,"Inputs/gSSURGO_",State,".gdb",sep="")
NC_chor<- sf::st_read(dsn = NCDB, layer = "chorizon")
NC_comp<- sf::st_read(dsn = NCDB, layer = "component")
NC_comon<-sf::st_read(dsn=NCDB, layer = "comonth")
NC_restrictive<-sf::st_read(dsn=NCDB, layer='corestrictions')

    

AllComponent<-NC_comp

#AllComponent<-rbind(GA_comp,SC_comp,NC_comp,KY_comp,VA_comp,WV_comp)
AllComponentBridge<-AllComponent[,c(108,109,24)]
#unique(AllComponentBridge$drainagecl)


gsurLUT<-read.csv(paste(w_dir,"Inputs/gssurgoLUT.csv",sep=""))
AllComponentBridge<-merge(AllComponentBridge,gsurLUT,by="drainagecl",all.x=TRUE)
#print(AllcomponentBridge)
AllChorizon<-(NC_chor)
#AllChorizon<-rbind(GA_chor,SC_chor,NC_chor,KY_chor,VA_chor,WV_chor)
#head(AllChorizon)
#colnames(AllChorizon)
UsefulChorizon<-AllChorizon[,c(34,50,61,92,95,170)]
UsefulChorizon[is.na(UsefulChorizon)]<-0
#print(UsefulChorizon)

All_resBridge<-NC_restrictive[,c(4,12)]
print(All_resBridge)
colnames(NC_restrictive)



keytomap<-merge(UsefulChorizon,AllComponentBridge,by="cokey",all.y=TRUE)

    
keytomap<-merge(keytomap,All_resBridge,by="cokey",all.x=TRUE)

print(keytomap)
LUT<-NULL
MeanSand<-mean(keytomap$sandtotal_r[!is.na(keytomap$sandtotal_r)])
keytomap$sandtotal_r[is.na(keytomap$sandtotal_r)]<-MeanSand
row<-cbind(MeanSand,"sandtota_r")
LUT<-rbind(LUT,row)

MeanClay<-mean(keytomap$claytotal_r[!is.na(keytomap$claytotal_r)])
keytomap$claytotal_r[is.na(keytomap$claytotal_r)]<-MeanClay
row<-cbind(MeanClay,"claytotal_r")
LUT<-rbind(LUT,row)

WP<-mean(keytomap$wthirdbar_r[!is.na(keytomap$wthirdbar_r)])
keytomap$wthirdbar_r[is.na(keytomap$wthirdbar_r)]<-WP
row<-cbind(WP,"wthirdbar_r")
LUT<-rbind(LUT,row)

FC<-mean(keytomap$wfifteenbar_r[!is.na(keytomap$wfifteenbar_r)])
keytomap$wfifteenbar_r[is.na(keytomap$wfifteenbar_r)]<-FC
row<-cbind(FC,"wfifteenbar_r")
LUT<-rbind(LUT,row)

DC<-median(keytomap$Landis[!is.na(keytomap$Landis)])
keytomap$Landis[is.na(keytomap$Landis)]<-DC
row<-cbind(DC,"drainagecl")
LUT<-rbind(LUT,row)

Res<-mean(keytomap$resdept_r[!is.na(keytomap$resdept_r)])
keytomap$resdept_r[is.na(keytomap$resdept_r)]<-Res
row<-cbind(Res,"resdept_r")
LUT<-rbind(LUT,row)
LUT<-as.data.frame(LUT)
colnames(LUT)<-c("Mean","Name")

Statemap<- raster(paste(w_dir,"Inputs/",State,"_Raster_Sub.tif",sep=""))
Statedf<-as.data.frame(Statemap)
Statedf[,1][is.na(Statedf[,1])]<-(-9999)
colnames(Statedf)<-"mukey"
print(length(Statemap))

Marker<-1:nrow(Statedf)
Statedf$Marker<-Marker
a<-capture.output(head(Statedf))

keytomap<-keytomap[,-3]
#traits<-c(seq(2,5,1),8,9)
traits<-9
for(i in traits){
  #print(i)
  FeildCap<-NULL
  keytomap2<-NULL
  Name<-names(keytomap)[i]
  FeildCap<-keytomap[,c(i,7)]
  colnames(FeildCap)<-c("FeildCap","mukey")
  FeildCap<-FeildCap[!duplicated(FeildCap$mukey),]
  print(length(FeildCap$mukey))
  
  keytomap2<-merge(x=Statedf,y=FeildCap,by="mukey",all.x=TRUE)
  ExampleRaster<-Statemap
  keytomap3<-keytomap2[order(keytomap2[,2]),]
  map<-as.vector(keytomap3$FeildCap)
  
  
  #Mean<-LUT[LUT$Name==Name,]
  #mean<-Mean[1]
  #map[map==0]<-mean
  #as.numeric(mean)  
  proj<-projection(ExampleRaster)
  
  output_matrix<-matrix(map,nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) #fir
  new_output_raster<-raster(output_matrix,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),ymx=ymax(ExampleRaster), crs=proj)
  plot(new_output_raster)
  new_output_file_name<-paste(w_dir,"Unmerged/",State,Name,".tif",sep="")
  plot(new_output_raster)
  writeRaster(new_output_raster, filename=new_output_file_name, datatype='FLT4S',overwrite=TRUE)
}
}    
    
```

Ran into some trouble with the merge so passed to Q-gis in order to do the merging 


Now we go back to python to cut each merged map to the study area. 


```{python,include=FALSE,eval=FALSE,message=FALSE,warning=FALSE}
#Imports
Cutlayers=["NCclaytotal_r","NCsandtotal_r","NCwthirdbar_r","NCwfifteenbar_r","NCLandis", "NCresdept_r"]
for Clayer in Cutlayers:
    print(Clayer)
    filename=InDir+"/Unmerged/"+Clayer+".tif"
    input_raster=gdal.Open(filename)
    "create a temp map, This is a weird gdal/rasterio work around"
    output_raster=InDir+"/temp.tif"
    "reformat raster to the format of AOI"
    gdal.Warp(output_raster,input_raster,dstSRS='EPSG:32617')
    "bring um back"
    data=rt.open(output_raster)
    " get the CRS cod for our projection"    
    crs = CRS.from_epsg(26917)
    #print(CRS.to_string(crs))
    #Lut_tif="C:/Users/zjrobbin/Desktop/Geopandas/temp/practice"+ecoregion+".tif"
    "load in the AOI shape"
    AOI=gp.read_file(InDir+"/Study_Extent_clean.shp",crs={'init':'EPSG:32617'})
   
    "get AOI's crs code"
    geo=AOI.to_crs(crs=data.crs.data)
    
    coords=getFeatures(geo)
    ###Copy the meta data
    out_meta = data.meta.copy()
    
    ####Preform a mask on the raster
    out_img,out_transform=mask(raster=data,shapes=coords,crop=True,nodata=-9999)
    out_meta = data.meta.copy()
    epsg_code = int(data.crs.data['init'][5:])
    out_meta.update({"driver": "GTiff",
                             "height": out_img.shape[1],
                             "width": out_img.shape[2],
                             "transform": out_transform}
                                )
    ######
    out_tif=InDir+"/Outputs/"+Clayer+"AOI.tif"
    #######
    with rasterio.open(out_tif, "w", **out_meta) as dest:
        dest.write(out_img)
        
```
```{r}

```



These are the resulting maps.



```{r, fig.height=10.0,fig.width=12.0,align="center"}
Ramp<-brewer.pal(9,"YlOrBr")

RasterDir<-"Z:/Robbins/Sapps/Model_Prep/Sapps_maps_2_18"
maps=c("WiltDone","Drain_Done","FeildDone","Soil_Depth_done","Clay_Done","Sand_cut")
par(mfrow=c(2,2))
for(map in maps){
Im1<-raster(paste(RasterDir,'/Outputs/',map,'.tif',sep=""))
mv<-max(matrix(Im1))
plot(Im1,zlim=c(0,mv),main=map,col=Ramp)
}
```



#### Dead Wood
```{python,include=FALSE,eval=FALSE,message=FALSE,warning=FALSE}

import pandas as pd
import geopandas as gp
##import shapely.wkt as shap
from shapely.geometry import Point

InDir="Z:/Robbins/Sapps/Model_Prep/Sapps_maps_2_18/"
##########Functions
```

To calculate dead wood I isolated each FIA plot in the study area within the last cycle. I looked at the total carbon down dead
and interpolated it to the whole study area. I assumed that dead coarse roots make up about a third of that value. 

```{python,include=FALSE,eval=FALSE,message=FALSE,warning=FALSE}
NC_Plt=pd.read_csv(InDir+"Inputs/NC_PLOT.csv",usecols=['PLOT','COUNTYCD','LAT','LON','INVYR','ELEV','STATECD'])                                                                               
NC_Plt['Coordinates']=list(zip(NC_Plt.LON,NC_Plt.LAT))
NC_Plt['Coordinates']=NC_Plt['Coordinates'].apply(Point)


crs={'init':'epsg:4326'}#### Set as what it is then change if needed. 
NC_map=gp.GeoDataFrame(NC_Plt,crs=crs,geometry='Coordinates')
NC_map_26917=NC_map.to_crs({'init':'EPSG:26917'})


#NC_map_26917.plot(color='red')

AOI=gp.read_file(InDir+"/Dissolved_AOI.shp",crs={'init':'EPSG:26917'})
NC_join= gp.sjoin(NC_map_26917, AOI, how="left", op="within")
NC_join=NC_join.dropna()
NC_join.plot(color='red')
NC_join.to_csv('Deadwood/NCPlots.csv')

###SC
SC_Plt=pd.read_csv(InDir+"Inputs/SC_PLOT.csv",usecols=['PLOT','COUNTYCD','LAT','LON','INVYR','ELEV','STATECD'])                                                                                 
SC_Plt['Coordinates']=list(zip(SC_Plt.LON,SC_Plt.LAT))
SC_Plt['Coordinates']=SC_Plt['Coordinates'].apply(Point)


crs={'init':'epsg:4326'}#### Set as what it is then change if needed. 
SC_map=gp.GeoDataFrame(SC_Plt,crs=crs,geometry='Coordinates')
SC_map_26917=SC_map.to_crs({'init':'EPSG:26917'})


#SC_map_26917.plot(color='red')

AOI=gp.read_file(InDir+"/Dissolved_AOI.shp",crs={'init':'EPSG:26917'})
SC_join= gp.sjoin(SC_map_26917, AOI, how="left", op="within")
SC_join=SC_join.dropna()
SC_join.plot(color='red')
SC_join.to_csv('Deadwood/SCPlots.csv')
####TN

TN_Plt=pd.read_csv(InDir+"Inputs/TN_PLOT.csv",usecols=['PLOT','COUNTYCD','LAT','LON','INVYR','ELEV','STATECD'])                                                                                 
TN_Plt['Coordinates']=list(zip(TN_Plt.LON,TN_Plt.LAT))
TN_Plt['Coordinates']=TN_Plt['Coordinates'].apply(Point)


crs={'init':'epsg:4326'}#### Set as what it is then change if needed. 
TN_map=gp.GeoDataFrame(TN_Plt,crs=crs,geometry='Coordinates')
TN_map_26917=TN_map.to_crs({'init':'EPSG:26917'})


#TN_map_26917.plot(color='red')

AOI=gp.read_file(InDir+"/Dissolved_AOI.shp",crs={'init':'EPSG:26917'})
TN_join= gp.sjoin(TN_map_26917, AOI, how="left", op="within")
TN_join=TN_join.dropna()
TN_join.plot(color='red')
TN_join.to_csv('Deadwood/TNPlots.csv')
#####GA


GA_Plt=pd.read_csv(InDir+"Inputs/GA_PLOT.csv",usecols=['PLOT','COUNTYCD','LAT','LON','INVYR','ELEV','STATECD'])                                                                                 
GA_Plt['Coordinates']=list(zip(GA_Plt.LON,GA_Plt.LAT))
GA_Plt['Coordinates']=GA_Plt['Coordinates'].apply(Point)


crs={'init':'epsg:4326'}#### Set as what it is then change if needed. 
GA_map=gp.GeoDataFrame(GA_Plt,crs=crs,geometry='Coordinates')
GA_map_26917=GA_map.to_crs({'init':'EPSG:26917'})


#GA_map_26917.plot(color='red')

AOI=gp.read_file(InDir+"/Dissolved_AOI.shp",crs={'init':'EPSG:26917'})
GA_join= gp.sjoin(GA_map_26917, AOI, how="left", op="within")
GA_join=GA_join.dropna()
GA_join.plot(color='red')
GA_join.to_csv('Deadwood/GAPlots.csv')
mapsmerge=[GA_join,TN_join,SC_join,NC_join]
Appsmaps=pd.concat(mapsmerge)
Appsmaps.plot(color='red')

Appsmaps.to_csv('Deadwood/Appsmaps.csv')
```

```{python,include=FALSE,eval=FALSE,message=FALSE,warning=FALSE}
import pandas as pd
###NC_Plt=pd.read_csv("B:/FIA/NC/NC_COND.csv",usecols=['CN','PLT_CN','INVYR','STATECD','COUNTYCD','PLOT','CARBON_DOWN_DEAD','CARBON_LITTER','CARBON_SOIL_ORG','CARBON_STANDING_DEAD'])                                                                        
###print(list(NC_Plt.columns.values))
States=['NC','SC','TN','GA']
AllST=pd.DataFrame()
for State in States:
    
    C_Plt=pd.DataFrame()
    C_Plt=pd.read_csv(InDir+"Inputs/"+State+"_COND.csv",usecols=['CN','PLT_CN','INVYR','STATECD','COUNTYCD','PLOT','CARBON_DOWN_DEAD','CARBON_LITTER','CARBON_SOIL_ORG','CARBON_STANDING_DEAD'])
    Plt_lst=pd.read_csv(InDir+"Deadwood/"+State+"Plots.csv",usecols=['PLOT','COUNTYCD','LAT','LON','INVYR','ELEV','STATECD','US_L4NAME'])
    
#Needs indents
##Years(2010:2017)
    Years=(Plt_lst.INVYR.unique())
####Yearhasendless build loop
    #print(Years)
    Years=[2011,2012,2013,2014,2015,2016]
    StateNm=State
    YearSt=pd.DataFrame()
    for Year in Years:
        YearSub=(C_Plt.loc[C_Plt.INVYR==Year])
        Pltsyear=(Plt_lst.loc[Plt_lst.INVYR==Year])
        CoInSt=(Pltsyear.COUNTYCD.unique())
        print(CoInSt)
    #print(CoInSt)
        OneYrOut=pd.DataFrame()
        for CDX in CoInSt:
            Ecoregion=Pltsyear.US_L4NAME[Pltsyear.COUNTYCD==CDX]
            #print(Ecoregion)
            CountySub=(YearSub.loc[YearSub.COUNTYCD==CDX])
            PltsCoSub=Pltsyear.loc[Pltsyear.COUNTYCD==CDX]
            Labeled=pd.merge(CountySub,PltsCoSub,on='PLOT',how='outer')
            Labeled=Labeled.dropna()
    # print(Labeled)
#print(Labeled)

###Pltlvl
            PltsinCo=(Labeled.PLOT.unique())
            CoOut=pd.DataFrame()
            for PLX in PltsinCo:
                OnePlt=(Labeled.loc[Labeled.PLOT==PLX])
                Lat=OnePlt.LAT.values[0]
                Lon=OnePlt.LON.values[0]
                CarbonDownDead=OnePlt.CARBON_DOWN_DEAD.values[0]
                CarbonStandingDead=OnePlt.CARBON_STANDING_DEAD.values[0]
                Carbon_Standing_Litter=OnePlt.CARBON_LITTER.values[0]
             
                outline=pd.DataFrame([[StateNm,Year,Ecoregion,Lat,Lon,CDX,PLX,CarbonDownDead,CarbonStandingDead,Carbon_Standing_Litter]],columns=['State','Year','Ecoregion','LAT','LON','COUNTYCD','PLOT','Dead C Down','Dead C Standing','Carbon_Standing_Litter'])
                CoOut=CoOut.append(outline)
                
            OneYrOut=OneYrOut.append(CoOut)
##print(OneYrOut)
        OneYrOut.to_csv('carbon'+str(Year)+State+'.csv')
        YearSt=YearSt.append(OneYrOut)
    AllST=AllST.append(YearSt)
AllST.to_csv('Deadwood/Carbon_All.csv')
    


```

After this, I interpolated in QGIS to get a map with continuous coverage.
Here we clean and shape to make the final map.

```{r,message=FALSE,warning=FALSE}
library(ggplot2) # start needed libraries
library(gstat)
library(sp)
library(raster)
library(rgdal)
w_dir<-"Z:/Robbins/Sapps/Model_Prep/Sapps_maps_2_18/"
```


```{r}

Altered<-raster(paste("C:/Users/zacha/Documents/GitHub/Project-Southern-Appalachians-2018/Parameterizing/Soils/DeadWood_TotalCarbon.tif",sep=""))
#print(thefiles)
ICTemplate<- raster(paste(w_dir,"Cleaning/Proc_InitialCommunities.img",sep=""))

IC<-as.data.frame(raster(paste(w_dir,"Cleaning/Outputs/DummyEco.tif",sep="")))
crs(Altered)<-CRS("+init=EPSG:26917")
proj<-CRS("+init=EPSG:26917")
plot(Altered)  
#get projection/extent from the sample
proj<-projection(ICTemplate)

##resample
resampled<-resample(Altered,ICTemplate,method='ngb')

#reassign proj
crs(resampled)<-proj

#plot(ICTemplate)
#write the raster

input<-as.data.frame(resampled)
input[,1][is.na(input[,1])] <-(-9999)
##bind all files together
df<-cbind(IC,input)
colnames(df)<-c("e","Input")
#Find mean value of the carbon/nitrogen file
meanvalue<-mean(input[input>-9999])

df$Input[df$Input<=(-1000) & df$e!=1]<-meanvalue


##Set all values that are NA in carbon/nitrogen and active in ecoregion to the mean value
root<-NULL
wood<-NULL
root$Input<-df$Input
wood$Inputs<-df$Input
root$Input[root$Input>=(-1000)]<-root$Input[root$Input>=(-1000)]*.3*2
wood$Input[wood$Input>=(-1000)]<-wood$Input[wood$Input>=(-1000)]*.7*2

#df$Input[df$Input<.00001 &df$Input != -9999]<-.0001
##Print rasters
ExampleRaster<-ICTemplate

output_matrix<-matrix(root$Input,nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) #fir

new_output_raster<-raster(output_matrix,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),ymx=ymax(ExampleRaster), crs=proj)

new_output_file_name<-paste("C:/Users/zacha/Documents/GitHub/Project-Southern-Appalachians-2018/Parameterizing/Soils/Deadwood_rootv_1_2.tif",sep="")
rast_IC_map<-writeRaster(new_output_raster, filename=new_output_file_name, datatype='FLT4S',overwrite=TRUE)#Th

output_matrix<-matrix(wood$Input,nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) #fir
new_output_raster<-raster(output_matrix,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),ymx=ymax(ExampleRaster), crs=proj)

new_output_file_name<-paste("C:/Users/zacha/Documents/GitHub/Project-Southern-Appalachians-2018/Parameterizing/Soils/Deadwood_woodv_1_2.tif",sep="")
rast_IC_map<-writeRaster(new_output_raster, filename=new_output_file_name, datatype='FLT4S',overwrite=TRUE)#Th
```


```{r, fig.height=10.0,fig.width=12.0,align="center"}
library(RColorBrewer)
Ramp<-brewer.pal(9,"YlOrBr")

map<-"Z:/Robbins/Sapps/Model_Prep/Sapps_maps_2_18/Cleaning/Final/Deadwood_wood.tif"

par(mfrow=c(1,1))
Im1<-raster(map)
mv<-max(matrix(Im1))
plot(Im1,zlim=c(1000,mv),main="Deadwood Biomass",col=Ramp)
map<-"Z:/Robbins/Sapps/Model_Prep/Sapps_maps_2_18/Cleaning/Final/Deadwood_root.tif"


Im1<-raster(map)
mv<-max(matrix(Im1))
plot(Im1,zlim=c(0,mv),main="Deadroot Biomass",col=Ramp)

```


#### Data clean up and Formatting.

Some additional steps that were used to prepare the maps for LANDIS-II use.

* The data needs to be resampled to the same size and in the same projection as the initial communities file 
* Create a simple ecoregion for testing 
* Find which files may not overlap with the ecoregion and assigned the missing values a mean value
* Sand and Clay files need to be between 0 and 1.0. The USGS values are percentage as 100s (0.0-1.0).
  So here they are divided by 100. Also to clean up values they are minimized at .1
* Depth that is zero can never grow trees and will trigger weird errors. Here I find each of these and turn the ecoregion to off. 
* Wilt point cannot be greater field capacity so their difference was reduced to 0.01  


```{r}
w_dir<-"Z:/Robbins/Sapps/Model_Prep/Sapps_maps_2_18/Cleaning/"
ICTemplate<- raster(paste(w_dir,"Proc_InitialCommunities.img",sep=""))
projection(ICTemplate)<-CRS("+init=EPSG:26917")
```

```{r}
##Pull in all files from the Input drive
thefiles<-list.files(paste(w_dir,"Inputs/",sep=""),pattern = "\\.tif$")

ICTemplate<- raster(paste(w_dir,"Proc_InitialCommunities.img",sep=""))
```

##### Resample to the same resolution.

```{r}
for(file in thefiles){
  #Readd in the raster
  Altered<-raster(paste(w_dir,"Inputs/",file,sep=""))
  
  crs(Altered)<-CRS("+init=EPSG:26917")
  
  #get projection/extent from the sample
  proj<-projection(ICTemplate)
  
  extent21<-extent(ICTemplate)
  #match extents
  #extent(Altered)<-extent21
  #plot(Altered)
  ##resample
  resampled<-resample(Altered,ICTemplate,method='ngb')

  #reassign proj
  crs(resampled)<-proj

  #plot(ICTemplate)
  #write the raster
  new_output_file_name<-(paste(w_dir,"Outputs/Proc",file,sep=""))
  writeRaster(resampled, filename=new_output_file_name, datatype='FLT8S',overwrite=TRUE)  
}
```

```{r}
file<-"Sand_cut.tif"
par(mfrow=c(1,2))
map<-paste(w_dir,"Inputs/",file,sep="")
Im1<-raster(map)
mv<-max(matrix(Im1))

#plot(Im1,zlim=c(0,mv),main="Soil Before",col=Ramp)

map<-paste(w_dir,"Outputs/Proc",file,sep="")
Im1<-raster(map)
mv<-max(matrix(Im1))
plot(Im1,zlim=c(0,mv),main="Soil After ",col=Ramp)
```



```{r}
proj<-CRS("+init=EPSG:26917")
ecoregions<-raster(paste(w_dir,"Proc_InitialCommunities.Img",sep=""))

#plot(ecoregions)
DummyEco<-ecoregions
##turn all except for the six to 1
DummyEco[DummyEco>=1,]<-2
DummyEco[is.na(DummyEco[,1]),]<-1
DummyEco[DummyEco<1,]<-1

#plot(DummyEco)
##Write Raster
new_output_file_name<-(paste(w_dir,"Outputs/DummyEco.tif",sep=""))
writeRaster(DummyEco, filename=new_output_file_name, datatype='FLT8S',overwrite=TRUE)  

ExampleRaster<-DummyEco
###Get just the Carbon/nitrogen files
```


```{r}
###This lists files in the folder 
IC<-as.data.frame(DummyEco)
#thefiles<-list.files(paste(w_dir,"Outputs/",sep=""),pattern = "\\.tif$")
thefiles<-c("ProcFeildDone.tif","ProcWiltDone.tif")
```



```{r}
### 
for(file in thefiles){
     #print(file)
     raster<-(raster(paste(w_dir,"Outputs/",file,sep="")))
     input<-as.data.frame(raster)
     input[,1][is.na(input[,1])] <-(-9999)
     ##bind all files together
     df<-cbind(IC,input)
     colnames(df)<-c("e","Input")
     #Find mean value of the carbon/nitrogen file
     meanvalue<-mean(input[input>-9999])
     #print("mean")
     #print(meanvalue)
     #print("min")
     #print(min(input[input>-9999]))
     #print("max")
     #print(max(input[input>-9999]))

     df$e
     #print(length(df$Input[df$Input<=(-1000) & df$e!=1]))
     ##Set all values that are NA in carbon/nitrogen and active in ecoregion to the mean value
     df$Input[df$Input<=(-1000) & df$e!=1]<-meanvalue

     #df$Input[df$Input<.00001 &df$Input != -9999]<-.0001
     ##Print rasters
     output_matrix<-matrix(df$Input,nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) #fir
     new_output_raster<-raster(output_matrix,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),ymx=ymax(ExampleRaster), crs=proj)

     new_output_file_name<-paste(w_dir,"Mean/MeanedandCleaned",file,sep="")
     rast_IC_map<-writeRaster(new_output_raster, filename=new_output_file_name, datatype='FLT4S',overwrite=TRUE)#Th
     }
```

```{r}

  file<-"MeanedandCleanedDummyEco.tif"
    
  input<-(raster(paste(w_dir,"Mean/",file,sep="")))
 
  new_output_file_name<-paste(w_dir,"Final/MR_",file,sep="")
  rast_IC_map<-writeRaster(input, filename=new_output_file_name, datatype='INT4S',overwrite=TRUE)#T

```

```{r}

#paste(w_dir,"IC_Repro.tif",sep="")
ExampleRaster<-raster(paste(w_dir,"Proc_InitialCommunities.img",sep=""))
input<-raster(paste(w_dir,"Proc_InitialCommunities.img",sep=""))
input<-as.data.frame(input)
input[,1][is.na(input[,1])] <-0
input[,1][(input[,1])<0] <-0
input[,1][(input[,1])>3000]<-0
#print(max(input[,1]))
#print(min(input[,1]))
output_matrix<-matrix(input[,1],nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) #fir
new_output_raster<-raster(output_matrix,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),ymx=ymax(ExampleRaster), crs=proj)
#plot(new_output_raster)
filename=paste(w_dir,"Final/MR_InitialCommunity_2_18.tif",sep="")
#print(filename)
writeRaster(new_output_raster, filename=filename, datatype='INT4S',overwrite=TRUE)
```


```{r}
input<-as.data.frame(raster(paste(w_dir,"Mean/MeanedandCleanedDummyEco.tif",sep="")))
Stormflow<-input[,1]
Stormflow[Stormflow==2]<-0.3
Stormflow[Stormflow==1]<-(-9999)
#length(Stormflow[Stormflow==0.3])
ExampleRaster<-raster(paste(w_dir,"Mean/MeanedandCleanedDummyEco.tif",sep=""))
output_matrix<-matrix(Stormflow,nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) #fir
new_output_raster<-raster(output_matrix,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),ymx=ymax(ExampleRaster), crs=proj)

new_output_file_name<-paste(w_dir,"Final/MR_Stormflow.tif",sep="")
rast_IC_map<-writeRaster(new_output_raster, filename=new_output_file_name, datatype='FLT4S',overwrite=TRUE)#
```


```{r}
Feild<-raster(paste(w_dir,"Mean/MeanedandCleanedProcFeildDone.tif",sep=""))
WP<-raster(paste(w_dir,"Mean/MeanedandCleanedProcWiltDone.tif",sep=""))
#Depth<-as.data.frame(raster(paste(w_dir,"Mean/MeanedandCleanedProcDepth_top.tif",sep="")))
#Ecoregion<-as.data.frame(raster(paste("C:/Users/zacha/Documents/GitHub/Project-Southern-Appalachians-2018/Models/LANDIS_Sapps_Active_v1_2/MR_FourEcoregions.tif")))
#

#plot(Feild)
Feild[Feild>(-1999),]<-Feild[Feild>(-1999),]/100
Feild[Feild>(-1999) & Feild<.05,]<-.05




WP[WP>(-1999),]<-WP[WP>(-1999),]/100
WP[WP>(-1999) & WP<.05,]<-.05

#plot(WP,zlim=c(0,.25),main="Wilting point")
#plot(Feild,zlim=c(0,.75),main="Feild Capacity")
unique(Feild[Feild>(-1999) & Feild< (WP+.05)])
Feild[Feild>(-1999) & Feild< (WP+.05)]<-WP[Feild>(-1999) & Feild<(WP+.05)]+.05
plot(Feild-WP,zlim=c(-1,1))
Dataframe<-as.data.frame(Feild-WP)
#unique(Feild$MeanedandCleanedProcFeildDone[WP[,1]>(-1999)& Feild[,1]>(-1999)& WP$MeanedandCleanedProcWiltDone+.05>Feild$MeanedandCleanedProcFeildDone])

#Feild$MeanedandCleanedProcFeildDone[WP[,1]>(-1999)& Feild[,1]>(-1999)]
                                                                                                                                                                                    #WP$MeanedandCleanedProcWiltDone+.05>Feild$MeanedandCleanedProcFeildDone]+.05

#min(Feild$MeanedandCleanedProcFeildDone[Feild$MeanedandCleanedProcFeildDone>(-1999)])




# (WP[WP[,1]>(-1999),])
# unique(Feild)
# #min(Feild[Feild[,1]>(-1999),])
# min(Feild[Feild[,1]>(-1999),]-WP[WP[,1]>(-1999),])
# min(WP[WP[,1]>(-1999),])
# unique(Ecoregion$MR_FourEcoregions[Feild$MeanedandCleanedProcFeildDone<0.05])
# 
# unique(Ecoregion$MR_FourEcoregions[WP$MeanedandCleanedProcWiltDone<0.05])





WP_Print<-as.vector(WP[,1])
FC_Print<-as.vector(Feild[,1])
ExampleRaster<-raster(paste(w_dir,"Mean/MeanedandCleanedProcFeildDone.tif",sep=""))

#output_matrix<-matrix(WP_Print,nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) #fir
#new_wilt_raster<-raster(output_matrix,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),ymx=ymax(ExampleRaster), crs=proj)
#plot(new_output_raster,zlim=c(0,.2))
new_output_file_name<-paste(w_dir,"Mean/MeanedandCleanedProcWiltDone2.tif",sep="")
rast_IC_map<-writeRaster(WP,filename=new_output_file_name, datatype='FLT8S',overwrite=TRUE)#Th

#output_matrix<-matrix(FC_Print,nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) #fir
#new_output_raster<-raster::raster(output_matrix,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),ymx=ymax(ExampleRaster), crs=proj)
#plot(new_output_raster,zlim=c(0,.5)

new_output_file_name<-paste(w_dir,"Mean/MeanedandCleanedProcFeildDone2.tif",sep="")
rast_IC_map<-writeRaster(Feild,filename=new_output_file_name, datatype='FLT8S',overwrite=TRUE)#Th
```


```{r}
library(RColorBrewer)

```



```{r}


#Sand and Clay files need to be between 0 and 1.0. The USGS values are percetages as 100s (0.0-1.0).
#So here they are divided by 100. Also to clean up values they are minimized at .1

###Sand and Clay
Sand<-as.data.frame(raster(paste(w_dir,"Mean/MeanedandCleanedProcSand_cut.tif",sep="")))

Clay<-as.data.frame(raster(paste(w_dir,"Mean/MeanedandCleanedProcClay_Done.tif",sep="")))

scaler<-.01
Sand[!is.na(Sand[,1]),]<-Sand[!is.na(Sand[,1]),]*scaler
Sand[,1][Sand[,1]<=0.1]<-0.1

Clay[!is.na(Clay[,1]),]<-Clay[!is.na(Clay[,1]),]*scaler
Clay[,1][Clay[,1]<=0.1]<-0.1


Clay_Print<-as.vector(Clay[,1])

Sand_Print<-as.vector(Sand[,1])

ExampleRaster<-raster(paste(w_dir,"Mean/MeanedandCleanedDummyEco.tif",sep=""))
proj<-projection(ExampleRaster)

output_matrix<-matrix(Clay_Print,nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) #fir
new_output_raster<-raster(output_matrix,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),ymx=ymax(ExampleRaster), crs=proj)
new_output_file_name<-paste(w_dir,"Mean/MeanedandCleanedProcClay_Done.tif",sep="")
rast_IC_map<-writeRaster(new_output_raster, filename=new_output_file_name, datatype='FLT4S',overwrite=TRUE)#Th

output_matrix<-matrix(Sand_Print,nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) #fir
new_output_raster<-raster(output_matrix,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),ymx=ymax(ExampleRaster), crs=proj)
new_output_file_name<-paste(w_dir,"Mean/MeanedandCleanedProcSand_cut.tif",sep="")
rast_IC_map<-writeRaster(new_output_raster, filename=new_output_file_name, datatype='FLT4S',overwrite=TRUE)#Th
```

```{r}
###Depth

#Depth that are zero can never grow trees and will trigger weird errors. Here I find each of these are turn their ecoregion to off. 

Depth<-as.data.frame(raster(paste(w_dir,"Mean/MeanedandCleanedProcDepth_top.tif",sep="")))
ecoregion<-as.data.frame(raster(paste(w_dir,"Final/MR_MeanedandCleanedDummyEco.tif",sep=""))) 
df<-cbind(Depth,ecoregion)

colnames(df)<-c("Input","e")
df$e[df$Input<=(0.0) & df$e!=1]<-1.0
output_matrix<-matrix(df$e,nrow=nrow(ExampleRaster),ncol=ncol(ExampleRaster),byrow=T) 
new_output_raster<-raster(output_matrix,xmn=xmin(ExampleRaster),ymn=ymin(ExampleRaster),xmx=xmax(ExampleRaster),ymx=ymax(ExampleRaster), crs=proj)

new_output_file_name<-paste(w_dir,"Final/MR_FinalDummyEco.tif",sep="")
rast_IC_map<-writeRaster(new_output_raster, filename=new_output_file_name, datatype='INT4S',overwrite=TRUE)#Th

```


```{r}
thefiles<-list.files(paste(w_dir,"Mean/",sep=""),pattern = "\\.tif$")
thefiles<-c("MeanedandCleanedProcFeildDone2.tif","MeanedandCleanedProcWiltDone2.tif")
```


```{r}

for(i in thefiles){
input<-(raster(paste(w_dir,"/Mean/",i,sep="")))

projection(input)<-CRS("+init=EPSG:26917")

str1<-i

##useful

cleanname<-gsub('MeanedandCleanedProc','',str1) 

new_output_file_name<-paste(w_dir,"Final/MR",cleanname,sep="")
rast_IC_map<-writeRaster(input, filename=new_output_file_name, datatype='FLT4S',overwrite=TRUE)#Th
}

```

