---
title: "Scrapple Param 9/21"
author: "Zjrobbins"
date: "09/2021"
output: github_document
---
This is a program to parameter and test a SCRPPLE Fire model for the Southern Appalachains_

Based on and borrowing the code structures of the Scrapple proof of concept designed by:
Alec Kretchun, 2017



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Ignitions
 
The purpose of this section is to paramaterized  the function for ignitions based on fire weather index. To do this we look the historical record of ignitions and 
pair it with fire weather index. We then will conduct a zero inflated poission model fit to this data. Lastly we examine how well this model fits the record. 



```{r cars}
library(raster)
library(foreign)
library(plyr)
#library(likelihood)
library(dplyr)
library(pscl)
library(boot)
library(rgdal)
library(reticulate)
#plot(wind_map)
```

```{r pressure, echo=FALSE}
w_dir <- "Z:/Robbins/Sapps/Chapter3/Code/Scrpple_111721/Inputs/"
out_dir <-  "Z:/Robbins/Sapps/Chapter3/Code/Scrpple_111721/Outputs/"
```

First start with the ignitions data. 

Short, Karen C. 2017. Spatial wildfire occurrence data for the United States, 1992-2015 [FPA_FOD_20170508]. 4th Edition. Fort Collins, CO: Forest Service Research Data Archive. https://doi.org/10.2737/RDS-2013-0009.4
https://www.fs.usda.gov/rds/archive/Product/RDS-2013-0009.4/

Abstract:This data publication contains a spatial database of wildfires that occurred in the United States from 1992 to 2015. It is the third update of a publication originally generated to support the national Fire Program Analysis (FPA) system. The wildfire records were acquired from the reporting systems of federal, state, and local fire organizations. The following core data elements were required for records to be included in this data publication: discovery date, final fire size, and a point location at least as precise as Public Land Survey System (PLSS) section (1-square mile grid). The data were transformed to conform, when possible, to the data standards of the National Wildfire Coordinating Group (NWCG). Basic error-checking was performed and redundant records were identified and removed, to the degree possible. The resulting product, referred to as the Fire Program Analysis fire-occurrence database (FPA FOD), includes 1.88 million geo-referenced wildfire records, representing a total of 140 million acres burned during the 24-year period.

[meta](https://www.fs.usda.gov/rds/archive/products/RDS-2013-0009.4/_metadata_RDS-2013-0009.4.html)



These data is spatially located then divided into lightning ignitions and accidental human ignited values. 

127<- we are filtering out fires smaller than 250x250 which would be ~15.4 acres. 
```{r}
l_fire_dat <- read.csv(paste(w_dir,"Natural_KS21.csv", sep=""))
head(l_fire_dat)
l_fire_dat<-l_fire_dat%>%
  subset(FIRE_SIZE>15.44)
##This moves us from 676 to 155

l_fire_days <- as.data.frame(cbind(l_fire_dat$FIRE_YEAR, l_fire_dat$DISCOVERY_DOY)) #Extracting year and julian day
colnames(l_fire_days) <- c("YEAR", "DISCOVERY_DOY")
l_fire_days_sort <- l_fire_days[order(l_fire_days[,1]),] #sorting by year

```


Here we can see the number of lightning ignited firest per year


```{r}
library(RColorBrewer)

red<-RColorBrewer::brewer.pal(9,'YlOrRd')
#plot no of fires/yr
l_fire_days_sort_count<- cbind(l_fire_days_sort, rep(1, nrow(l_fire_days_sort)))
l_fires_count <- cbind.data.frame(unique(l_fire_days_sort_count$YEAR) , 
                                 tapply(l_fire_days_sort_count$`rep(1, nrow(l_fire_days_sort))`,l_fire_days_sort_count$YEAR, sum))
colnames(l_fires_count) <- c("YEAR", "COUNT")

barplot(l_fires_count$COUNT, main ="No of ign/yr Lightning Observed",col=red,names.arg=l_fires_count$YEAR)

```

```{r}
h_fire_dat <- read.csv(paste(w_dir, "/Human_KS21.csv", sep=""))
h_fire_dat<-h_fire_dat%>%
  subset(FIRE_SIZE>15.44)
##Goes from 24789 to 1531
#head(h.fire.dat)
h_fire_days <- as.data.frame(cbind(h_fire_dat$FIRE_YEAR, h_fire_dat$DISCOVERY_DOY)) #Extracting year and julian day

colnames(h_fire_days) <- c("YEAR", "DISCOVERY_DOY")
h_fire_days_sort <- h_fire_days[order(h_fire_days[,1]),] #sorting by year
#plot no of fires/yr
h_fire_days_sort_count<- cbind(h_fire_days_sort, rep(1, nrow(h_fire_days_sort)))
h_fires_count <- cbind.data.frame(unique(h_fire_days_sort_count$YEAR) , 
                                  tapply(h_fire_days_sort_count$`rep(1, nrow(h_fire_days_sort))`,h_fire_days_sort_count$YEAR, sum))
colnames(h_fires_count) <- c("YEAR", "COUNT")
barplot(h_fires_count$COUNT, main ="No of ign/yr Human Accidental Observed",col=red,names.arg=h_fires_count$YEAR)

```


Match them up with FWI data generated from the historic record of weather fed through LANDIS-II Fire weather to get the models calculation of FWI.

```{r}

ign_types <- c("Lightning", "HumanAccidental")

fire_days_list <- list(l_fire_days_sort, h_fire_days_sort) ##organizing all ignition types into a list


##Import daily historic FWI data
FWI_dat <- read.csv(paste0(w_dir,"Climate-future-input-log_916.csv"))

FWI_dat<-with(FWI_dat,aggregate(FWI,by=list(Year=Year,Timestep=Timestep),FUN=mean))
FWI_dat <- FWI_dat[,c(1,2,3)]
colnames(FWI_dat)[3]<-"FWI"
FWI_day<-with(FWI_dat,aggregate(FWI,by=list(Timestep),FUN=max))


FWI_dat$ID <- paste(FWI_dat$Year, "_", FWI_dat$Timestep, sep="") #creating date identifier out of date and julian day



igns_list <- list()

for (i in 1:length(ign_types[1:2])){#THIS DOESN'T INCLUDE RX BURNS BUT THATS CAUSE WE ARE PROVIDING THOSE TO SCRAPPLE DIRECT
  ign_type_select <- fire_days_list[[i]] ##selecting each ignition type individually
  fire_days_count <- ddply(ign_type_select, .(ign_type_select$YEAR, ign_type_select$DISCOVERY_DOY), nrow) #finds duplicate rows in fire data
  colnames(fire_days_count) <- c("YEAR", "JD", "No_FIRES") #Renaming columns for consistency
  fire_days_count$ID <- paste(fire_days_count$YEAR, "_", fire_days_count$JD, sep="") #creating date identifier out of date and julian day

  ##Merging dataframes by year and julian day
  fire_days_short <- subset(fire_days_count, fire_days_count$YEAR<2017) ##restricting fire records to climate file years
  FWI_short <- subset(FWI_dat, FWI_dat$Year > 1991) #restricting climate data to fire history records
  merge_col <- FWI_short$ID
  FWI_fire_merge <- join(FWI_short, fire_days_short, type="left") ##Merging based on unique date id
  FWI_fire_number <- FWI_fire_merge[,c(1,3,7)] #pulling out FWI and number of fires
  FWI_fire_number[is.na(FWI_fire_number)] <- 0 #converting NAs to 0, meaning 0 fires
  plot(FWI_fire_number[,2], FWI_fire_number[,3], main =ign_types[i], xlab = "dailyFWI", ylab = "noFires") #plotting FWI against no of fires just to look at pattern
  igns_list[[i]] <- FWI_fire_number 
}
```

```{r}
plot(FWI_day$Group.1,FWI_day$x)
```


```{r}
#Lighting
print("Ignition")
summary(igns_list[[1]])
#Humnan
print("Human")
summary(igns_list[[2]])

```

Fit the lightning model

```{r}

Lightning<-as.data.frame(igns_list[[1]])

Lightning<-Lightning[-2758,]
#Lightning$No_FIRES
###Lightning
zeroinf_mod <- zeroinfl(No_FIRES~FWI,data=Lightning, dist="poisson")
summary(zeroinf_mod)
#Tst<-predict(zeroinf_mod,type="zero")
```

Should be noted there is a lot of variance in the random draw

```{r}
zero<-predict(zeroinf_mod,data.frame(FWI=Lightning$FWI), type = "zero")
#print(zero)
#n<-data.frame(FWI=Lightning$FWI)
lambda <- predict(zeroinf_mod,data.frame(FWI=Lightning$FWI), type = "count")
Simulation<-ifelse(rbinom(9124,size = 1, prob = zero) > 0, 0, rpois(9124, lambda = lambda))

ReturnDf<-cbind(Simulation,Lightning)
Sample<-aggregate(ReturnDf$Simulation,by=list(year=ReturnDf$Year),FUN=sum)
barplot(Sample$x, main ="No of ign/yr Lightning Simulated",col='black', ylim=c(0,25),names.arg=Sample$year)



Simulation_Stack_ZIP<-function(zeros,lambdas,data,nsimulations){
  Samples<-NULL
  for(i in 1:nsimulations){
  Simulation<-ifelse(rbinom(9124,size = 1, prob = zeros) > 0, 0, rpois(9125, lambda = lambdas))
  ReturnDf<-cbind(Simulation,data)
  Sample<-aggregate(ReturnDf$Simulation,by=list(year=ReturnDf[,2]),FUN=sum)
  if(i==1){Samples<-Sample}else{Samples<-cbind(Samples,Sample[,2])}
  }
  return(cbind(Samples[1],rowMeans(Samples[-1])))
}


```

```{r}
#Tst<-predict(zeroinf_mod,type="zero")
zero<-predict(zeroinf_mod,data.frame(FWI=seq(0,40,0.1)), type = "zero",xlab="")
#print(zero)
#n<-data.frame(FWI=Lightning$FWI)
lambda <- predict(zeroinf_mod,data.frame(FWI=seq(0,40,0.1)), type = "count")



par(mfrow=c(1,2))
plot(seq(0,40,0.1),zero,xlab="FWI",ylab="(p) of zero ignitions",main="Lightning Ignition and FWI",type="l",lwd="5.0",cex.axis=1.5,cex.lab=1.5,cex.main=1.5)
plot(seq(0,40,0.1),lambda,ylab="Probable count of ignitions",xlab="FWI",type="l",lwd="5.0",cex.axis=1.5,cex.lab=1.5)

```


It is a noisy random draw so lets run 1000 and take the mean.

```{r}

Sims_Zip<-Simulation_Stack_ZIP(zero,lambda,Lightning,10)
barplot(Sims_Zip$`rowMeans(Samples[-1])`, main ="No of ign/yr Lightning Simulated x1000",col='black', ylim=c(0,20),names.arg=Sample$year)
```

We see here that in a set of runs the random draw accounts for a greater influence than the predictor. 

And here is the historic,
```{r}
barplot(l_fires_count$COUNT, main ="No of ign/yr Lightning Observed",col=red,ylim=c(0,50),names.arg=l_fires_count$YEAR)
```

```{r}
#https://fukamilab.github.io/BIO202/04-C-zero-data.html
#Dispersion statistic
E2 <- resid(zeroinf_mod, type = "pearson")
N  <- nrow(Lightning)
p  <- length(coef(zeroinf_mod))  
sum(E2^2) / (N - p)
```

```{r}
Model<-glm(No_FIRES~FWI,data=Lightning, family="poisson")
summary(Model)
```
The Poisson Looks good too.



```{r}

Pois<-glm(No_FIRES~FWI,data=Lightning, family="poisson")

print("Scores for candidate Accidental Ignition Models")
print(data.frame(Model=c("ZIP","Pois"),Score=c(AIC(zeroinf_mod),AIC(Pois))))

```
```{r}
TotalIG<-sum(l_fires_count$COUNT)
Total_Sim_IG<-sum(Sample$x)


Mean_IG<-mean(l_fires_count$COUNT)
Mean_IG_Sim<-mean(Sample$x)
Var_IG<-var(l_fires_count$COUNT)
Var_IG_Sim<-var(Sample$x)
boxplot(Sample$x,l_fires_count$COUNT,names.arg=c("Simulated","Observed"))
```


### Fit the human accidental model

```{r}
Accidental<-as.data.frame(igns_list[[2]])

###Lightning
Acc_zeroinf_mod <- zeroinfl(No_FIRES~FWI,data=Accidental, dist="poisson")
summary(Acc_zeroinf_mod)
```


Accidental

Likelihood of an ignition day:

Should be noted this bar plot is a random simulation

```{r}


#Tst<-predict(zeroinf_mod,type="zero")
zero<-predict(Acc_zeroinf_mod,data.frame(FWI=seq(0,40,0.1)), type = "zero")
#print(zero)
#n<-data.frame(FWI=Lightning$FWI)
lambda <- predict(Acc_zeroinf_mod,data.frame(FWI=seq(0,40,0.1)), type = "count")

par(mfrow=c(1,2))
plot(seq(0,40,0.1),zero,ylim=c(0,1),xlab="FWI",ylab="(p) of zero ignitions",main="Accidental Ignition and FWI",type="l",lwd="5.0",cex.axis=1.5,cex.lab=1.5,cex.main=1.5)
plot(seq(0,40,0.1),lambda,ylab="Probable count of ignitions",xlab="FWI",type="l",lwd="5.0",cex.axis=1.5,cex.lab=1.5)




Simulation<-ifelse(rbinom(9124,size = 1, prob = zero) > 0, 0, rpois(9124, lambda = lambda))

ReturnDf<-cbind(Simulation,Lightning)
Sample<-aggregate(ReturnDf$Simulation,by=list(year=ReturnDf$Year),FUN=sum)


barplot(Sample$x, main ="No of ign/yr Accidental_Simulated",col='black', ylim=c(0,150),names.arg=Sample$year)
```

```{r}
barplot(h_fires_count$COUNT, main ="No of ign/yr Human Accidental Observed",col=red,ylim=c(0,140))

```


```{r}
E2 <- resid(Acc_zeroinf_mod, type = "pearson")
N  <- nrow(Accidental)
p  <- length(coef(Acc_zeroinf_mod))  
sum(E2^2) / (N - p)
```

Summary Statistics

```{r}
TotalIG<-sum(h_fires_count$COUNT)
Total_Sim_IG<-sum(Sample$x)


Mean_IG<-mean(h_fires_count$COUNT)
Mean_IG_Sim<-mean(Sample$x)
Var_IG<-var(h_fires_count$COUNT)
Var_IG_Sim<-var(Sample$x)
boxplot(Sample$x,h_fires_count$COUNT,names.arg=c("Simulated","Observed"))
```

Left is simulated, Right is Observed

```{r}

print(data.frame(Names=c("Simulation","Observed"),Total=c(Total_Sim_IG,TotalIG),Mean=c(Mean_IG_Sim,Mean_IG),
                 Var=c(Var_IG_Sim,Var_IG)))

```


#### Fire Spread Parameters.

```{r}
##Alec Kretchun, 2017
library(geosphere)
library(maptools)
library(raster)
library(dplyr)
library(rgdal)
library(rgeos)
library(geosphere)
library(nplr)
library(pscl)
library(ROCR)
library(likelihood)
library(hexbin)
library(RColorBrewer)
##Read things
```


Ecoregions: This is the ecoregions from LANDIS_II to link weather to location. 

```{r}
w_dir <- "Z:/Robbins/Sapps/Chapter3/Code/Scrpple_111721/Inputs/"

fwi_dat <- read.csv(paste0(w_dir,"Climate-future-input-log_916.csv"),stringsAsFactors = FALSE)
wind_map<- raster::raster(paste(w_dir,"11_Ecoregions.tif",sep=""))

plot(wind_map)
unique(wind_map$X11_Ecoregions)
```



Here we are looking to fit a zero inflated poisson equation looking at how fire size (or probability of spread) is related to the FWI, wind, and fuels.
We wil do a similar process as above, of matching each fire event to a database on weather, wind and the fuels. 

Wind data 
This is Grit metdata fro the University of Idaho http://www.climatologylab.org/gridmet.html
From their website.

WHAT IS GRIDMET?
gridMET is a dataset of daily high-spatial resolution (~4-km, 1/24th degree) surface meteorological data covering the contiguous US from 1979-yesterday. We have also extended these data to cover southern British Columbia in our real time products. 
These data can provide important inputs for ecological, agricultural, and hydrological models. These data are updated daily.  gridMET is the preferred naming convention for these data; however, the data are also known as cited as METDATA.

http://www.climatologylab.org/gridmet.html


[meta](https://cida.usgs.gov/thredds/dodsC/UofIMETDATA.html)


```{r}

wsv_dat <- read.csv(paste(w_dir,"Wind_Gridmet.csv",sep=""),stringsAsFactors = FALSE)
#wsv_dat<-wsv_dat[,c(-1)]
```

Fuels:

Cropped to the landscape. 

```{r}
###Fixing landis GDAL problem

ExampleRaster<-raster(paste(w_dir,"11_Ecoregions.tif",sep=""))
projy<-crs(ExampleRaster)


#raster of fuel types from LANDFIRE

#fccs_raster <- raster(paste(w_dir,"Crop_Fuel.tif",sep="")) #raster of 2001 fuel beds
###Secondfule<-
fccs_raster<-raster(paste(w_dir,"LANDIS_fuels_spinup.IMG",sep=""))
plot(fccs_raster)
crs(fccs_raster)<-projy
extent(fccs_raster)<-extent(ExampleRaster)
plot(fccs_raster)
fccs_raster

##
```

```{r,eval=FALSE}
#Fuel bed LUT
#fccs_defs <- read.csv(paste(w_dir, "us_110flm_12202013.csv",sep="")) #definitions of fuelbed types

fuel_map <- projectRaster(fccs_raster, to = wind_map, method='bilinear') #I chose nearest neighbor for the fuels maps cause its a categorical variable
#Resample to fill in zeros
### Manual cardinal stretching



r=fccs_raster
r[r==0] <- NA

fill.na <- function(x, i=5) {
  if( is.na(x)[i] ) {
    return( round(mean(x, na.rm=TRUE),0) )
  } else {
    return( round(x[i],0) )
  }
}  

r2 <- focal(r, w = matrix(1,3,3), fun = fill.na, 
            pad = TRUE, na.rm = FALSE )
plot(r2)
r3<-focal(r2, w = matrix(1,3,3), fun = fill.na, 
            pad = TRUE, na.rm = FALSE )

plot(r3)

r4<-focal(r3, w = matrix(1,3,3), fun = fill.na, 
            pad = TRUE, na.rm = FALSE )

plot(r4)
fuel_map<-r4

plot(fuel_map)

writeRaster(fuel_map,paste0(w_dir,"InterpolatedFuels.tif"))
```

Azimuth and Slope Maps:

True wind spread is relative to the the slope and aspect. To capture that a zimuth and slope need to be usped as well 

```{r}
fuel_map<-raster(paste0(w_dir,"InterpolatedFuels.tif"))
slope_azi_map <- raster(paste(w_dir,"SAPPS_aspect_inverted_atModelRes.tif",sep=""))

uphill_azi_map <- projectRaster(slope_azi_map, to = fuel_map, method='bilinear')
wdir_dat <- read.csv(paste(w_dir,"Winddir.csv",sep=""),stringsAsFactors = FALSE)
colnames(wdir_dat) <- c("date", "eco1", 'eco2', 'eco3', 'eco4','eco5','eco6','eco8','eco9','eco10','eco11')

SNslope_map <-  raster(paste(w_dir,"SAPPS_Slope_ChrisArcmapprocess_modelres.tif",sep=""))
#slope_map <- projectRaster(SNslope_map, to = fuel_map, method='bilinear')

```

```{r}
wind_map <- projectRaster(wind_map, to = fuel_map, method='ngb')
##Stacking all rasters as a test
climate_stack <- stack(wind_map, fuel_map, uphill_azi_map, slope_azi_map)
plot(climate_stack)
```

Now we will clean up the variable stack

```{r}
################## PROCESSING EXTERNAL DATA SETS TO USE WITH EPA REGION AND CONSUME LOOK UP TABLES #####################
### THIS IS WHERE I TAKE CATEGORICAL VARIABLES FROM INPUT RASTERS AND SET UP LOOKUPS FOR REAL VALUES OF WIND SPEED, FUEL BIOMASS ETC ######

##Process FWI values produced by LANDIS climate library to prep for attaching to larger spread matrix
##Need to attach ecoregion info
fwi_dat_slim <- fwi_dat[,c(1,2,3,27)]
colnames(fwi_dat)
fwi_date_info <- with(fwi_dat_slim, paste(Year, Timestep))
fwi_dates <- strptime(fwi_date_info, "%Y %j") #COnverting from julian day to y-m-d
#unique(fwi_date_dat$EcoregionName)
fwi_date_dat <- cbind(as.POSIXct(fwi_dates), fwi_dat_slim[,3:4]) #attaching 
colnames(fwi_date_dat) <- c("Date", "Ecoregion", "FWI")
fwi_date_dat$Ecoregion<-gsub("eco","",fwi_date_dat$Ecoregion)
fwi_date_dat$Ecoregion<-as.numeric(as.character(fwi_date_dat$Ecoregion))
##Attach LANDFIRE fuel loading info based on fuel type number
##I selected columns I thought would define fine fuels, but these can change if we need. Units are tons/acre
#fccs_loading <- fccs_defs[,c("Value", "Litter","Duff")] ##removed "shrubs_primary_loading", "shrubs_secondary_loading",
#fccs_loading_total <- rowSums(fccs_loading[,c(2,3)])
#fccs_loading_total <- fccs_loading_total #* 224.17 #convert from tons/acre to g/m-2


#fccs_finefuels <- cbind(fccs_loading[,1], fccs_loading_total)
#colnames(fccs_finefuels) <- c("fueltype", "finefuels_loading")

##Linking up successful spread days with actual wind speed 

colnames(wsv_dat) <- c("date", "eco1", 'eco2', 'eco3', 'eco4','eco5','eco6','eco8','eco9','eco10','eco11')

```


Geomac Files Boundary Files:

GeoMAC is an internet based mapping application which allows the public to access online maps of current fire locations and perimeters using standard web browsers.

Please select from the menu on the top to get help on the application and information on the individual map layers. The data in the viewer is displayed in the Web Mercator (Auxiliary Sphere) projection (WGS84 datum).

If additional assistance is needed please email geomac@usgs.gov.

https://www.geomac.gov/viewer/viewer.shtml

https://rmgsc.cr.usgs.gov/outgoing/GeoMAC/historic_fire_data/

These shape files provide daily boundaries for fires. These have been isolated to the study area. 


```{r}
##Empty objects and column names and stuff used in loops
newfire<-readOGR(paste(w_dir,"fire_geomac_loc.shp",sep=""))
## Putting into sets based on differnces in meta-data (columns not matched)
newfire1<-newfire[newfire$incidentna!=0,]
newfire2<-newfire[newfire$incidentna==0,]
newfire_df<-data.frame(newfire)
perimeter_map<-newfire
### Here we are cleaning the data
perimeter_map$TrueDate<-as.Date(perimeter_map$perimeterd)
perimeter_map$TrueDate[is.na(perimeter_map$TrueDate)]<-as.Date(perimeter_map$date_[is.na(perimeter_map$TrueDate)])
### Subseting to our time period of climate coverage (< 2017)
perimeter_map<-perimeter_map[perimeter_map$TrueDate<"2017-01-01",]
perimeter_map$incidentna[perimeter_map$incidentna=='0']<-perimeter_map$fire_name[perimeter_map$incidentna=='0']
perimeter_map$incidentna[perimeter_map$incidentna==0]<-perimeter_map$fire_name[perimeter_map$incidentna==0]
DFP<-as.data.frame(perimeter_map)
fire_names<-as.character(perimeter_map$incidentna)
## Here we plot the shapefiles to see that they overlap
###Climate regions
plot(ExampleRaster)
plot(newfire,add=TRUE)
plot(fuel_map)
plot(newfire,add=TRUE)


```

### Visually filtering fires. 
Looking for fires, that are not just the final burn shape. 


```{r,fig.width=15.0,fig.height=40}
#Setting up names of fire perimeter shapefiles
years <- 1992:2018

```
```{r,fig.width=15.0,fig.height=15}
 #  library(raster)
 #  climate_day_mat <- NULL
 # # One_fire <- newfire[newfire$incidentna,] #This pulls out all fire names
 #  
 #  ##Select for fires that lasted more than 1 day
 #  fire_names_manydays <- unique(fire_names[duplicated(fire_names)])
 #  fire_names_manydays <- fire_names_manydays[!is.na(fire_names_manydays)] ##Remo
 #  for (i in 1:length(fire_names_manydays)){
 #    
 #    #fire_select <- perimeter_map[perimeter_map$fire_name == fire_names_manydays[i],] #selecting an individual fire_ doesn't work 7/7 #
 #    #print(fire_names_manydays[i])
 #    fire_select <- subset(perimeter_map, perimeter_map$incidentna ==fire_names_manydays[i])#selecting an individual fire
 #    fire_days <- as.character(sort(unique(fire_select$perimeterd)))
 #  
 #   #print(max)
 #   #print(max[4]) 
 #   #if(is.na(fire_days)){fire_days<-as.character(sort(unique(fire_select$date_)))}
 #    #sorting fire days into chronological order
 #   # print(fire_days)
 #    ##Add a short escape in case fire days <= 1
 #    if(length(fire_days) < 2) next
 #    par(mfrow=c(3,3))
 #    for(j in 1:(length(fire_days))){
 #    max<-raster::bbox( subset(fire_select, fire_select$perimeterd == max(fire_days)))
 #    fire_day_select <- subset(fire_select, fire_select$perimeterd == fire_days[j])
 #    plot(fire_day_select,axes=T,main=paste0(fire_day_select$incidentna,"   Day number ",j),xlim=c(max[1],max[3]),ylim=c(max[2],max[4]))
 #    #selecting the first fire perim from that date, in case there are multiples
 #    }
   # }
```

Class A ("BOTELER","Halls Top","SILVER MINE",'Chestnut Knob',"Rough Ridge","DICK'S CREEK",'CLIFFSIDE','Rattlesnake Hollow','MAPLE SPRINGS','Rock Mountain',"OLD ROUGHY",
"KNOB","QUARRY CREEK","DOBSON 3","CLEAR CREEK","TELLICO","TIMBER RIDGE","East Miller Cove","FEREBEE MEMORIAL","HORTON","CAMP BRANCH","DOBSON KNOB") 
Class B ("PARTY ROCK","Pinnacle Mountain", "COBBLY NOB",)


```{r}
SoundInc<-c("BOTELER","Halls Top","SILVER MINE",'Chestnut Knob',"Rough Ridge","DICK'S CREEK",'CLIFFSIDE','Rattlesnake Hollow','MAPLE SPRINGS','Rock Mountain',"OLD ROUGHY",
"KNOB","Quarry Creek","DOBSON 3","CLEAR CREEK","TELLICO","TIMBER RIDGE","East Miller Cove","FEREBEE MEMORIAL","HORTON","CAMP BRANCH","DOBSON KNOB","Wolf Creek","HAPPY VALLEY RIDGE","ROUGH RIDGE","WHITE CREEK")
Firesinclude<-perimeter_map %>%
  subset(perimeter_map$incidentna %in% SoundInc)
#SoundInc[!SoundInc %in% unique(Firesinclude$incidentna)]

length(unique(perimeter_map$incidentna))
```




Pre-Processing for the Geomac files

Here we are calculating the spread direction and rate for each file
The direction is determined by looking at the differnce between the centroids of the fire between two steps.


```{r,message=FALSE,warning=FALSE,eval=F}
 
climate_day_mat <- NULL

wsv_dat_df<-as.data.frame(wsv_dat)
##Select for fires that lasted more than 1 day
fire_names_manydays <-fire_names[!duplicated(fire_names)]
fire_names_manydays <- fire_names_manydays[!is.na(fire_names_manydays)] ##Removing potential NAs
fire_names_manydays<- fire_names_manydays[fire_names_manydays %in% SoundInc]

### For each fire for each day. 
for (i in 1:length(fire_names_manydays)){
 # print(fire_names_manydays[i])

  fire_select <- subset(perimeter_map, perimeter_map$incidentna ==fire_names_manydays[i])#selecting an individual fire
  fire_days <- as.character(sort(unique(fire_select$TrueDate)))
  ### Check that there are two days worth of data to look at. 
  if(length(fire_days) < 2) next
  storedcells<-NULL
  dftest<-as.data.frame(fire_select)
   ### This subloop looks through each set of polygons (t, t+1) and finds the last day in which expansion occurs
  ### this will indicate when to tell th algorithim to consider the remaining cells failed spread. 
  
  for(j in 1:(length(fire_days)-1)){
    ## Day t shape
    fire_day_select <- subset(fire_select, fire_select$TrueDate == fire_days[j])# selecting the first day of the fire
    fire_day_select<-fire_day_select[order(fire_day_select$acres),]
    fire_day_select <- fire_day_select[1,] #selecting the first fire perim from that date, in case there are multiples
    ## Day t+1 shape
    fire_day_select_1 <- subset(fire_select, fire_select$TrueDate== fire_days[j+1])# getting day 2 fire perimeter
    fire_day_select_1<-fire_day_select_1[order(fire_day_select_1$acres),]
    fire_day_select_1 <- fire_day_select_1[1,] #selecting the first fire perim from that date, in case there are multiples
    area_expansion <-(area(fire_day_select_1)/4046.86)-(area(fire_day_select)/4046.86)
    if(area_expansion < 30.00){
      next()
      }
    lastday<-j
 
  }
 
  for(j in 1:(length(fire_days)-1)){
 
    Failedvalues<-NA
    Successcells<-NA
    EndFailedvalues<-NA
    #print(paste0("day  ",j))
    ## day t shape
    fire_day_select <- subset(fire_select, fire_select$TrueDate == fire_days[j])# selecting the first day of the fire
    fire_day_select<-fire_day_select[order(fire_day_select$acres),]
    fire_day_select <- fire_day_select[1,] #selecting the first fire perim from that date, in case there are multiples
    ## day t+1 shape
    fire_day_select_1 <- subset(fire_select, fire_select$TrueDate== fire_days[j+1])#getting day 2 fire perimeter
    fire_day_select_1<-fire_day_select_1[order(fire_day_select_1$acres),]
    fire_day_select_1 <- fire_day_select_1[1,] #selecting the first fire perim from that date, in case there are multiples
    ## calculate area of expansion, Area m2 to acres.
    area_expansion <-(area(fire_day_select_1)/4046.86)-(area(fire_day_select)/4046.86)
    ### In this case the spread would be less than one 250m cell in our simulation.
    if(area_expansion < 30.00){
      #print("next")
      next()
      }
    
    ### Here we associate the wind and fire weather index, and reclassify the 
    ### raster to associate with spread/not spread cells
    wind_today<-wsv_dat_df %>%
      subset(date==gsub("/","-",paste0(fire_days[j],'T00:00:00Z')))
    WindMap<-climate_stack$X11_Ecoregions
    WindTrans=as.matrix(data.frame(was=c(1,2,3,4,5,6,8,9,10,11),
               is=as.numeric(t(wind_today[2:11]))))
    Wind_Reclas<-reclassify(WindMap,WindTrans)
    windir_today<-wdir_dat %>%
      subset(date==gsub("/","-",paste0(fire_days[j],'T00:00:00Z')))
    WindDirRe=as.matrix(data.frame(was=c(1,2,3,4,5,6,8,9,10,11),
               is=as.numeric(t(windir_today[2:11]))))
    WindDir_Reclas<-reclassify(WindMap,WindDirRe)
    
    
    fire_today<-fwi_date_dat%>%
      subset(Date ==gsub("/","-",paste0(fire_days[j],'T00:00:00Z')))%>%
      arrange(Ecoregion)
    FireMap<-climate_stack$X11_Ecoregions
    FireTrans=as.matrix(data.frame(was=c(1,2,3,4,5,6,8,9,10,11),
               is=fire_today$FWI))
    FireWeather<-reclassify(FireMap,FireTrans)  
    End_stack<-stack(climate_stack,FireWeather,Wind_Reclas,WindDir_Reclas)
    
    #Creating vector of fire dates. It doesnt work when I bind them below for some reason 
    date_char <- as.POSIXct(as.character(fire_day_select$TrueDate)) 
    
    ##Extracting climate and fuels variables from raster stack.
    #This will compile a data frame of every cell that fire perimeters touch and whether 
    day1 <- extract(End_stack, fire_day_select, cellnumbers = TRUE, df=TRUE, method="simple")
    
    day2 <- extract(End_stack, fire_day_select_1, cellnumbers = TRUE, df=TRUE, method="simple")
    
    # First find day not in stored, then find adajecnts, remove adjecnets in stored. 
    
    day1cells<-day1$cell[!day1$cell %in% storedcells]
    storedcells<-c(storedcells,day1$cell)
    if( length(day1cells) >0){ 
    adjacentcells1<-adjacent(End_stack,day1cells,directions=4, pairs=TRUE,id=TRUE)
    adjacentcells1<-unique(adjacentcells1[,3])
    adjacentcells1<-adjacentcells1[!adjacentcells1 %in% storedcells]
    }else(adjacentcells1=NA)
    newspread<-day2$cell[!day2$cell %in% storedcells]
    ### Calculate failed spread, areas where spred could occur, but are have not previously been tried. 
    Failedvalues<-data.frame()
    if( length(day1cells) >0){ 
    FailedCells=adjacentcells1[!adjacentcells1 %in% newspread]
    Failedvalues<-as.data.frame(extract(End_stack,adjacentcells1))
    }
    if (nrow(Failedvalues)>0){ Failedvalues$spread_success<-0}
    Successcells<-as.data.frame(extract(End_stack,newspread))
    if (nrow(Successcells)==0){next}
    ### Successful spread gets one 
    Successcells$spread_success<-1
    ### Here if it is the last day of spread, calculate one more days possible spread,
    ### all of which is counted as failed. 
    EndFailedvalues<-data.frame()
    if(j==(lastday)){
    ### Creating the same wind and fire weather index as above. 
    wind_today<-wsv_dat_df %>%
      subset(date==gsub("/","-",paste0(fire_days[j],'T00:00:00Z')))
    WindMap<-climate_stack$X11_Ecoregions
    WindTrans=as.matrix(data.frame(was=c(1,2,3,4,5,6,8,9,10,11),
               is=as.numeric(t(wind_today[2:11]))))
    Wind_Reclas<-reclassify(WindMap,WindTrans)
    windir_today<-wdir_dat %>%
      subset(date==gsub("/","-",paste0(fire_days[j],'T00:00:00Z')))
    WindDirRe=as.matrix(data.frame(was=c(2,3,4,5,6,7,8,9,10,11),
               is=as.numeric(t(windir_today[2:11]))))
    WindDir_Reclas<-reclassify(WindMap,WindDirRe)
    fire_today<-fwi_date_dat%>%
      subset(Date ==gsub("/","-",paste0(fire_days[j],'T00:00:00Z')))%>%
      arrange(Ecoregion)
    FireMap<-climate_stack$X11_Ecoregions
    FireTrans=as.matrix(data.frame(was=c(1,2,3,4,5,6,8,9,10,11),
               is=fire_today$FWI))
    FireWeather<-reclassify(FireMap,FireTrans)  
    End_stack<-stack(climate_stack,FireWeather)
    End_stack<-stack(End_stack,Wind_Reclas)
    EndCells<-adjacent(End_stack,day2$cell,directions=4, pairs=TRUE,id=TRUE)
    EndCells<-unique(EndCells[,3])
    EndCells<-EndCells[!EndCells %in% storedcells]
    EndFailedvalues<-as.data.frame(extract(End_stack,EndCells))
    EndFailedvalues$spread_success<-0
    }
    ### Adding cells to one dataframe.
    if(nrow(Failedvalues)>0 & nrow(Successcells)>0){
    Dfout<-rbind(Failedvalues,Successcells)}else{Dfout<-Successcells}
    if(nrow(EndFailedvalues)>0){Dfout<-rbind(Dfout,EndFailedvalues) }
   # print(table(Dfout$spread_success))
    Dfout$Area_expansion<-area_expansion
    climate_day_df <- cbind(fire_names_manydays[j],
                                 as.character(date_char),Dfout) #Putting everything into a big dataframe with all climate variables
    climate_day_mat <- rbind.data.frame(climate_day_mat, climate_day_df) #binding individual days to every other day
  }
  
}
## Save for future analysis
write.csv(climate_day_mat,"Spread_91621.csv")
#rm(k)
unique(as.Date(climate_day_mat$V2,origin="1970-1-1"))
table(climate_day_mat$spread_success)  
Expansion<-climate_day_mat[climate_day_mat$Area_expansion>1,]
table(Expansion$spread_success)
```




```{r}
fix<-function(x){return(as.numeric(as.character(x)))}
### Cleaning up the dataframe. 
climate_day_mat<-read.csv("Z:/Robbins/Sapps/Chapter3/Code/Scrpple_111721/Spread_91621.csv")
climate_day_total<-climate_day_mat[-1]

### Looking at files that have all the nessecary data 
climate_day_total<-climate_day_total[climate_day_total$X11_Ecoregions.1!=0,]
climate_day_complete <- climate_day_total[complete.cases(climate_day_total[2:10]),]

##Attaching a unique ID to each row in case we need it later
climate_day_complete <- cbind(1:nrow(climate_day_complete), climate_day_complete)

##Renaming columns
#climate_day_complete<-climate_day_complete[,-1]
colnames(climate_day_complete) <- c("ID","FireName",  "date", "wind_region", "fuel_number", "uphill_azi", "slope",
                               "FWI","WSPD" , "spread","expansion")
climate_day_complete$expansion<-climate_day_complete$expansion*0.404686 ## To hectares
climate_day_complete$fuel_number<-climate_day_complete$fuel_number/2500
climate_day_complete$fuel_number[climate_day_complete$fuel_number >1.0]<-1.0



U_b <- 5 # This changes based on fire severity. Combustion bounancy.
### Caculating windspeed in direction of spread 
relative_wd <- as.numeric(climate_day_complete$WSPD) - as.numeric(climate_day_complete$uphill_azi)
### Calculating effective wind speed. 
climate_day_complete$effective_wsv <- U_b * ((fix(climate_day_complete$WSPD)/U_b) ^ 2 + 2*(fix(climate_day_complete$WSPD)/U_b) *  
                sin(fix(climate_day_complete$slope)) * cos(relative_wd) + (sin(fix(climate_day_complete$slope))^2)^0.5)

head(climate_day_complete)

hexbinplot(fix(climate_day_complete$spread)~fix(climate_day_complete$FWI),xlab="FWI",ylab="Spread",xbins=50,aspect=1,type="r")

hexbinplot(fix(climate_day_complete$spread)~fix(climate_day_complete$effective_wsv),xlab="Wind Speed",ylab="Spread",xbins=50,aspect=1,type="r")
hexbinplot(fix(climate_day_complete$spread)~fix(climate_day_complete$fuel_number),xlab="Fuel number",ylab="Spread",xbins=50,aspect=1,type="r")
hexbinplot(fix(climate_day_complete$expansion)~fix(climate_day_complete$FWI),xlab="FWI",ylab="Spread",xbins=50,aspect=1,type="r")
hexbinplot(fix(climate_day_complete$expansion)~fix(climate_day_complete$effective_wsv),xlab="Wind Speed",ylab="Spread",xbins=50,aspect=1,type="r")
```



```{r}
spread_vars_short<-climate_day_complete
#table(spread_vars_short$spread)
Full_logit <- glm(spread ~fix(FWI)+fix(fuel_number)+fix(effective_wsv), 
                  data = spread_vars_short, family = "binomial")
summary(Full_logit)
#hist(spread_vars_short$finefuels)
AIC(Full_logit)
```


Calculating Spread Probability

```{r}
Full_logit <- glm(fix(spread) ~  fix(fuel_number)+fix(FWI), 
                  data = spread_vars_short, family = "binomial")
summary(Full_logit)
#hist(spread_vars_short$finefuels)
AIC(Full_logit)
```

```{r}
Nofinefuels_logit<-glm(fix(spread) ~ fix(effective_wsv) + fix(FWI), 
                  data = spread_vars_short, family = "binomial")

summary(Nofinefuels_logit)

AIC(Nofinefuels_logit)
(AIC(Full_logit)-AIC(Nofinefuels_logit))
```
Removing the fine fuels component has a negligible influence on model preformance 

```{r}
JustFWI<-glm(fix(spread) ~ fix(FWI), 
                  data = spread_vars_short, family = "binomial")
summary(JustFWI)
```




```{r}
AIC(JustFWI)
AIC(Full_logit)
(AIC(Full_logit)-AIC(JustFWI))
```
Using just fire weather index preforms far worse than either the full or the no fine fuels model 



```{r}
NoWind<-glm(fix(spread) ~  fix(fuel_number)+fix(FWI), data = spread_vars_short, family = "binomial")

summary(NoWind)


#min(fix(spread_vars_short$FWI))
#max(fix(spread_vars_short$FWI))
```

```{r}
AIC(NoWind)
(AIC(Full_logit)-AIC(NoWind))
anova(Nofinefuels_logit,Full_logit)
```


The fuels plus FWI model preforms the worse of all 


Plotting out the influence.

```{r,fig.width=6.0,fig.height=6.0}
High_FF<-data.frame(FWI=seq(min(fix(spread_vars_short$FWI)),40,length.out = 1000),fuel_number=rep(quantile(fix(spread_vars_short$fuel_number),.99),1000))
Med_FF<-data.frame(FWI=seq(min(fix(spread_vars_short$FWI)),40,length.out = 1000),fuel_number=rep(quantile(fix(spread_vars_short$fuel_number),.50),1000))
Low_FF<-data.frame(FWI=seq(min(fix(spread_vars_short$FWI)),40,length.out = 1000),fuel_number=rep(quantile(fix(spread_vars_short$fuel_number),.01),1000))





plot(High_FF$FWI,predict(Full_logit,High_FF,type="response"),ylab="Probability of Spread",xlab="Fire Weather Index",cex.axis=1.5,cex.lab=1.5,cex.main=1.7,type="l",lwd=5.0,main="Fire Spread Probability")
lines(Med_FF$FWI,predict(Full_logit,Med_FF,type="response"),col="red",lwd=5.0)
lines(Low_FF$FWI,predict(Full_logit,Low_FF,type="response"),col="blue",lwd=5.0)
legend(10,.8,legend=c("99th percentile fuel","Median fine fuel","1st percentile fuel"),lty=c(1,1,1),lwd=c(5.0,5.0,5.0),col=c("black","red","blue"),cex=1.2)
```

```{r,fig.width=6.0,fig.height=6.0}

High_FF<-data.frame(fuel_number=seq(0,1,length.out = 1000),FWI=rep(quantile(fix(spread_vars_short$FWI),.99),1000))
Med_FF<-data.frame(fuel_number=seq(0,1,length.out = 1000),FWI=rep(quantile(fix(spread_vars_short$FWI),.5),1000))
Low_FF<-data.frame(fuel_number=seq(0,1,length.out = 1000),FWI=rep(quantile(fix(spread_vars_short$FWI),.01),1000))

plot(High_FF$fuel_number,predict(Full_logit,High_FF,type="response"),ylab="Probability of Spread",ylim=c(0,1.0),
     xlab="Fine fuel rating",cex=1.2)
points(Med_FF$fuel_number,predict(Full_logit,Med_FF,type="response"),col="red")
points(Low_FF$fuel_number,predict(Full_logit,Low_FF,type="response"),col="blue")
legend(.58,.32,legend=c("99th percentile FWI","Median FWI","1st percentile FWI"),lty=c(1,1,1),col=c("black","red","blue"),cex=1.2)
```



```{r}
hist(spread_vars_short$FWI)
```

#### Maximum Daily Spread


```{r}
####Maximum daily spread area
#Linear relationship

my_colors<-colorRampPalette(rev(brewer.pal(11,'Spectral')))
# colnames(spread_vars_short)
# removezero<-spread_vars_success
# 
# 
# 
# hexbinplot(fix(spread_vars_success$expansion)~fix(spread_vars_success[,2]),xlab="FWI",ylab="Spread",xbins=50,aspect=1,type="r",colramp=my_colors)
# hexbinplot(fix(spread_vars_success$expansion)~fix(spread_vars_success[,4]),xlab="Windspeed",ylab="Spread",xbins=50,aspect=1,type="r",colramp=my_colors)

```



```{r}
library(dplyr)
spvar<-spread_vars_short[spread_vars_short$expansion>=0,]
colnames(spvar)
spva2<-spvar %>%
  dplyr::group_by(FireName,date)%>%
  dplyr::summarise(FWI=mean(FWI),WSPD=mean(WSPD),expansion=mean(expansion))

Expansionfull<-glm(fix(expansion) ~ fix(WSPD) + fix(FWI), 
             data =spvar )

summary(Expansionfull)
```



```{r}
library(MASS)
ExpansionFWI<-glm(fix(expansion) ~ fix(FWI), data =spvar)
summary(ExpansionFWI)
ExpansionWSPD<-glm(expansion~ WSPD, data =spvar)
summary(ExpansionWSPD)


AIC(ExpansionFWI)-AIC(ExpansionWSPD)

hist(fix(spread_vars_short$expansion))
anova(Expansionfull,ExpansionFWI)
AIC(Expansionfull)-AIC(ExpansionFWI)
```

```{r}
Expansionfull<-glm(fix(expansion) ~ fix(WSPD), 
             data =spvar )
anova(Expansionfull,ExpansionFWI)
AIC(Expansionfull)-AIC(ExpansionFWI)
```


```{r}
plot(seq(0,30,.5),predict(ExpansionWSPD,newdata=data.frame(WSPD=seq(0,30,.5)),type="response"),ylab="Max daily HA burned",xlab="Windspeed Km/h")
hist(spread_vars_short$WSPD)
```